### 2019-01-11 fj_teamken_analysis.Rmd
sloppy now but it'll be ok

---
title: "Team Ken FJ! analysis"
author: "Monica Thieu"
date: "11/22/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(googledrive)
require(magrittr)
require(tidyverse)
```

## Setup

```{r}
# Load the data from me google drive
drive_download(as_id("https://docs.google.com/a/columbia.edu/spreadsheets/d/10l6IeI0VtWBaBtZDquGgIXUa0cSw-NnbbGW-F4hzfLE/edit"), path = "fj_teamken", type = "csv", overwrite = TRUE)

raw <- read_csv("fj_teamken.csv",
                col_names = c("timestamp",
                              "name",
                              "show_number",
                              "show_date",
                              "category",
                              "response",
                              "n_show_correct",
                              "comments",
                              "dd_sj_200",
                              "dd_sj_400",
                              "dd_sj_600",
                              "dd_sj_800",
                              "dd_sj_1000",
                              "dd_dj_400",
                              "dd_dj_800",
                              "dd_dj_1200",
                              "dd_dj_1600",
                              "dd_dj_2000"),
                skip = 1)

dds <- raw %>%
  filter(name == "Monica") %>%
  select(show_number, starts_with("dd")) %>%
  gather(key = "key", value = "clue_col", -show_number) %>%
  filter(!is.na(clue_col)) %>%
  separate(key, into = c("discard", "round", "clue_row")) %>%
  arrange(show_number, desc(round)) %>%
  group_by(show_number, round) %>%
  separate(clue_col, into = c("clue_col_1", "clue_col_2"), sep = "[,]", fill = "right") %>%
  select(-discard) %>%
  mutate(clue_row = as.integer(clue_row),
         clue_row = if_else(round == "sj",
                            clue_row / 200,
                            clue_row / 400),
         clue_row = as.integer(clue_row),
         clue_col_2 = str_sub(clue_col_2, start = 2L)) %>%
  gather(key = "discard", value = "clue_col", starts_with("clue_col")) %>%
  select(-discard) %>%
  filter(!is.na(clue_col)) %>%
  mutate(clue_col = as.integer(str_sub(clue_col, start = -1L)))

d <- raw %>%
  select(-timestamp, -show_date, -starts_with("dd")) %>%
  mutate(category = toupper(category),
         response = tolower(response),
         response = recode(response,
                           `incorrect, but thought of the correct answer and negged myself` = "self_neg",
                           `incorrect, but only because of spelling etc.` = "misspell",
                           `incorrect, but figured out what the clue was really asking for` = "almost"),
         response_binary = if_else(response == "correct", 1L, 0L),
         response_ternary = case_when(response == "correct" ~ 1,
                                      response %in% c("self_neg", "misspell") ~ 0.5,
                                      TRUE ~ 0),
         season = if_else(show_number >= 7586, 34, 26),
         category_ll = if_else(str_detect(comments, "ll \\("),
                               str_extract(comments, "\\(([^)]+)\\)"),
                               NA_character_),
         category_ll = str_sub(category_ll, start = 2L, end = -2L),
         category_ll = str_split(category_ll, pattern = ", "),
         category_ll_main = map_chr(category_ll, ~.x[1])) %>%
  group_by(season, show_number, category) %>%
  # Hack to get Monica's stuff on top
  arrange(desc(name)) %>%
  nest() %>%
  mutate(category_ll = map(data, ~.x$category_ll[[1]]),
         category_ll_main = map_chr(data, ~.x$category_ll_main[1]),
         data = map(data, ~.x %>% select(-starts_with("category_ll"))),
         toc = if_else(show_number %in% c(5916:5925, 7626:7635), TRUE, FALSE))

d_wide <- d %>%
  unnest(data, .preserve = "category_ll") %>%
  select(-comments, -starts_with("response_")) %>%
  mutate(name = recode(name,
                       Ken = "resp_kj",
                       Matt = "resp_mj",
                       Monica = "resp_mt")) %>%
  spread(name, response)

d_wide_complete <- d_wide %>%
  filter(!is.na(resp_kj), !is.na(resp_mj), !is.na(resp_mt))
```

## Person performance stuff

```{r}
d %>%
  filter(show_number %in% d_wide_complete$show_number, !is.na(category_ll_main), season == 34) %>%
  unnest(data) %>%
  ggplot(aes(x = name, fill = factor(response_binary))) +
  geom_bar() +
  scale_fill_manual(values = c("salmon", "springgreen2")) +
  facet_wrap(~category_ll_main, scales = "free_y") +
  labs(x = "Team member",
       y = "# of questions",
       fill = "Correct?") +
  theme_bw()
```

```{r}
d %>%
  filter(show_number %in% d_wide_complete$show_number, !is.na(category_ll_main), season == 34) %>%
  unnest(data) %>%
  ggplot(aes(x = name, fill = factor(response_ternary))) +
  geom_bar() +
  scale_fill_manual(values = c("salmon", "goldenrod1", "springgreen2")) +
  facet_wrap(~category_ll_main, scales = "free_y") +
  labs(x = "Team member",
       y = "# of questions",
       fill = "Correct?") +
  theme_bw()
```

```{r}
d %>%
  filter(toc) %>%
  unnest(data) %>%
  ggplot(aes(x = name, fill = factor(response_binary))) +
  geom_bar() +
  scale_fill_manual(values = c("salmon", "springgreen2")) +
  facet_wrap(~season, scales = "fixed") +
  labs(x = "Team member",
       y = "# of questions",
       fill = "Correct?") +
  theme_bw()
```

## Category frequency stuff

```{r}
d_wide_complete %>%
  filter(!is.na(category_ll_main)) %>%
  group_by(season) %>%
  count(category_ll_main) %>%
  mutate(n = if_else(season == 26, -1L * n, n),
         category_ll_main = fct_reorder(category_ll_main, n, .fun = max, .desc = TRUE)) %>%
  ggplot(aes(x = category_ll_main, y = n, fill = factor(season))) +
  geom_bar(stat = "identity") +
  # scale_fill_manual(values = c("salmon", "springgreen2")) +
  # facet_wrap(~category_ll_main, scales = "free_y") +
  coord_flip() +
  labs(x = "broad category",
       y = "# of questions",
       fill = "season",
       title = "FJ category frequencies by season") +
  theme_bw()
```

## Daily double stuff

```{r}
dds %>%
  group_by(round, clue_row, clue_col) %>%
  tally() %>%
  ungroup() %>%
  mutate(round = recode(round,
                        sj = "Single Jeopardy",
                        dj = "Double Jeopardy"),
         round = fct_rev(round)) %>%
  ggplot(aes(x = clue_col, y = clue_row, fill = n)) +
  geom_raster() +
  scale_y_reverse() +
  viridis::scale_fill_viridis() +
  facet_wrap(~ round) +
  labs(x = "Clue column",
       y = "Clue row",
       title = "Heatmap of DD incidence, most of S34",
       subtitle = "SJ slightly dimmer than DJ bc of more DDs left covered?",
       fill = "# of DDs") +
  theme_bw()
```

```{r}
dds %>%
  filter(round == "dj") %>%
  select(-clue_col) %>%
  group_by(show_number) %>%
  mutate(index = paste0("row_", 1:n())) %>%
  spread(index, clue_row) %>%
  mutate(row_diff = row_2 - row_1) %>%
  ggplot(aes(x = row_diff)) +
  geom_histogram(binwidth = 1) +
  labs(x = "ROW distance ($ amount) between DJ DDs") +
  theme_bw()
```

```{r}
dds %>%
  filter(round == "dj") %>%
  select(-clue_row) %>%
  group_by(show_number) %>%
  mutate(index = paste0("col_", 1:n())) %>%
  spread(index, clue_col) %>%
  mutate(col_diff = abs(col_2 - col_1)) %>%
  ggplot(aes(x = col_diff)) +
  geom_histogram(binwidth = 1) +
  labs(x = "COL distance (categories) between DJ DDs") +
  theme_bw()
```

```{r}
# If daily double locations were chosen completely independently of each other,
# what should the base rates of col-wise distance be? row-wise distance?

dd_sims <- tibble(id = 1:1000) %>%
  mutate(col_1 = sample(1:6, size = n(), replace = T),
         col_2 = map_int(col_1, ~sample((1:6)[1:6 != .x], size = 1, replace = T)),
         row_1 = sample(2:5, size = n(), replace = T),
         row_2 = sample(2:5, size = n(), replace = T),
         col_diff = abs(col_2 - col_1),
         row_diff = abs(row_2 - row_1))

dd_sims %>%
  ggplot(aes(x = row_diff)) +
  geom_histogram(binwidth = 1) +
  labs(x = "ROW distance ($ amount) between DJ DDs") +
  theme_bw()

dd_sims %>%
  ggplot(aes(x = col_diff)) +
  geom_histogram(binwidth = 1) +
  labs(x = "COL distance (categories) between DJ DDs") +
  theme_bw()
```

### 2020-09-02 writing/ms.Rmd
jstudy docs, they should probably be moved

---
title: "J-Study manuscript"
author: "Monica Thieu"
date: "5/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Intro

Derpy abstract for myself:

Individual behavioral differences in human memory pay testament to the complexity of our memory systems. Studying people performing at extremes of the memory spectrum can help us learn more about memory systems as they might function in the typical individual. However, memory, especially superior memory, is not a single construct. People may exhibit markedly strong memory in a variety of ways, each of which might rely on a different feature of the memory system. Nearly all research on people with superior memory has focused on superior memorizers, or individuals with the ability, through some combination of untrained and trained strategy, to quickly encode large amounts of information, typically otherwise meaningless, and retrieve it with high accuracy.

Not all feats of impressive memory involve encoding large bodies of information at once, whether incidental or intentional. Other feats of memory are (or appear) more retrieval-based. Trivia games are one popular example, where competitors attempt to retrieve the most general knowledge, often as quickly as possible. Trivia experts are able to rapidly retrieve a broad range of facts, often having first encoded these facts years in the past. Notably, they often do this without apparent use of any memorization strategy [CITE]. Given two people with approximately equivalent life experience, and exposure to general knowledge through schooling, what leads one person to be more successful in retaining and/or retrieving facts in a cued recall situation?

Basic outline:

- Episodic and semantic memory: separate? intertwined?
    - MTL amnesics perform worse than controls on semantic fluency tasks (name exemplars of X category) that can be solved with an autobiographical episodic strategy [e.g. @Greenberg:2009fq; @Sheldon:2012ju]
    - To the degree that a task is not "process-pure," we are likely to observe interdependencies between semantic and episodic memory if both might be individually contributing to task performance. But what about semantic memory tasks that do not have obvious episodic strategies, typically those that are speeded enough to preclude episodic elaboration?
        - Participants making famous/nonfamous judgments of names, and reading names out loud, are faster to judge/read famous names with greater autobiographical significance, such that those names are more likely to be associated with autobiographical memories [@Westmacott:2003ee]
        - Participants make lexical decisions about studied words faster for words they will later "remember" vs "know" [@Sheldon:2010cd]. The authors suggest this provides evidence for ecphory or some other fast episodic retrieval component
        - Ecphoric signals may be detected _early_ during old/new recognition trials [@Waldhauser:2016fx]
        - Can this putative ecphory also support complex semantic retrieval, like answering general knowledge questions?
- What can studying trivia experts tell us about overlap between episodic and semantic memory?
    - individual differences in ecphoric strength at retrieval could contribute to 
    - detect differing contributions of encoding- and retrieval-stage processes to overall retrieval success
    - 
- What can studying trivia experts tell us that studying other special populations doesn't?
    - Relative to **amnesic patients:** patient work allows us to make critical claims about necessary and sufficient contributions of different structures/systems to memory tasks. However, these conclusions might not apply at the other end of the spectrum. Said otherwise, the contribution of "pure" episodic vs semantic components to task performance might not vary linearly with episodic and semantic memory ability all the way along the spectrum from impaired to exceptional.
    - Relative to folks with **highly superior autobiographical memory:** Most people with HSAM who have been documented in case and group studies fail to show superior memory for historical events that happened before they were born. General knowledge expertise seems epiphenomenal to superior memory for current events as a subset of autobiographical memory [@McGaugh:2014jh]
    - Relative to **memory champions:** modern memory champions deploy deliberate mnemonic strategies to encode huge amounts of information in a single sitting. General knowledge generally is acquired bit by bit and then tested at once, as opposed to having to encode at once and retrieve at once. Memory champions SEEM (cite? hard to find when people test this stuff) not to show above average general knowledge

- What research has been done on superior memory?
    - Superior memorizers
    - (MAYBE SCRATCH) savants?
    - Highly superior autobiographical memory
- What can studying trivia experts tell us that studying other superior memory groups doesn't?
    - Trivia expertise might be more likely to derive from innate memory differences than superior memorization, which tends to rely on becoming facile with a strategy
    - Trivia facts, as must anything else, must be encoded through episodic mechanisms, but once encoded, are considered squarely within the domain of semantic memory. Studying trivia memory can tell us a lot about the putative boundary between episodic and semantic memory
    - [@Brandt:2017cd]
- What research has been done on general knowledge capacity as its own memory construct?
- Thus, the current study

### 2020-12-24 jeopardy_proper/fj_teamken_analysis.Rmd
move to new folder

--- 2019-01-11 fj_teamken_analysis.Rmd
@@
 date: "11/22/2018"
-output: html_document
+output:
+  html_document:
+    toc: true
+    toc_float: true
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
 require(googledrive)
@@
 require(tidyverse)
+require(rvest)
+# Apparently we need this shit now
+options(mc.cores = parallel::detectCores())
 ```
+
+Jeopardy!, the ultimate knowledge-based game show (in my opinion), lends itself very well to analysis about the game itself.
+
+For the 2019 Jeopardy! All-Star Games, I started doing some rough analyses about what kinds of patterns appear in Jeopardy! games that we might be able to harness for our own use.
+
+What this blog post **is:**
+
+What this blog post **is not:**
 
@@
 
+I realized that a big piece of information we could recover from the Final Jeopardy! clues that we all answered was _clue categories._
+
 ```{r}
@@
 ```
+
+## extra lock 2 game shit
+
+I was going to do a rough grid search across possible score sets to see the conformations that end in a game 2 lock, but the dataframe gets huge very quickly and stuff was running a little too slow for my taste.
+
+```{r, eval = FALSE}
+scores <- crossing(team1_game1 = 1:30,
+                   team2_game1 = 1:30,
+                   team3_game1 = 1:30) %>%
+  filter(team1_game1 >= team2_game1, team1_game1 >= team3_game1)
+```
+
+## Daily Double extravaganza (as heard on Planet Money)
+
+```{r big ass dd scrapey bitch, eval = FALSE}
+seasons_raw <- 25:35 %>%
+  paste0("http://www.j-archive.com/showseason.php?season=", .) %>%
+  map(~read_html(.)) %>%
+  map(~html_nodes(., "a"))
+
+jscrape_raw <- seasons_raw %>%
+  tibble(season = 25:35,
+         raw = .) %>%
+  mutate(text = map(raw, ~html_text(., trim = T)),
+         link = map(raw, ~html_attr(., "href"))) %>%
+  select(-raw) %>%
+  unnest() %>%
+  filter(grepl("showgame", link)) %>%
+  mutate(web_id = as.integer(str_sub(link, start = -4L)),
+         game_id = as.integer(str_sub(text, start = 2L, end = 5L)),
+         these_htmls = map(web_id, ~read_html(paste0("http://j-archive.com/showgame.php?game_id=", .x))),
+         these_nodes = map(these_htmls, ~html_nodes(.x, ".clue")))
+
+jscrape <- jscrape_raw$these_nodes %>%
+  map(~.x %>%
+        html_text(trim = T) %>%
+        tibble(raw = .) %>%
+        # bye bye FJ, for now at least
+        slice(-nrow(.))) %>%
+  tibble(season = jscrape_raw$season,
+         web_id = jscrape_raw$web_id,
+         stuff = .) %>%
+  filter(map_int(stuff, nrow) == 60) %>%
+  unnest() %>%
+  separate(raw, into = c("value", "order", "blank1", "blank2", "clue"), sep = "\n", fill = "right") %>%
+  select(-starts_with("blank")) %>%
+  mutate_all(str_trim, side = "both") %>%
+  mutate(web_id = as.integer(web_id)) %>%
+  # Splicing clue point value for the empty cells
+  group_by(web_id) %>%
+  mutate(idx = 1:n()) %>%
+  filter(web_id != 3719) %>%
+  mutate(column = rep(1:6, times = 10),
+         row = rep(1:5, each = 6, times = 2),
+         round = rep(c("sj", "dj"), each = 30),
+         is_dd = if_else(startsWith(value, "DD"), TRUE, FALSE),
+         nspaces_clue = str_count(clue, " ")) %>%
+  select(-value, -idx)
+
+write_csv(jscrape, "dd_scrape_25_35.csv")
+```
+
+```{r}
+jscrape <- read_csv("dd_scrape_25_35.csv")
+```
+
+```{r}
+jscrape %>%
+  group_by(season, web_id, round, row, column) %>%
+  summarize(n = sum(is_dd),
+            mean_nspaces = mean(nspaces_clue, na.rm = TRUE)) %>%
+  mutate(category_length = if_else(mean_nspaces > 10,
+                                      "long",
+                                      "short",
+                                      missing = "short")) %>%
+  group_by(round, row, column, category_length) %>%
+  summarize(n = sum(n)) %>%
+  ungroup() %>%
+  mutate(round = recode(round,
+                        sj = "Single Jeopardy",
+                        dj = "Double Jeopardy"),
+         round = fct_rev(round),
+         n = na_if(n, 0),
+         n = if_else(round == "Double Jeopardy",
+                     n/2,
+                     as.double(n))) %>%
+  ggplot(aes(x = column, y = row, fill = n)) +
+  geom_raster() +
+  scale_y_reverse() +
+  viridis::scale_fill_viridis() +
+  # Remove category_length if not conditioning by this
+  facet_grid(category_length ~ round) +
+  labs(x = "Clue column",
+       y = "Clue row",
+       title = "Heatmap of DD incidence, most of seasons 25-35",
+       subtitle = "DDs don't come up in wordplay categories",
+       fill = "# of DDs") +
+  theme_bw()
+```
+
+```{r}
+jscrape %>%
+  group_by(web_id, round, column) %>%
+  summarize(mean_nspaces = mean(nspaces_clue, na.rm = TRUE),
+            contains_dd = sum(is_dd)) %>%
+  ungroup() %>%
+  mutate(round = recode(round,
+                        sj = "Single Jeopardy",
+                        dj = "Double Jeopardy"),
+         round = fct_rev(round)) %>%
+  ggplot(aes(x = mean_nspaces, fill = factor(contains_dd))) +
+  geom_density(alpha = 0.5) +
+  labs(x = "# spaces per clue (proxy for word count)",
+       title = "Category wordiness by DD incidence") +
+  facet_grid(~round) +
+  theme_bw()
+```
+
+```{r}
+jscrape %>%
+  filter(round == "dj", is_dd) %>%
+  select(web_id, row) %>%
+  group_by(web_id) %>%
+  mutate(index = paste0("row_", 1:n())) %>%
+  spread(index, row) %>%
+  select(-row_3) %>%
+  mutate(row_diff = row_2 - row_1) %>%
+  ggplot(aes(x = row_diff)) +
+  geom_histogram(binwidth = 1) +
+  labs(x = "ROW distance ($ amount) between DJ DDs") +
+  theme_bw()
+```
+
+```{r}
+jscrape %>%
+  filter(round == "dj", is_dd) %>%
+  select(web_id, column) %>%
+  group_by(web_id) %>%
+  mutate(index = paste0("col_", 1:n())) %>%
+  spread(index, column) %>%
+  # This one game has 3 DDs listed but it must be wrong lol
+  select(-col_3) %>%
+  mutate(col_diff = abs(col_2 - col_1)) %>%
+  ggplot(aes(x = col_diff)) +
+  geom_histogram(binwidth = 1) +
+  labs(x = "COL distance (categories) between DJ DDs") +
+  theme_bw()
+```
+
+```{r}
+dd_by_row <- jscrape %>%
+  mutate(is_dd = as.integer(is_dd),
+         # center at 10 words/clue (my wordplay cutoff)
+         row = row - 3,
+         row_quad = abs(row),
+         column = column - 1,
+         season = season - 35) %>%
+  group_by(web_id, round, column) %>%
+  mutate(category_length = if_else(mean(nspaces_clue) > 10,
+                                      "long",
+                                      "short",
+                                      missing = "short")) %>%
+  ungroup() %>%
+  filter(!is.na(is_dd)) %>%
+  nest(-round) %>%
+  mutate(model = map(data, ~glm(is_dd ~ factor(row) + category_length + season - 1, 
+                                family = binomial(),
+                                data = .)))
+```
+
+```{r}
+summary(dd_by_row$model[[2]])
+```
+
+```{r}
+summary(dd_by_row$model[[1]])
+```
+
+```{r glm of prob of wordplay by column location}
+category_length_by_col <- jscrape %>%
+  group_by(season, web_id, round, column) %>%
+  # signed so 1 is a short category
+  summarize(category_length = mean(nspaces_clue, na.rm = T) <= 10) %>%
+  ungroup() %>%
+  filter(!is.na(category_length)) %>%
+  mutate(season = season - 35) %>%
+  nest(-round) %>%
+  mutate(model = map(data, ~glm(category_length ~ factor(column) + season - 1, family = binomial(), data = .)))
+
+category_length_by_col$model %>% map(summary)
+```
+
+Wordplay categories are less likely to be in the 1st column and more likely to be in the 6th column.
+
+```{r}
+dd_by_col <- jscrape %>%
+  mutate(is_dd = as.integer(is_dd),
+         # center at 10 words/clue (my wordplay cutoff)
+         season = season - 35) %>%
+  filter(!is.na(is_dd)) %>%
+  group_by(season, web_id, round, column) %>%
+  summarize(category_length = if_else(mean(nspaces_clue, na.rm = TRUE) > 10,
+                                      "long",
+                                      "short"),
+            contains_dd = sum(is_dd)) %>%
+  ungroup() %>%
+  nest(-round) %>%
+  mutate(model = map(data, ~glm(contains_dd ~ factor(column) + category_length + season, 
+                                family = binomial(),
+                                data = .)))
+```
+
+```{r}
+summary(dd_by_col$model[[2]])
+```
+
+```{r}
+summary(dd_by_col$model[[1]])
+```
+
+```{r}
+dd_by_col %>%
+  select(-model) %>%
+  unnest() %>%
+  filter(contains_dd == 1)
+
+# This is category long-ness by column, categorically
+jscrape %>%
+  group_by(season, web_id, round, column) %>%
+  # signed so 1 is a short category
+  summarize(category_length = mean(nspaces_clue, na.rm = T) <= 10) %>%
+  ungroup() %>%
+  filter(!is.na(category_length)) %>%
+  mutate(season = season - 35) %>%
+  glm(category_length ~ factor(column) + season - 1, family = binomial(), data = .) %>%
+  summary()
+```

### 2021-04-26 R/clean_encoding.R
init hella gorilla data cleaning

@@ -1,0 +1,45 @@
+require(tidyverse)
+require(magrittr)
+source(here::here("R", "utils_read_gorilla.R"))
+
+raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+  read_gorilla_data("task-ujps|task-wckg")
+
+pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
+  select(-n_correct) %>%
+  pivot_wider(names_from = category_num, values_from = category, names_prefix = "category") %>%
+  mutate(categories = paste(category1, category2, sep = "_"))
+
+less_raw <- raw %>% 
+  select(subj_num = `Participant Private ID`,
+         group,
+         group_trial_num = trial_num,
+         trial_screen = `Screen Name`,
+         zone = `Zone Name`,
+         rt = `Reaction Time`,
+         resp = `Response`,
+         starts_with("encoding_sentence")) %>% 
+  filter(trial_screen == "fact", zone == "slider") %>%
+  mutate(# Should catch slider trials where the slider was never clicked
+         # bc I think timeout will still be true if submitResp was never clicked but the slider was moved
+         resp = if_else(zone == "scale" & rt >= 34900, NA_character_, resp),
+         resp = as.integer(resp)) %>%
+  nest(data = -c(subj_num, group, group_trial_num)) %>% 
+  # stuff to pull only the row of scale trials where the slider stopped moving
+  mutate(data = map(data, get_slider_rt)) %>%
+  unnest(data) %>% 
+  # this SHOULD keep one row per trial and also keep no responses
+  select(-c(trial_screen, zone)) %>% 
+  nest(data = -subj_num) %>% 
+  left_join(pretest, by = "subj_num") %>% 
+  mutate(data = map2(data, categories,
+                     ~.x %>% select(group_trial_num,
+                                    group,
+                                    resp,
+                                    rt,
+                                    encoding_sentence = paste0("encoding_sentence.", .y)))) %>%
+  unnest(data) %>% 
+  mutate(category = if_else(group == "academic", category1, category2)) %>% 
+  select(-c(category1, category2, categories))
+
+write_csv(less_raw, file = here::here("ignore", "data", "task_encoding.csv"))

### 2021-04-26 R/clean_expertise.R

@@ -2,6 +2,8 @@ require(tidyverse)
 require(magrittr)
 source(here::here("R", "utils_read_gorilla.R"))
 
+## reading in and cleaning ----
+
 raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
   read_gorilla_data("task-v9u2")
 
@@ -25,14 +27,11 @@ less_raw <- raw %>%
   # stuff to pull only the row of scale trials where the slider stopped moving
   nest(data = -c(subj_num, trial_num, trial_screen)) %>%
   pivot_wider(names_from = trial_screen, values_from = data) %>% 
-  mutate(confidence = map(confidence,
+  mutate(confidence = map(confidence, ~.x %>% 
+                            mutate(resp = as.integer(resp)) %>% 
+                            get_slider_rt()),
+         confidence = map(confidence,
                           ~.x %>%
-                            mutate(trial_num_within = 1:nrow(.),
-                                   resp = as.integer(resp),
-                                   resp_diff = c(diff(resp), NA_integer_),
-                                   resp_diff = coalesce(resp_diff, 0L)) %>%
-                            # this SHOULD keep one row per trial and also keep no responses
-                            filter(trial_num_within == min(trial_num_within[resp_diff == 0])) %>% 
                             select(resp, rt, timeout) %>% 
                             rename_with(~paste0(., "_conf"), everything())),
          recall = map(recall, ~.x %>%
@@ -40,6 +39,22 @@ less_raw <- raw %>%
                         mutate(rt = if_else(!is.na(timeout), 15000, rt)) %>% 
                         rename_with(~paste0(., "_recall"), c(resp, rt, timeout)))) %>%
   unnest(c(recall, confidence)) %>% 
-  mutate(acc_recall_rough = map2_lgl(resp_recall, answer, grepl, ignore.case = TRUE))
+  mutate(acc_recall_rough = map2_lgl(resp_recall, answer,
+                                     ~(grepl(.x, .y, ignore.case = T) | grepl(.y, .x, ignore.case = T)) %>% 
+                                       coalesce(FALSE)))
 
-write_csv(less_raw, file = here::here("ignore", "data", "task_jeopardy_recall.csv"))
+## scoring some by hand----
+
+less_raw %>%
+  arrange(answer) %>%
[…]

### 2021-04-26 R/clean_metamemory.R

@@ -1,0 +1,29 @@
+require(tidyverse)
+require(magrittr)
+source(here::here("R", "utils_read_gorilla.R"))
+
+raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+  read_gorilla_data("task-wlkb")
+
+less_raw <- raw %>% 
+  select(subj_num = `Participant Private ID`,
+         trial_num = `Trial Number`,
+         trial_screen = `Screen Name`,
+         zone = `Zone Name`,
+         rt = `Reaction Time`,
+         resp = `Response`,
+         timeout = `Timed Out`,
+         question,
+         answer)
+
+mem_states <- less_raw %>%
+  filter(trial_screen == "recall") %>% 
+  select(-c(trial_screen, zone))
+
+write_csv(mem_states, file = here::here("ignore", "data", "task_jeopardy_meta_states.csv"))
+
+mem_descriptions <- less_raw %>%
+  filter(trial_screen == "describe" & zone == "response") %>% 
+  select(subj_num, trial_num, question, resp)
+
+write_csv(mem_descriptions, file = here::here("ignore", "data", "task_jeopardy_meta_descriptions.csv"))

### 2021-04-26 R/clean_pretest.R

@@ -1,0 +1,16 @@
+require(tidyverse)
+require(magrittr)
+source(here::here("R", "utils_read_gorilla.R"))
+
+raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+  read_gorilla_data("task-4elo")
+
+less_raw <- raw %>% 
+  select(subj_num = "Participant Private ID",
+         category_num = "Zone Name",
+         category = "Response",
+         n_correct = "Reaction Time") %>% 
+  filter(startsWith(category_num, "category")) %>% 
+  mutate(category_num = as.integer(str_sub(category_num, start = -1L)))
+
+write_csv(less_raw, file = here::here("ignore", "data", "task_pretest.csv"))

### 2021-04-26 R/clean_q_posttask.R

@@ -1,0 +1,15 @@
+require(tidyverse)
+require(magrittr)
+source(here::here("R", "utils_read_gorilla.R"))
+
+raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+  read_gorilla_data("questionnaire-qdx5")
+
+less_raw <- raw %>% 
+  select(subj_num = `Participant Private ID`, q_key = `Question Key`, resp = Response) %>%
+  filter(!endsWith(q_key, "QUESTIONNAIRE")) %>% 
+  pivot_wider(names_from = q_key, values_from = resp) %>% 
+  rename_with(~str_replace(., "-", "_"), everything()) %>% 
+  mutate(across(ends_with("alreadyknew"), as.integer))
+
+write_csv(less_raw, file = here::here("ignore", "data", "q_posttask.csv"))

### 2021-04-26 R/clean_q_trivia_demos.R

@@ -1,0 +1,15 @@
+require(tidyverse)
+require(magrittr)
+source(here::here("R", "utils_read_gorilla.R"))
+
+raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+  read_gorilla_data("questionnaire-d6y6")
+
+less_raw <- raw %>% 
+  select(subj_num = `Participant Private ID`, q_key = `Question Key`, resp = Response) %>%
+  filter(!endsWith(q_key, "QUESTIONNAIRE")) %>% 
+  pivot_wider(names_from = q_key, values_from = resp) %>% 
+  rename_with(~str_replace(., "-", "_"), everything()) %>% 
+  mutate(across(c(starts_with("trivia"), ends_with("quantised")), as.integer))
+
+write_csv(less_raw, file = here::here("ignore", "data", "q_trivia_demos.csv"))

### 2021-04-26 R/clean_retrieval_facts.R

@@ -1,0 +1,75 @@
+require(tidyverse)
+require(magrittr)
+source(here::here("R", "utils_read_gorilla.R"))
+
+## reading in and cleaning ----
+
+raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+  read_gorilla_data("task-txhz")
+
+pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
+  select(-n_correct) %>%
+  pivot_wider(names_from = category_num, values_from = category, names_prefix = "category") %>%
+  mutate(categories = paste(category1, category2, sep = "_"))
+
+less_raw <- raw %>% 
+  select(subj_num = `Participant Private ID`,
+         group,
+         encoding_block,
+         group_trial_num = trial_num,
+         retrieval_trial_num = `Trial Number`,
+         retrieval_block = randomise_blocks,
+         trial_screen = `Screen Name`,
+         zone = `Zone Name`,
+         rt = `Reaction Time`,
+         resp = `Response`,
+         timeout = `Timed Out`,
+         starts_with("test_question"),
+         starts_with("test_answer")) %>%
+  filter(trial_screen == "recall") %>%
+  mutate(retrieval_trial_num = as.integer(retrieval_trial_num),
+         timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout)) %>%
+  filter(zone == "response") %>%
+  select(-c(trial_screen, zone)) %>% 
+  nest(data = -subj_num) %>% 
+  left_join(pretest, by = "subj_num") %>% 
+  mutate(data = map2(data, categories,
+                     ~.x %>% select(group,
+                                    group_trial_num,
+                                    retrieval_block,
+                                    retrieval_trial_num,
+                                    resp,
+                                    rt,
+                                    test_question = paste0("test_question.", .y),
+                                    test_answer = paste0("test_answer.", .y)))) %>%
+  unnest(data) %>% 
+  mutate(category = if_else(group == "academic", category1, category2)) %>% 
+  select(-c(category1, category2, categories)) %>%
+  mutate(acc_recall_rough = map2_lgl(resp, test_answer,
+                                     ~(grepl(.x, .y, ignore.case = TRUE) | grepl(.y, .x, ignore.case = TRUE)) %>% 
[…]

### 2021-04-26 R/clean_retrieval_pics.R

@@ -1,0 +1,53 @@
+require(tidyverse)
+require(magrittr)
+source(here::here("R", "utils_read_gorilla.R"))
+
+raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+  read_gorilla_data("task-3n9k")
+
+pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
+  select(-n_correct) %>%
+  pivot_wider(names_from = category_num, values_from = category, names_prefix = "category") %>%
+  mutate(categories = paste(category1, category2, sep = "_"))
+
+less_raw <- raw %>% 
+  select(subj_num = `Participant Private ID`,
+         group,
+         group_trial_num = trial_num,
+         trial_screen = `Screen Name`,
+         zone = `Zone Name`,
+         rt = `Reaction Time`,
+         resp = `Response`,
+         timeout = `Timed Out`,
+         encoding_pic = `counterbalance-mqv3`,
+         retrieval_pic = `counterbalance-ekxi`,
+         starts_with("pic_c"),
+         starts_with("pic_d")) %>% 
+  filter(trial_screen == "test") %>% 
+  mutate(across(c(group_trial_num, resp), as.integer),
+         timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout)) %>% 
+  nest(data = -c(subj_num, group, group_trial_num)) %>% 
+  # stuff to pull only the row of scale trials where the slider stopped moving
+  mutate(data = map(data, get_slider_rt)) %>%
+  unnest(data) %>% 
+  select(-c(trial_screen, zone)) %>% 
+  nest(data = -subj_num) %>% 
+  left_join(pretest, by = "subj_num") %>% 
+  mutate(data = map2(data, categories,
+                     ~.x %>% select(group,
+                                    group_trial_num,
+                                    ends_with("_pic"),
+                                    resp,
+                                    rt,
+                                    pic_c = paste0("pic_c.", .y),
+                                    pic_d = paste0("pic_d.", .y)))) %>%
+  unnest(data) %>% 
+  mutate(category = if_else(group == "academic", category1, category2),
+         pic_shown = if_else(retrieval_pic == "c", pic_c, pic_d),
+         resp_binary = if_else(resp > 50, 1L, 0L)) %>% 
+  separate(pic_shown, into = c("pic_shown", NA)) %>% 
[…]

### 2021-04-26 R/clean_retrieval_source.R

@@ -1,0 +1,45 @@
+require(tidyverse)
+require(magrittr)
+source(here::here("R", "utils_read_gorilla.R"))
+
+raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+  read_gorilla_data("task-1152")
+
+pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
+  select(-n_correct) %>%
+  pivot_wider(names_from = category_num, values_from = category, names_prefix = "category") %>%
+  mutate(categories = paste(category1, category2, sep = "_"))
+
+less_raw <- raw %>% 
+  select(subj_num = `Participant Private ID`,
+         group,
+         group_trial_num = trial_num,
+         trial_screen = `Screen Name`,
+         zone = `Zone Name`,
+         rt = `Reaction Time`,
+         resp = `Response`,
+         timeout = `Timed Out`,
+         starts_with("encoding_sentence")) %>% 
+  filter(trial_screen == "test") %>% 
+  mutate(across(c(group_trial_num, resp), as.integer),
+         timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout)) %>% 
+  nest(data = -c(subj_num, group, group_trial_num)) %>% 
+  # stuff to pull only the row of scale trials where the slider stopped moving
+  mutate(data = map(data, get_slider_rt)) %>%
+  unnest(data) %>% 
+  select(-c(trial_screen, zone)) %>% 
+  nest(data = -subj_num) %>% 
+  left_join(pretest, by = "subj_num") %>% 
+  mutate(data = map2(data, categories,
+                     ~.x %>% select(group,
+                                    group_trial_num,
+                                    resp,
+                                    rt,
+                                    encoding_sentence = paste0("encoding_sentence.", .y)))) %>%
+  unnest(data) %>% 
+  mutate(category = if_else(group == "academic", category1, category2),
+         encoding_block = if_else(group_trial_num <= 20, 0L, 1L),
+         resp_binary = if_else(resp > 50, 1L, 0L)) %>% 
+  select(-c(category1, category2, categories))
+
+write_csv(less_raw, file = here::here("ignore", "data", "task_retrieval_source.csv"))

### 2021-04-26 R/utils_read_gorilla.R
drop temp cols in get_slider_rt

@@ -8,7 +8,8 @@ get_slider_rt <- function (df) {
            resp_diff = c(diff(resp), NA_integer_),
            resp_diff = coalesce(resp_diff, 0L)) %>%
     # this SHOULD keep one row per trial and also keep no responses
-    filter(trial_num_within == min(trial_num_within[resp_diff == 0]))
+    filter(trial_num_within == min(trial_num_within[resp_diff == 0])) %>% 
+    select(-trial_num_within, -resp_diff)
   
   return (out)
 }

### 2021-04-26 R/make_spreadsheet_retrieval_facts.R
label retrieval chonks in comments

@@ -8,6 +8,7 @@ master_spreadsheet <- read_csv(here::here("stim_stuff", "master_spreadsheet_pars
 ## format spreadsheet ----
 
 retrieval_facts_order <- list(
+  # 1-4: same episodic same semantic
   tibble(randomise_blocks = 1L,
          block_trial_num = 1:5,
          group = rep("academic", 5),
@@ -24,6 +25,7 @@ retrieval_facts_order <- list(
          block_trial_num = 1:5,
          group = rep("nonacademic", 5),
          encoding_block = rep("late", 5)),
+  # 5-8: same episodic different semantic
   tibble(randomise_blocks = rep(5:6, each = 5),
          block_trial_num = rep(1:5, 2),
          group = rep(c("academic", "nonacademic"), 5),
@@ -32,6 +34,7 @@ retrieval_facts_order <- list(
          block_trial_num = rep(1:5, 2),
          group = rep(c("academic", "nonacademic"), 5),
          encoding_block = rep("late", 10)),
+  # 9-12: different episodic same semantic
   tibble(randomise_blocks = rep(9:10, each = 5),
          block_trial_num = rep(1:5, 2),
          group = rep("academic", 10),
@@ -40,6 +43,7 @@ retrieval_facts_order <- list(
          block_trial_num = rep(1:5, 2),
          group = rep("nonacademic", 10),
          encoding_block = rep(c("early", "late"), 5)),
+  # 12-16: different episodic different semantic
   tibble(randomise_blocks = rep(13:14, each = 5),
          block_trial_num = rep(1:5, 2),
          group = rep(c("academic", "nonacademic"), 5),

### 2021-04-26 R/exploration.Rmd
init data exploration

---
title: "JStudy exploratory data analysis"
author: "Monica Thieu"
date: "4/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(magrittr)
j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv"))
j_meta <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_states.csv"))
encoding <- read_csv(here::here("ignore", "data", "task_encoding.csv"))
r_facts <- read_csv(here::here("ignore", "data", "task_retrieval_facts.csv"))
r_pics <- read_csv(here::here("ignore", "data", "task_retrieval_pics.csv"))
r_source <- read_csv(here::here("ignore", "data", "task_retrieval_source.csv"))
q_demos  <- read_csv(here::here("ignore", "data", "q_trivia_demos.csv"))
q_posttask  <- read_csv(here::here("ignore", "data", "q_posttask.csv"))
```

## Trivia expertise

```{r}
j_recall %>% 
  group_by(subj_num) %>% 
  summarize(score = mean(acc_recall))
```

```{r}
j_recall %>% 
  mutate(acc_recall = as.integer(acc_recall),
         resp_conf = (resp_conf - 50) / 100) %>% 
  glm(acc_recall ~ resp_conf, family = "binomial", data = .) %>% 
  summary()
```

```{r}
j_recall %>% 
  group_by(subj_num) %>% 
  ggplot(aes(x = resp_conf, y = as.integer(acc_recall))) + 
  geom_point() + 
  geom_smooth(method = "glm", method.args = list(family = "binomial")) + 
  facet_wrap(~subj_num)
```

## Metamemory states

```{r}
j_meta %>%
  left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
  filter(acc_recall) %>% 
  ggplot(aes(x = factor(subj_num), fill = resp)) +
  geom_bar()
```

```{r}
j_meta %>%
  left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
  filter(acc_recall) %>% 
  count(subj_num, resp) %>% 
  group_by(subj_num) %>% 
  mutate(prob = n / sum(n)) %>% 
  ggplot(aes(x = factor(subj_num), y = prob, fill = resp)) +
  geom_col()
```
```{r}
j_meta %>%
  left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
  filter(!acc_recall) %>% 
  ggplot(aes(x = factor(subj_num), fill = resp)) +
  geom_bar()
```

### Museum task retrieval

```{r}
r_pics %>%
  ggplot(aes(x = resp, fill = factor(is_old))) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 20) + facet_wrap(~ subj_num)
```

```{r}
r_source %>%
  ggplot(aes(x = resp, fill = factor(encoding_block))) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 20) + facet_wrap(~ subj_num)
```

### Source helpage

```{r}
retrieval <- r_facts %>%
  select(subj_num, group, group_trial_num, retrieval_block, retrieval_trial_num, category, acc_recall, rt_recall = rt) %>% 
  left_join(r_pics %>%
              mutate(resp = resp - 50,
                     acc = if_else(is_old == resp_binary, abs(resp), -abs(resp))) %>%
              select(subj_num, group, group_trial_num, category, pic_is_old = is_old, acc_pic = acc, rt_pic = rt)) %>% 
  left_join(r_source %>%
              mutate(resp = resp - 50,
                     acc = if_else(encoding_block == resp_binary, abs(resp), -abs(resp))) %>%
              select(subj_num, group, group_trial_num, category, acc_source = acc, rt_source = rt)) %>%
  left_join(encoding %>% 
              select(subj_num, group, group_trial_num, category, interest = resp)) %>% 
  mutate(retrieval_block = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
                                     retrieval_block <= 8 ~ "ep_same_sem_diff",
                                     retrieval_block <= 12 ~ "ep_diff_sem_same",
                                     retrieval_block <= 16 ~ "ep_diff_sem_diff",
                                     TRUE ~ NA_character_))
```

```{r}
retrieval %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = interest, y = acc_recall)) + 
  geom_point() + 
  geom_smooth(method = "glm", method.args = list(family = "binomial")) + 
  facet_wrap(~subj_num)
```

```{r}
retrieval %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = acc_pic, y = acc_recall)) + 
  geom_point() + 
  geom_smooth(method = "glm", method.args = list(family = "binomial")) + 
  facet_wrap(~subj_num)
```

```{r}
retrieval %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = acc_source, y = acc_recall)) + 
  geom_point() + 
  geom_smooth(method = "glm", method.args = list(family = "binomial")) + 
  facet_wrap(~subj_num)
```

```{r}
retrieval %>% 
  ggplot(aes(x = interest, y = acc_source)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  facet_wrap(~subj_num)
```

```{r}
retrieval %>% 
  ggplot(aes(x = acc_source, y = acc_pic)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  facet_wrap(~subj_num)
```

### 2021-04-28 R/clean_retrieval_facts.R
calculate retrieval block manually

@@ -18,7 +18,6 @@ less_raw <- raw %>%
          encoding_block,
          group_trial_num = trial_num,
          retrieval_trial_num = `Trial Number`,
-         retrieval_block = randomise_blocks,
          trial_screen = `Screen Name`,
          zone = `Zone Name`,
          rt = `Reaction Time`,
@@ -36,7 +35,6 @@ less_raw <- raw %>%
   mutate(data = map2(data, categories,
                      ~.x %>% select(group,
                                     group_trial_num,
-                                    retrieval_block,
                                     retrieval_trial_num,
                                     resp,
                                     rt,
@@ -47,7 +45,13 @@ less_raw <- raw %>%
   select(-c(category1, category2, categories)) %>%
   mutate(acc_recall_rough = map2_lgl(resp, test_answer,
                                      ~(grepl(.x, .y, ignore.case = TRUE) | grepl(.y, .x, ignore.case = TRUE)) %>% 
-                                       coalesce(FALSE)))
+                                       coalesce(FALSE)),
+         encoding_is_late = if_else(group_trial_num <= 20, 0L, 1L)) %>% 
+  group_by(subj_num) %>% 
+  mutate(retrieval_block = rep(1:16, each = 5)) %>% 
+  group_by(subj_num, retrieval_block) %>% 
+  mutate(ep_is_same = if_else(length(unique(encoding_is_late)) == 1, 1L, 0L),
+         sem_is_same = if_else(length(unique(group)) == 1, 1L, 0L))
 
 ## scoring some by hand----
 

### 2021-04-28 R/exploration.Rmd
add timeseries graph by retrieval block

@@
 
-### Museum task retrieval
+## Museum task retrieval
 
@@
 retrieval <- r_facts %>%
-  select(subj_num, group, group_trial_num, retrieval_block, retrieval_trial_num, category, acc_recall, rt_recall = rt) %>% 
+  select(subj_num, group, group_trial_num, retrieval_block, ep_is_same, sem_is_same, retrieval_trial_num, category, acc_recall, rt_recall = rt) %>% 
   left_join(r_pics %>%
@@
               select(subj_num, group, group_trial_num, category, interest = resp)) %>% 
-  mutate(retrieval_block = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
+  mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
                                           retrieval_block <= 8 ~ "ep_same_sem_diff",
@@
                                           TRUE ~ NA_character_))
+```
+
+```{r}
+retrieval %>% 
+  ggplot(aes(x = retrieval_trial_num, y = acc_recall)) +
+  geom_rect(aes(x = NULL, y = NULL, xmin = xmin, xmax = xmax, fill = interaction(ep_is_same, sem_is_same)),
+            data = retrieval %>%
+              select(subj_num, retrieval_block, retrieval_trial_num, ep_is_same, sem_is_same) %>%
+              group_by(subj_num, retrieval_block) %>%
+              filter(retrieval_trial_num %in% range(retrieval_trial_num)) %>%
+              mutate(xtype = if_else(retrieval_trial_num == min(retrieval_trial_num), "xmin", "xmax")) %>%
+              ungroup() %>%
+              pivot_wider(names_from = xtype, values_from = retrieval_trial_num) %>% 
+              mutate(xmin = xmin - 0.5,
+                     xmax = xmax + 0.5),
+            ymin = 0, ymax = 1, alpha = 0.5) +
+  geom_line() +
+  geom_point(aes(color = retrieval_block)) +
+  scale_colour_viridis_b() +
+  facet_grid(subj_num ~ .)
+```
+
+```{r}
+retrieval %>% 
+  group_by(subj_num, ep_is_same, sem_is_same) %>% 
+  summarize(mean_acc = mean(acc_recall))
 ```

### 2021-05-07 R/clean_expertise.R
trim some non-alphanums before scoring

@@ -34,27 +34,39 @@ less_raw <- raw %>%
                           ~.x %>%
                             select(resp, rt, timeout) %>% 
                             rename_with(~paste0(., "_conf"), everything())),
-         recall = map(recall, ~.x %>%
+         recall = map(recall, ~.x %>% 
                         select(-zone) %>% 
-                        mutate(rt = if_else(!is.na(timeout), 15000, rt)) %>% 
-                        rename_with(~paste0(., "_recall"), c(resp, rt, timeout)))) %>%
+                        get_typing_rts() %>% 
+                        rename_with(~paste0(., "_recall"), c(resp, rt_start, rt_end, timeout)))) %>%
   unnest(c(recall, confidence)) %>% 
   mutate(acc_recall_rough = map2_lgl(resp_recall, answer,
-                                     ~(grepl(.x, .y, ignore.case = T) | grepl(.y, .x, ignore.case = T)) %>% 
-                                       coalesce(FALSE)))
+                                     function (a, b) {
+                                       # trim non alpha nums in response in case they make grepl yell
+                                       a <- str_remove_all(a, "[^a-zA-Z\\d\\s-]")
+                                       out <- (grepl(a, b, ignore.case = T) | grepl(b, a, ignore.case = T)) %>% 
+                                         coalesce(FALSE)
+                                       
+                                       return (out)
+                                     }
+                                     ))
 
 ## scoring some by hand----
 
-less_raw %>%
-  arrange(answer) %>%
-  select(subj_num, resp_recall, answer, acc_recall_rough, question, everything())
-
 scored <- less_raw %>% 
   mutate(acc_recall = case_when(
-    answer == "Andrea Bocelli" & grepl("Bocelli", resp_recall, ignore.case = T) ~ TRUE,
+    answer == "Andrea Bocelli" & grepl("Boccelli", resp_recall, ignore.case = T) ~ TRUE,
+    answer == "Andrea Bocelli" & grepl("vocelli", resp_recall, ignore.case = T) ~ TRUE,
     answer == "SF Giants" & grepl("Giants", resp_recall, ignore.case = T) ~ TRUE,
     answer == "Spanish-American War" & grepl("Spanish American", resp_recall, ignore.case = T) ~ TRUE,
+    answer == "Yosemite National Park" & grepl("Josemite", resp_recall, ignore.case = T) ~ TRUE,
[…]

### 2021-05-07 R/clean_retrieval_facts.R
start and end rt, trim some non-alphanums before scoring

@@ -30,6 +30,9 @@ less_raw <- raw %>%
          timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout)) %>%
   filter(zone == "response") %>%
   select(-c(trial_screen, zone)) %>% 
+  nest(data = -c(subj_num, retrieval_trial_num)) %>% 
+  mutate(data = map(data, get_typing_rts)) %>% 
+  unnest(data) %>% 
   nest(data = -subj_num) %>% 
   left_join(pretest, by = "subj_num") %>% 
   mutate(data = map2(data, categories,
@@ -37,15 +40,26 @@ less_raw <- raw %>%
                                     group_trial_num,
                                     retrieval_trial_num,
                                     resp,
-                                    rt,
+                                    rt_start,
+                                    rt_end,
                                     test_question = paste0("test_question.", .y),
                                     test_answer = paste0("test_answer.", .y)))) %>%
   unnest(data) %>% 
   mutate(category = if_else(group == "academic", category1, category2)) %>% 
   select(-c(category1, category2, categories)) %>%
   mutate(acc_recall_rough = map2_lgl(resp, test_answer,
-                                     ~(grepl(.x, .y, ignore.case = TRUE) | grepl(.y, .x, ignore.case = TRUE)) %>% 
-                                       coalesce(FALSE)),
+                                     function (a, b) {
+                                       # trim non alpha nums in response in case they make grepl yell
+                                       a <- str_remove_all(a, "[^a-zA-Z\\d\\s-']")
+                                       if (!is.na(a) & nchar(a) == 0) {
+                                         return (FALSE)
+                                       } else {
+                                         out <- (grepl(a, b, ignore.case = T) | grepl(b, a, ignore.case = T)) %>% 
+                                           coalesce(FALSE)
+                                         
+                                         return (out)
+                                       }
+                                     }),
          encoding_is_late = if_else(group_trial_num <= 20, 0L, 1L)) %>% 
   group_by(subj_num) %>% 
[…]

### 2021-05-07 R/clean_retrieval_pics.R
correctly get trial num, old and new task version

@@ -3,7 +3,7 @@ require(magrittr)
 source(here::here("R", "utils_read_gorilla.R"))
 
 raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
-  read_gorilla_data("task-3n9k")
+  read_gorilla_data("task-3n9k|task-cuj6")
 
 pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
   select(-n_correct) %>%
@@ -13,20 +13,21 @@ pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
 less_raw <- raw %>% 
   select(subj_num = `Participant Private ID`,
          group,
-         group_trial_num = trial_num,
+         trial_num,
          trial_screen = `Screen Name`,
          zone = `Zone Name`,
          rt = `Reaction Time`,
          resp = `Response`,
          timeout = `Timed Out`,
          encoding_pic = `counterbalance-mqv3`,
-         retrieval_pic = `counterbalance-ekxi`,
+         retrieval_pic_oldnew = `counterbalance-ekxi`,
+         retrieval_pic_2afc = `randomiser-snec`,
          starts_with("pic_c"),
          starts_with("pic_d")) %>% 
   filter(trial_screen == "test") %>% 
-  mutate(across(c(group_trial_num, resp), as.integer),
+  mutate(across(c(trial_num, resp), as.integer),
          timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout)) %>% 
-  nest(data = -c(subj_num, group, group_trial_num)) %>% 
+  nest(data = -c(subj_num, group, trial_num)) %>% 
   # stuff to pull only the row of scale trials where the slider stopped moving
   mutate(data = map(data, get_slider_rt)) %>%
   unnest(data) %>% 
@@ -35,19 +36,37 @@ less_raw <- raw %>%
   left_join(pretest, by = "subj_num") %>% 
   mutate(data = map2(data, categories,
                      ~.x %>% select(group,
-                                    group_trial_num,
-                                    ends_with("_pic"),
+                                    trial_num,
+                                    contains("_pic"),
                                     resp,
                                     rt,
[…]

### 2021-05-07 R/clean_retrieval_source.R
resp is now acc-signed

@@ -39,7 +39,8 @@ less_raw <- raw %>%
   unnest(data) %>% 
   mutate(category = if_else(group == "academic", category1, category2),
          encoding_block = if_else(group_trial_num <= 20, 0L, 1L),
-         resp_binary = if_else(resp > 50, 1L, 0L)) %>% 
+         resp = if_else(encoding_block == 1, resp - 50, -(resp - 50)),
+         resp_binary = if_else(resp > 0, 1L, 0L)) %>% 
   select(-c(category1, category2, categories))
 
 write_csv(less_raw, file = here::here("ignore", "data", "task_retrieval_source.csv"))

### 2021-05-07 R/utils_read_gorilla.R
add get_typing_rts

@@ -1,6 +1,24 @@
 require(tidyverse)
 require(magrittr)
 
+get_typing_rts <- function (df) {
+  out <- df %>% 
+    mutate(timeout = if_else(any(!is.na(timeout)), 1L, NA_integer_))
+  if (nrow(df) > 1) {
+    out %<>% 
+      mutate(rt_type = c("start", "end"), resp = tail(resp, 1)) %>%
+      pivot_wider(names_from = rt_type, values_from = rt, names_prefix = "rt_")
+  } else {
+    out %<>%
+      rename(rt_end = rt) %>% 
+      mutate(rt_start = NA_real_)
+  }
+  out %<>% 
+    mutate(rt_end = if_else(!is.na(timeout), 15000, rt_end))
+  
+  return (out)
+}
+
 get_slider_rt <- function (df) {
   # stuff to pull only the row of scale trials where the slider stopped moving
   out <- df %>% 

### 2021-05-07 R/exploration.Rmd
make it into xaringan and nice ish

--- 2021-04-26 R/exploration.Rmd
@@
 title: "JStudy exploratory data analysis"
-author: "Monica Thieu"
-date: "4/25/2021"
-output: html_document
+subtitle: "with xaringan"
+author: "Monica Thieu & Lauren Wilkins"
+institute: "Columbia University Dept of Psychology"
+date: "`r Sys.Date()`"
+output:
+  xaringan::moon_reader:
+    lib_dir: libs
+    nature:
+      highlightStyle: github
+      highlightLines: true
+      countIncrementalSlides: false
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE, dev = "svglite", message = FALSE, warning = FALSE, fig.asp = 3/4)
 require(tidyverse)
@@
 j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv"))
-j_meta <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_states.csv"))
-encoding <- read_csv(here::here("ignore", "data", "task_encoding.csv"))
-r_facts <- read_csv(here::here("ignore", "data", "task_retrieval_facts.csv"))
-r_pics <- read_csv(here::here("ignore", "data", "task_retrieval_pics.csv"))
-r_source <- read_csv(here::here("ignore", "data", "task_retrieval_source.csv"))
-q_demos  <- read_csv(here::here("ignore", "data", "q_trivia_demos.csv"))
+
+j_exp <- j_recall %>% 
+  group_by(subj_num) %>% 
+  summarize(j_score = mean(acc_recall))
+
+j_recall %<>%
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+
+j_meta <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_states.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+encoding <- read_csv(here::here("ignore", "data", "task_encoding.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+r_facts <- read_csv(here::here("ignore", "data", "task_retrieval_facts.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+r_pics_oldnew <- read_csv(here::here("ignore", "data", "task_retrieval_pics_oldnew.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+r_pics_2afc <- read_csv(here::here("ignore", "data", "task_retrieval_pics.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+r_source <- read_csv(here::here("ignore", "data", "task_retrieval_source.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+q_demos  <- read_csv(here::here("ignore", "data", "q_trivia_demos.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
 q_posttask  <- read_csv(here::here("ignore", "data", "q_posttask.csv"))
@@
 
-## Trivia expertise
+class: inverse, middle
+
+# Trivia expertise assessment
+
+---
+
+```{r}
+q_demos %>% 
+  ggplot(aes(x = trivia_skill_self, y = j_score)) +
+  geom_point(size = 3) +
+  labs(x = "Self-reported trivia expertise (relative to 'average person')",
+       y = "Expertise score on Jeopardy audition test") +
+  theme_bw()
+```
+
+---
+
+## Trivia recall by confidence
 
@@
 j_recall %>% 
-  group_by(subj_num) %>% 
-  summarize(score = mean(acc_recall))
+  ggplot(aes(x = resp_conf, y = as.integer(acc_recall), color = j_score, fill = j_score)) + 
+  geom_jitter(alpha = 0.3, height = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
+  theme_bw()
 ```
 
-```{r}
-j_recall %>% 
-  mutate(acc_recall = as.integer(acc_recall),
-         resp_conf = (resp_conf - 50) / 100) %>% 
-  glm(acc_recall ~ resp_conf, family = "binomial", data = .) %>% 
-  summary()
-```
+---
 
-```{r}
-j_recall %>% 
-  group_by(subj_num) %>% 
-  ggplot(aes(x = resp_conf, y = as.integer(acc_recall))) + 
-  geom_point() + 
-  geom_smooth(method = "glm", method.args = list(family = "binomial")) + 
-  facet_wrap(~subj_num)
-```
-
-## Metamemory states
+## Metamemory state counts
 
@@
   left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
-  filter(acc_recall) %>% 
-  ggplot(aes(x = factor(subj_num), fill = resp)) +
-  geom_bar()
+  mutate(acc_recall = recode(as.character(acc_recall),
+                             `FALSE` = "incorrect",
+                             `TRUE` = "correct")) %>% 
+  ggplot(aes(x = subj_num, fill = resp)) +
+  geom_bar() +
+  scale_x_discrete(guide = guide_axis(angle = 30)) +
+  facet_grid(~acc_recall) +
+  labs(x = "Participant", y = "# facts labeled with that memory state", fill = "Memory state") +
+  theme_bw()
 ```
+
+---
+
+## Metamemory state relative percentages
 
@@
   left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
-  filter(acc_recall) %>% 
-  count(subj_num, resp) %>% 
-  group_by(subj_num) %>% 
+  mutate(acc_recall = recode(as.character(acc_recall),
+                             `FALSE` = "incorrect",
+                             `TRUE` = "correct")) %>% 
+  count(subj_num, acc_recall, resp) %>% 
+  group_by(subj_num, acc_recall) %>% 
   mutate(prob = n / sum(n)) %>% 
-  ggplot(aes(x = factor(subj_num), y = prob, fill = resp)) +
-  geom_col()
-```
-```{r}
-j_meta %>%
-  left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
-  filter(!acc_recall) %>% 
-  ggplot(aes(x = factor(subj_num), fill = resp)) +
-  geom_bar()
+  ggplot(aes(x = subj_num, y = prob, fill = resp)) +
+  geom_col() +
+  scale_x_discrete(guide = guide_axis(angle = 30)) +
+  facet_grid(~acc_recall) +
+  labs(x = "Participant", y = "Percent facts labeled with that memory state", fill = "Memory state") +
+  theme_bw()
 ```
 
-### Museum task retrieval
+---
+
+class: inverse, middle
+
+# Museum task retrieval
+
+---
+
+## Fact recall as a function of question order/chunk type
 
 ```{r}
-r_pics %>%
-  ggplot(aes(x = resp, fill = factor(is_old))) +
-  geom_histogram(position = "identity", alpha = 0.5, bins = 20) + facet_wrap(~ subj_num)
+r_facts %>% 
+  ggplot(aes(x = retrieval_trial_num, y = acc_recall)) +
+  geom_rect(aes(x = NULL, y = NULL, xmin = xmin, xmax = xmax, fill = interaction(ep_is_same, sem_is_same)),
+            data = r_facts %>%
+              mutate(ep_is_same = recode(ep_is_same,
+                                         `0` = "ep diff",
+                                         `1` = "ep same"),
+                     sem_is_same = recode(sem_is_same,
+                                          `0` = "sem diff",
+                                          `1` = "sem same")) %>% 
+              select(subj_num, retrieval_block, retrieval_trial_num, ep_is_same, sem_is_same) %>%
+              group_by(subj_num, retrieval_block) %>%
+              filter(retrieval_trial_num %in% range(retrieval_trial_num)) %>%
+              mutate(xtype = if_else(retrieval_trial_num == min(retrieval_trial_num), "xmin", "xmax")) %>%
+              ungroup() %>%
+              pivot_wider(names_from = xtype, values_from = retrieval_trial_num) %>% 
+              mutate(xmin = xmin - 0.5,
+                     xmax = xmax + 0.5),
+            ymin = 0, ymax = 1, alpha = 0.5) +
+  geom_line() +
+  geom_point() +
+  scale_colour_viridis_b() +
+  scale_y_continuous(n.breaks = 3) +
+  facet_grid(subj_num ~ .) +
+  labs(x = "Fact recall trial (beginning to end)", y = "Fact recall accuracy", fill = "Chunk type") +
+  theme_bw()
+```
+
+---
+
+## Fact recall by chunk type
+
+```{r}
+r_facts %>% 
+  mutate(ep_is_same = recode(ep_is_same,
+                                         `0` = "ep diff",
+                                         `1` = "ep same"),
+                     sem_is_same = recode(sem_is_same,
+                                          `0` = "sem diff",
+                                          `1` = "sem same")) %>% 
+  group_by(subj_num, j_score, ep_is_same, sem_is_same) %>% 
+  summarize(mean_acc = mean(acc_recall)) %>% 
+  ggplot(aes(x = interaction(ep_is_same, sem_is_same), y = mean_acc,
+             group = subj_num,
+             color = j_score)) +
+  geom_line() +
+  geom_point() +
+  scale_x_discrete(guide = guide_axis(angle = 30)) +
+  scale_color_viridis_c() +
+  labs(x = "Chunk type", y = "Percent facts correctly recalled", color = "Expertise score") +
+  theme_bw()
+```
+
+---
+
+## Photo recognition
+
+Old setup: A-B' old-new recognition with similar lures as foils
+
+```{r}
+r_pics_oldnew %>%
+  ggplot(aes(x = factor(subj_num), y = resp, fill = factor(is_old))) +
+  geom_hline(yintercept = 0, linetype = "dotted") +
+  geom_boxplot() +
+  labs(x = "Participant", y = "Accuracy with confidence (positive = correct)") +
+  theme_bw()
 ```
@@
 ```{r}
+r_pics_oldnew %>%
+  mutate(say_old = case_when(is_old == 0 & resp_binary == 1 ~ 0L,
+                             is_old == 0 & resp_binary == 0 ~ 1L,
+                             is_old == 1 & resp_binary == 0 ~ 0L,
+                             is_old == 1 & resp_binary == 1 ~ 1L,
+                             TRUE ~ NA_integer_)) %>% 
+  nest(data = -subj_num) %>% 
+  mutate(coefs = map(data, ~glm(say_old ~ is_old, family = binomial(link = "logit"), data = .) %>% 
+                       broom::tidy())) %>% 
+  select(subj_num, coefs) %>% 
+  unnest(coefs) %>% 
+  filter(term == "is_old")
+```
+
+---
+
+### Current setup: A-A' 2AFC with similar lure
+
+```{r}
+r_pics_2afc %>%
+  ggplot(aes(x = factor(subj_num), y = resp, color = j_score)) +
+  geom_hline(yintercept = 0, linetype = "dotted") +
+  geom_boxplot() +
+  scale_colour_viridis_c() +
+  guides(color = FALSE) +
+  labs(x = "Participant", y = "Accuracy with confidence (positive = correct)") +
+  theme_bw()
+```
+
+---
+
+### Source memory for which museum
+
+```{r}
 r_source %>%
-  ggplot(aes(x = resp, fill = factor(encoding_block))) +
-  geom_histogram(position = "identity", alpha = 0.5, bins = 20) + facet_wrap(~ subj_num)
+  ggplot(aes(x = factor(subj_num), y = resp, color = j_score)) +
+  geom_hline(yintercept = 0, linetype = "dotted") +
+  geom_boxplot() +
+  scale_colour_viridis_c() +
+  guides(color = FALSE) +
+  labs(x = "Participant", y = "Accuracy with confidence (positive = correct)") +
+  theme_bw()
 ```
+
+---
 
@@
 retrieval <- r_facts %>%
-  select(subj_num, group, group_trial_num, retrieval_block, retrieval_trial_num, category, acc_recall, rt_recall = rt) %>% 
-  left_join(r_pics %>%
-              mutate(resp = resp - 50,
-                     acc = if_else(is_old == resp_binary, abs(resp), -abs(resp))) %>%
-              select(subj_num, group, group_trial_num, category, pic_is_old = is_old, acc_pic = acc, rt_pic = rt)) %>% 
+  select(subj_num, j_score, group, group_trial_num, retrieval_block, ep_is_same, sem_is_same, retrieval_trial_num, category, acc_recall, rt_start_recall = rt_start, rt_end_recall = rt_end) %>% 
+  left_join(r_pics_oldnew %>%
+              select(subj_num, group, group_trial_num, category, pic_is_old = is_old, resp_pic = resp, rt_pic = rt) %>% 
+              bind_rows(r_pics_2afc %>% 
+                          select(subj_num, group, group_trial_num, category, resp_pic = resp, rt_pic = rt))) %>% 
   left_join(r_source %>%
-              mutate(resp = resp - 50,
-                     acc = if_else(encoding_block == resp_binary, abs(resp), -abs(resp))) %>%
-              select(subj_num, group, group_trial_num, category, acc_source = acc, rt_source = rt)) %>%
+              select(subj_num, group, group_trial_num, category, resp_source = resp, rt_source = rt)) %>%
   left_join(encoding %>% 
               select(subj_num, group, group_trial_num, category, interest = resp)) %>% 
-  mutate(retrieval_block = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
+  mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
                                           retrieval_block <= 8 ~ "ep_same_sem_diff",
@@
 
+---
+
+### Does successful photo retrieval predict successful fact retrieval?
+
 ```{r}
@@
   mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
-  ggplot(aes(x = interest, y = acc_recall)) + 
+  ggplot(aes(x = resp_pic, y = acc_recall, color = j_score, fill = j_score)) + 
+  geom_jitter(alpha = 0.3, height = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Photo recognition accuracy", y = "Fact recall accuracy (generous)") +
+  theme_bw()
+```
+
+---
+
+### Does successful source retrieval predict successful fact retrieval?
+
+```{r}
+retrieval %>% 
+  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
+  ggplot(aes(x = resp_source, y = acc_recall, color = j_score, fill = j_score)) + 
+  geom_jitter(alpha = 0.3, height = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Source recognition accuracy", y = "Fact recall accuracy (generous)") +
+  theme_bw()
+```
+
+---
+
+### Does interest at encoding predict successful _fact_ retrieval?
+
+```{r}
+retrieval %>% 
+  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
+  ggplot(aes(x = interest, y = acc_recall, color = j_score, fill = j_score)) + 
+  geom_jitter(alpha = 0.3, height = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Interest in fact at encoding", y = "Fact recall accuracy (generous)") +
+  theme_bw()
+```
+
+---
+
+### Does interest at encoding predict successful _photo_ retrieval?
+
+```{r}
+retrieval %>% 
+  ggplot(aes(x = interest, y = resp_pic, color = j_score, fill = j_score)) + 
   geom_point() + 
-  geom_smooth(method = "glm", method.args = list(family = "binomial")) + 
-  facet_wrap(~subj_num)
+  geom_smooth(method = "lm") + 
+  facet_wrap(~subj_num) +
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Interest in fact at encoding", y = "Photo recognition accuracy") +
+  theme_bw()
+```
+
+---
+
+### Does interest at encoding predict successful _source_ retrieval?
+
+```{r}
+retrieval %>% 
+  ggplot(aes(x = interest, y = resp_source, color = j_score, fill = j_score)) + 
+  geom_point() + 
+  geom_smooth(method = "lm") + 
+  facet_wrap(~subj_num) +
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Interest in fact at encoding", y = "Source recognition accuracy") +
+  theme_bw()
+```
+
+---
+
+### Does successful _source_ retrieval predict successful _photo_ retrieval?
+
+```{r}
+retrieval %>% 
+  ggplot(aes(x = resp_source, y = resp_pic, color = j_score, fill = j_score)) + 
+  geom_point() + 
+  geom_smooth(method = "lm") + 
+  facet_wrap(~subj_num) +
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Source recognition accuracy", y = "Photo recognition accuracy") +
+  theme_bw()
+```
+
+---
+
+```{r}
+retrieval %>% 
+  ggplot(aes(x = log(rt_pic), y = resp_pic)) + 
+  geom_point() + 
+  geom_smooth(method = "lm") + 
+  facet_wrap(~subj_num, scales = "free_x")
 ```
@@
 retrieval %>% 
-  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
-  ggplot(aes(x = acc_pic, y = acc_recall)) + 
-  geom_point() + 
-  geom_smooth(method = "glm", method.args = list(family = "binomial")) + 
-  facet_wrap(~subj_num)
-```
-
-```{r}
-retrieval %>% 
-  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
-  ggplot(aes(x = acc_source, y = acc_recall)) + 
-  geom_point() + 
-  geom_smooth(method = "glm", method.args = list(family = "binomial")) + 
-  facet_wrap(~subj_num)
-```
-
-```{r}
-retrieval %>% 
-  ggplot(aes(x = interest, y = acc_source)) + 
+  ggplot(aes(x = log(rt_source), y = resp_source)) + 
   geom_point() + 
   geom_smooth(method = "lm") + 
-  facet_wrap(~subj_num)
+  facet_wrap(~subj_num, scales = "free_x")
 ```
-
-```{r}
-retrieval %>% 
-  ggplot(aes(x = acc_source, y = acc_pic)) + 
-  geom_point() + 
-  geom_smooth(method = "lm") + 
-  facet_wrap(~subj_num)
-```

### 2021-05-12 slides/exploration.Rmd
xaringan prezzie folder (with ignored figs)

--- 2021-05-07 R/exploration.Rmd
@@
 ---
-title: "JStudy exploratory data analysis"
-subtitle: "with xaringan"
+title: "Exploratory data analysis"
+subtitle: "J-Study"
 author: "Monica Thieu & Lauren Wilkins"
@@
   xaringan::moon_reader:
+    css: ["theme.css", "fonts.css"]
     lib_dir: libs
@@
 j_meta <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_states.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+j_meta_desc <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_descriptions.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
@@
 
+### Do Ps accurately assess their own trivia skill?
+
 ```{r}
@@
 
-## Trivia recall by confidence
+### Trivia recall by confidence
 
@@
 
-## Metamemory state counts
+### Metamemory state counts
 
@@
 
-## Metamemory state relative percentages
+### Metamemory state relative percentages
 
@@
 
+### Metamemory descriptions: Guess
+
+```{r, results = "asis"}
+j_meta_desc %>%
+  filter(question == "Guess") %>% 
+  arrange(subj_num) %>% 
+  pull(resp) %>% 
+  paste0(">", .) %>% 
+  cat(sep = "\n\n")
+```
+
+---
+
+### Metamemory descriptions: Just Know
+
+```{r, results = "asis"}
+j_meta_desc %>%
+  filter(question == "Just Know") %>% 
+  arrange(subj_num) %>% 
+  pull(resp) %>% 
+  paste0(">", .) %>% 
+  cat(sep = "\n\n")
+```
+
+---
+
+### Metamemory descriptions: Related Memory
+
+```{r, results = "asis"}
+j_meta_desc %>%
+  filter(question == "Related Memory") %>% 
+  arrange(subj_num) %>% 
+  pull(resp) %>% 
+  paste0(">", .) %>% 
+  cat(sep = "\n\n")
+```
+
+---
+
+### Metamemory descriptions: Learning Memory
+
+```{r, results = "asis"}
+j_meta_desc %>%
+  filter(question == "Learning Memory") %>% 
+  arrange(subj_num) %>% 
+  pull(resp) %>% 
+  paste0(">", .) %>% 
+  cat(sep = "\n\n")
+```
+
+---
+
 class: inverse, middle
@@
 
-## Fact recall as a function of question order/chunk type
+### Fact recall by question order/chunk type
 
@@
 
-## Fact recall by chunk type
+### Fact recall by chunk type
 
@@
 
-## Photo recognition
+### Photo recognition
 
@@
 
-### Current setup: A-A' 2AFC with similar lure
+### Photo recognition
+
+Current setup: A-A' 2AFC with similar lure
 
@@
 
-### Source helpage
+class: inverse, middle
+
+# Retrieval between-task relationships
 
@@
 
-### Does successful photo retrieval predict successful fact retrieval?
+### Does _photo_ retrieval predict _fact_ retrieval?
 
@@
 
-### Does successful source retrieval predict successful fact retrieval?
+### Does _source_ retrieval predict _fact_ retrieval?
 
@@
 
-### Does interest at encoding predict successful _fact_ retrieval?
+### Does _source_ retrieval predict _photo_ retrieval?
+
+```{r}
+retrieval %>% 
+  ggplot(aes(x = resp_source, y = resp_pic, color = j_score, fill = j_score)) + 
+  geom_point() + 
+  geom_smooth(method = "lm") + 
+  facet_wrap(~subj_num) +
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Source recognition accuracy", y = "Photo recognition accuracy") +
+  theme_bw()
+```
+
+---
+
+### Does interest at encoding predict _fact_ retrieval?
 
@@
 
-### Does interest at encoding predict successful _photo_ retrieval?
+### Does interest at encoding predict _photo_ retrieval?
 
@@
 
-### Does interest at encoding predict successful _source_ retrieval?
+### Does interest at encoding predict _source_ retrieval?
 
@@
 
-### Does successful _source_ retrieval predict successful _photo_ retrieval?
+class: inverse, middle
 
-```{r}
-retrieval %>% 
-  ggplot(aes(x = resp_source, y = resp_pic, color = j_score, fill = j_score)) + 
-  geom_point() + 
-  geom_smooth(method = "lm") + 
-  facet_wrap(~subj_num) +
-  scale_color_viridis_c() +
-  scale_fill_viridis_c() +
-  labs(x = "Source recognition accuracy", y = "Photo recognition accuracy") +
-  theme_bw()
-```
+# STOP! Dirty graphs ahead
 

### 2021-06-30 R/clean_demos_ids.R
init file

@@ -1,0 +1,13 @@
+require(tidyverse)
+require(magrittr)
+source(here::here("R", "utils_read_gorilla.R"))
+
+raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
+  read_gorilla_data("questionnaire-4vcn")
+
+less_raw <- raw %>% 
+  select(subj_num = `Participant Private ID`, q_key = `Question Key`, resp = Response) %>%
+  filter(!endsWith(q_key, "QUESTIONNAIRE")) %>% 
+  pivot_wider(names_from = q_key, values_from = resp)
+
+write_csv(less_raw, file = here::here("ignore", "data", "demos_ids.csv"))

### 2021-06-30 R/clean_encoding.R
all scoring now done in semi-interactive scripts

@@ -2,7 +2,7 @@ require(tidyverse)
 require(magrittr)
 source(here::here("R", "utils_read_gorilla.R"))
 
-raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
   read_gorilla_data("task-ujps|task-wckg")
 
 pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
@@ -19,7 +19,11 @@ less_raw <- raw %>%
          rt = `Reaction Time`,
          resp = `Response`,
          starts_with("encoding_sentence")) %>% 
-  filter(trial_screen == "fact", zone == "slider") %>%
+  filter((trial_screen == "fact" & zone == "slider") | trial_screen == "already_knew") %>%
+  nest(data = -c(subj_num, group, group_trial_num, trial_screen)) %>%
+  pivot_wider(names_from = trial_screen, values_from = data) %>% 
+  mutate(already_knew = map_chr(already_knew, ~.x$resp)) %>% 
+  unnest(fact) %>% 
   mutate(# Should catch slider trials where the slider was never clicked
          # bc I think timeout will still be true if submitResp was never clicked but the slider was moved
          resp = if_else(zone == "scale" & rt >= 34900, NA_character_, resp),
@@ -29,7 +33,7 @@ less_raw <- raw %>%
   mutate(data = map(data, get_slider_rt)) %>%
   unnest(data) %>% 
   # this SHOULD keep one row per trial and also keep no responses
-  select(-c(trial_screen, zone)) %>% 
+  select(-zone) %>% 
   nest(data = -subj_num) %>% 
   left_join(pretest, by = "subj_num") %>% 
   mutate(data = map2(data, categories,
@@ -37,6 +41,7 @@ less_raw <- raw %>%
                                     group,
                                     resp,
                                     rt,
+                                    already_knew,
                                     encoding_sentence = paste0("encoding_sentence.", .y)))) %>%
   unnest(data) %>% 
   mutate(category = if_else(group == "academic", category1, category2)) %>% 

### 2021-06-30 R/clean_expertise.R

@@ -4,7 +4,7 @@ source(here::here("R", "utils_read_gorilla.R"))
 
 ## reading in and cleaning ----
 
-raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
   read_gorilla_data("task-v9u2")
 
 less_raw <- raw %>% 
@@ -22,7 +22,22 @@ less_raw <- raw %>%
          timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout),
          # Should catch slider trials where the slider was never clicked
          # bc I think timeout will still be true if submitResp was never clicked but the slider was moved
-         resp = if_else(zone == "scale" & rt >= 14900, NA_character_, resp)) %>%
+         resp = if_else(zone == "scale" & rt >= 14900, NA_character_, resp),
+         # Fix the typo for the older subjects so the question text doesn't appear repeated
+         question = str_replace(question, "1890", "1899"),
+         answer = if_else(answer == "SF Giants", "San Francisco Giants", answer)) %>%
+  nest(data = -c(subj_num, trial_num, trial_screen)) %>% 
+  # patch in a "response" row if fully timed out
+  mutate(data = map(data,
+                    function (x) {
+                      if (nrow(x) == 1) {
+                        if (x$zone == "timelimit") {
+                          x$zone <- "response"
+                        }
+                      }
+                      return (x)
+                    })) %>% 
+  unnest(data) %>% 
   filter(!(zone %in% c("continueButton", "timelimit"))) %>%
   # stuff to pull only the row of scale trials where the slider stopped moving
   nest(data = -c(subj_num, trial_num, trial_screen)) %>%
@@ -38,35 +53,6 @@ less_raw <- raw %>%
                         select(-zone) %>% 
                         get_typing_rts() %>% 
                         rename_with(~paste0(., "_recall"), c(resp, rt_start, rt_end, timeout)))) %>%
-  unnest(c(recall, confidence)) %>% 
-  mutate(acc_recall_rough = map2_lgl(resp_recall, answer,
-                                     function (a, b) {
-                                       # trim non alpha nums in response in case they make grepl yell
-                                       a <- str_remove_all(a, "[^a-zA-Z\\d\\s-]")
[…]

### 2021-06-30 R/score_expertise.R

@@ -1,0 +1,116 @@
+## setup ----
+
+require(tidyverse)
+require(magrittr)
+
+unscored <- read_csv(here::here("ignore", "data", "task_jeopardy_recall_unscored.csv"))
+
+if (FALSE) {
+  googledrive::drive_download(file = as_id("1e7R4CSDjSA5trC820aiwUbe7szjn7DTfMiZPI4my8Rk"),
+                              path = here::here("stim_stuff", "jeopardy_spreadsheet.csv"),
+                              type = "csv",
+                              overwrite = TRUE)
+}
+
+questions <- read_csv(here::here("stim_stuff", "jeopardy_spreadsheet.csv")) %>% 
+  filter(use_question == 1) %>% 
+  select(question, answer, answer_short) %>% 
+  mutate(answer_short = coalesce(answer_short, answer))
+
+
+## grepl scoring first pass ----
+
+scored <- unscored %>% 
+  left_join(questions) %>% 
+  mutate(acc_recall_grepl_strict = map2_lgl(resp_recall, answer,
+                                            function (a, b) {
+                                              # trim non alpha nums in response in case they make grepl yell
+                                              a <- str_remove_all(a, "[^a-zA-Z\\d\\s-]")
+                                              if (is.na(a) | nchar(a) == 0) return (FALSE)
+                                              out <- (grepl(a, b, ignore.case = T) | grepl(b, a, ignore.case = T))
+                                              
+                                              return (out)
+                                            }),
+         # Particular very common misspellings that get special treatment
+         acc_recall_grepl_strict = case_when(answer == "Spanish-American War" & grepl("spanish american", resp_recall, ignore.case = T) ~ TRUE,
+                                             answer == "Andrea Bocelli" & grepl("andrea boccelli", resp_recall, ignore.case = T) ~ TRUE,
+                                             answer == "distillation" & startsWith(tolower(resp_recall), "distill") ~ TRUE,
+                                             answer == "uranium" & grepl("plutonium", resp_recall, ignore.case = T) ~ FALSE,
+                                             TRUE ~ acc_recall_grepl_strict),
+         acc_recall_grepl_fuzzy = map2_lgl(resp_recall, answer,
[…]

### 2021-06-30 R/score_retrieval_facts.R

@@ -1,0 +1,125 @@
+## setup ----
+
+require(tidyverse)
+require(magrittr)
+
+unscored <- read_csv(here::here("ignore", "data", "task_retrieval_facts_unscored.csv"))
+
+## grepl scoring first pass----
+
+scored <- unscored %>% 
+  mutate(acc_recall_grepl_strict = map2_lgl(resp, test_answer,
+                                            function (a, b) {
+                                              # trim non alpha nums in response in case they make grepl yell
+                                              a <- str_remove_all(a, "[^a-zA-Z\\d\\s-]")
+                                              b <- str_remove_all(b, "[^a-zA-Z\\d\\s-]")
+                                              if (is.na(a) | nchar(a) == 0) return (FALSE)
+                                              out <- (grepl(a, b, ignore.case = T) | grepl(b, a, ignore.case = T))
+                                              return (out)
+                                            }),
+         # Particular very common misspellings or key short phrases that get special treatment
+         acc_recall_grepl_strict = case_when(
+           nchar(str_remove_all(resp, "[^a-zA-Z\\d\\s-]")) / nchar(test_answer) <= 0.25 ~ FALSE,
+           group_trial_num == 1 & category == "gems" & grepl("cleav", resp, ignore.case = T) ~ TRUE,
+           group_trial_num == 13 & category == "musi" & tolower(resp) == "hurdy gurdy" ~ TRUE,
+           group_trial_num == 37 & category == "cook" & grepl("orchid", resp, ignore.case = T) ~ TRUE,
+           group_trial_num == 38 & category == "cook" & grepl("hen-of-the-woods", resp, ignore.case = T) ~ TRUE,
+           group_trial_num == 21 & category == "dino" & grepl("medullary", resp, ignore.case = T) ~ TRUE,
+           group_trial_num == 36 & category == "dino" & grepl("saw fish", resp, ignore.case = T) ~ TRUE,
+           TRUE ~ acc_recall_grepl_strict
+         ),
+         acc_recall_grepl_fuzzy = map2_lgl(resp, test_answer,
+                                           function (a, b) {
+                                             # trim non alpha nums so they don't artificially pad the resp length
[…]

### 2021-06-30 R/clean_metamemory.R
updated for new folder structure for real data

@@ -2,7 +2,7 @@ require(tidyverse)
 require(magrittr)
 source(here::here("R", "utils_read_gorilla.R"))
 
-raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
   read_gorilla_data("task-wlkb")
 
 less_raw <- raw %>% 
@@ -14,7 +14,9 @@ less_raw <- raw %>%
          resp = `Response`,
          timeout = `Timed Out`,
          question,
-         answer)
+         answer) %>% 
+  mutate(question = str_replace(question, "1890", "1899"),
+         answer = if_else(answer == "SF Giants", "San Francisco Giants", answer))
 
 mem_states <- less_raw %>%
   filter(trial_screen == "recall") %>% 

### 2021-06-30 R/clean_pretest.R

@@ -2,7 +2,7 @@ require(tidyverse)
 require(magrittr)
 source(here::here("R", "utils_read_gorilla.R"))
 
-raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
   read_gorilla_data("task-4elo")
 
 less_raw <- raw %>% 

### 2021-06-30 R/clean_q_posttask.R

@@ -2,14 +2,13 @@ require(tidyverse)
 require(magrittr)
 source(here::here("R", "utils_read_gorilla.R"))
 
-raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
   read_gorilla_data("questionnaire-qdx5")
 
 less_raw <- raw %>% 
   select(subj_num = `Participant Private ID`, q_key = `Question Key`, resp = Response) %>%
   filter(!endsWith(q_key, "QUESTIONNAIRE")) %>% 
   pivot_wider(names_from = q_key, values_from = resp) %>% 
-  rename_with(~str_replace(., "-", "_"), everything()) %>% 
-  mutate(across(ends_with("alreadyknew"), as.integer))
+  rename_with(~str_replace(., "-", "_"), everything())
 
 write_csv(less_raw, file = here::here("ignore", "data", "q_posttask.csv"))

### 2021-06-30 R/clean_q_trivia_demos.R

@@ -2,7 +2,7 @@ require(tidyverse)
 require(magrittr)
 source(here::here("R", "utils_read_gorilla.R"))
 
-raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
   read_gorilla_data("questionnaire-d6y6")
 
 less_raw <- raw %>% 

### 2021-06-30 R/clean_retrieval_facts.R

@@ -4,7 +4,7 @@ source(here::here("R", "utils_read_gorilla.R"))
 
 ## reading in and cleaning ----
 
-raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
   read_gorilla_data("task-txhz")
 
 pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
@@ -28,6 +28,18 @@ less_raw <- raw %>%
   filter(trial_screen == "recall") %>%
   mutate(retrieval_trial_num = as.integer(retrieval_trial_num),
          timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout)) %>%
+  nest(data = -c(subj_num, retrieval_trial_num)) %>% 
+  # patch in a "response" row if fully timed out
+  mutate(data = map(data,
+                    function (x) {
+                      if (nrow(x) == 1) {
+                        if (x$zone == "timelimit") {
+                          x$zone <- "response"
+                        }
+                      }
+                      return (x)
+                    })) %>% 
+  unnest(data) %>% 
   filter(zone == "response") %>%
   select(-c(trial_screen, zone)) %>% 
   nest(data = -c(subj_num, retrieval_trial_num)) %>% 
@@ -47,67 +59,13 @@ less_raw <- raw %>%
   unnest(data) %>% 
   mutate(category = if_else(group == "academic", category1, category2)) %>% 
   select(-c(category1, category2, categories)) %>%
-  mutate(acc_recall_rough = map2_lgl(resp, test_answer,
-                                     function (a, b) {
-                                       # trim non alpha nums in response in case they make grepl yell
-                                       a <- str_remove_all(a, "[^a-zA-Z\\d\\s-']")
-                                       if (!is.na(a) & nchar(a) == 0) {
-                                         return (FALSE)
-                                       } else {
-                                         out <- (grepl(a, b, ignore.case = T) | grepl(b, a, ignore.case = T)) %>% 
-                                           coalesce(FALSE)
-                                         
[…]

### 2021-06-30 R/clean_retrieval_pics.R

@@ -2,7 +2,7 @@ require(tidyverse)
 require(magrittr)
 source(here::here("R", "utils_read_gorilla.R"))
 
-raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
+raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
   read_gorilla_data("task-3n9k|task-cuj6")
 
 pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
@@ -20,7 +20,7 @@ less_raw <- raw %>%
          resp = `Response`,
          timeout = `Timed Out`,
          encoding_pic = `counterbalance-mqv3`,
-         retrieval_pic_oldnew = `counterbalance-ekxi`,
+         # retrieval_pic_oldnew = `counterbalance-ekxi`,
          retrieval_pic_2afc = `randomiser-snec`,
          starts_with("pic_c"),
          starts_with("pic_d")) %>% 
@@ -44,18 +44,6 @@ less_raw <- raw %>%
                                     pic_d = paste0("pic_d.", .y)))) %>%
   unnest(data)
 
-d_oldnew <- less_raw %>% 
-  filter(is.na(retrieval_pic_2afc)) %>% 
-  mutate(category = if_else(group == "academic", category1, category2),
-         pic_shown = if_else(retrieval_pic_oldnew == "c", pic_c, pic_d),
-         resp_binary = if_else(resp > 50, 1L, 0L)) %>% 
-  separate(pic_shown, into = c("pic_shown", NA)) %>% 
-  separate(pic_shown, into = c(NA, "group_trial_num", "is_old"), sep = c(4L, -1L), convert = TRUE) %>% 
-  mutate(is_old = if_else(is_old == encoding_pic, 1L, 0L),
-         resp = if_else(is_old == 1, resp - 50, -(resp - 50)),
-         resp_binary = if_else(resp > 0, 1L, 0L)) %>% 
-  select(-c(trial_num, category1, category2, categories, pic_c, pic_d, encoding_pic, starts_with("retrieval_pic")))
-
 d_2afc <- less_raw %>% 
   filter(!is.na(retrieval_pic_2afc)) %>% 
   mutate(category = if_else(group == "academic", category1, category2),
@@ -67,6 +55,19 @@ d_2afc <- less_raw %>%
          resp_binary = if_else(resp > 0, 1L, 0L)) %>% 
[…]

### 2021-06-30 R/clean_retrieval_source.R

@@ -2,8 +2,8 @@ require(tidyverse)
 require(magrittr)
 source(here::here("R", "utils_read_gorilla.R"))
 
-raw <- list.files(here::here("ignore", "data", "raw"), recursive = T, full.names = T) %>% 
-  read_gorilla_data("task-1152")
+raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
+  read_gorilla_data("task-1152|task-iqq7|task-dyao")
 
 pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
   select(-n_correct) %>%

### 2021-06-30 slides/data_checking.Rmd
init checking real data copied from exploration

--- 2021-05-12 slides/exploration.Rmd
@@
 require(magrittr)
-j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv"))
+j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv")) %>% 
+  mutate(resp_conf = if_else(is.na(resp_recall), NA_real_, resp_conf))
 
@@
   left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score),
+         resp = fct_relevel(resp, "Learning Memory", after = Inf))
 j_meta_desc <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_descriptions.csv")) %>% 
@@
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-r_pics_oldnew <- read_csv(here::here("ignore", "data", "task_retrieval_pics_oldnew.csv")) %>% 
-  left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-r_pics_2afc <- read_csv(here::here("ignore", "data", "task_retrieval_pics.csv")) %>% 
+r_pics <- read_csv(here::here("ignore", "data", "task_retrieval_pics.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
@@
 q_posttask  <- read_csv(here::here("ignore", "data", "q_posttask.csv"))
+
+retrieval <- r_facts %>%
+  select(subj_num, j_score, group, group_trial_num, retrieval_block, ep_is_same, sem_is_same, retrieval_trial_num, category, acc_recall, rt_start_recall = rt_start, rt_end_recall = rt_end) %>% 
+  left_join(r_pics %>% 
+              select(subj_num, group, group_trial_num, category, resp_pic = resp, rt_pic = rt)) %>% 
+  left_join(r_source %>%
+              select(subj_num, group, group_trial_num, category, resp_source = resp, rt_source = rt)) %>%
+  left_join(encoding %>% 
+              select(subj_num, group, group_trial_num, category, interest = resp, already_knew)) %>% 
+  mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
+                                          retrieval_block <= 8 ~ "ep_same_sem_diff",
+                                          retrieval_block <= 12 ~ "ep_diff_sem_same",
+                                          retrieval_block <= 16 ~ "ep_diff_sem_diff",
+                                          TRUE ~ NA_character_))
 ```
@@
   ggplot(aes(x = trivia_skill_self, y = j_score)) +
+  geom_abline(slope = .01, intercept = 0, linetype = "dotted") +
   geom_point(size = 3) +
+  expand_limits(y = 0) +
   labs(x = "Self-reported trivia expertise (relative to 'average person')",
@@
   geom_jitter(alpha = 0.3, height = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), se = FALSE) + 
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
+  theme_bw()
+```
+
+---
+
+```{r}
+j_recall %>% 
+  ggplot(aes(x = rt_end_recall, y = as.integer(acc_recall), color = j_score, fill = j_score)) + 
+  geom_jitter(alpha = 0.3, height = 0.05) + 
   geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
@@
   scale_fill_viridis_c() +
-  labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
+  labs(x = "Recall submit RT", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
+  theme_bw()
+```
+
+---
+
+```{r}
+j_recall %>% 
+  ggplot(aes(x = rt_end_recall, y = resp_conf, color = j_score, fill = j_score)) + 
+  geom_jitter(alpha = 0.3, height = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "lm", alpha = 0.05) + 
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Recall submit RT", y = "Recall confidence", color = "Expertise score", fill = "Expertise score") +
   theme_bw()
@@
 j_meta %>%
+  filter(!is.na(resp)) %>% 
   left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
@@
 
+# Museum task encoding
+
+---
+
+```{r}
+encoding %>% 
+  ggplot(aes(x = resp, fill = category)) +
+  geom_histogram(position = "identity", alpha = 0.5) +
+  facet_wrap(~subj_num)
+```
+
+---
+
+```{r}
+encoding %>% 
+  ggplot(aes(x = resp, y = rt, color = j_score, fill = j_score)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~subj_num) +
+  scale_colour_viridis_c() +
+  scale_fill_viridis_c()
+```
+
+---
+
+```{r}
+encoding %>% 
+  mutate(already_knew = fct_relevel(already_knew, "Did not know this before", "Knew some of this before")) %>% 
+  ggplot(aes(x = subj_num, fill = already_knew)) +
+  geom_bar() +
+  scale_x_discrete(guide = guide_axis(angle = 30)) +
+  labs(x = "Participant", y = "# facts already knew", fill = "Prior knowledge") +
+  theme_bw()
+```
+
+---
+
+class: inverse, middle
+
 # Museum task retrieval
@@
 
-Old setup: A-B' old-new recognition with similar lures as foils
-
-```{r}
-r_pics_oldnew %>%
-  ggplot(aes(x = factor(subj_num), y = resp, fill = factor(is_old))) +
-  geom_hline(yintercept = 0, linetype = "dotted") +
-  geom_boxplot() +
-  labs(x = "Participant", y = "Accuracy with confidence (positive = correct)") +
-  theme_bw()
-```
-
-```{r}
-r_pics_oldnew %>%
-  mutate(say_old = case_when(is_old == 0 & resp_binary == 1 ~ 0L,
-                             is_old == 0 & resp_binary == 0 ~ 1L,
-                             is_old == 1 & resp_binary == 0 ~ 0L,
-                             is_old == 1 & resp_binary == 1 ~ 1L,
-                             TRUE ~ NA_integer_)) %>% 
-  nest(data = -subj_num) %>% 
-  mutate(coefs = map(data, ~glm(say_old ~ is_old, family = binomial(link = "logit"), data = .) %>% 
-                       broom::tidy())) %>% 
-  select(subj_num, coefs) %>% 
-  unnest(coefs) %>% 
-  filter(term == "is_old")
-```
-
----
-
-### Photo recognition
-
 Current setup: A-A' 2AFC with similar lure
@@
 ```{r}
-r_pics_2afc %>%
+r_pics %>%
   ggplot(aes(x = factor(subj_num), y = resp, color = j_score)) +
@@
 # Retrieval between-task relationships
-
-```{r}
-retrieval <- r_facts %>%
-  select(subj_num, j_score, group, group_trial_num, retrieval_block, ep_is_same, sem_is_same, retrieval_trial_num, category, acc_recall, rt_start_recall = rt_start, rt_end_recall = rt_end) %>% 
-  left_join(r_pics_oldnew %>%
-              select(subj_num, group, group_trial_num, category, pic_is_old = is_old, resp_pic = resp, rt_pic = rt) %>% 
-              bind_rows(r_pics_2afc %>% 
-                          select(subj_num, group, group_trial_num, category, resp_pic = resp, rt_pic = rt))) %>% 
-  left_join(r_source %>%
-              select(subj_num, group, group_trial_num, category, resp_source = resp, rt_source = rt)) %>%
-  left_join(encoding %>% 
-              select(subj_num, group, group_trial_num, category, interest = resp)) %>% 
-  mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
-                                          retrieval_block <= 8 ~ "ep_same_sem_diff",
-                                          retrieval_block <= 12 ~ "ep_diff_sem_same",
-                                          retrieval_block <= 16 ~ "ep_diff_sem_diff",
-                                          TRUE ~ NA_character_))
-```
 

### 2021-06-30 R/get_participants.R
init file, handle p records from inquiry to payment

@@ -1,0 +1,63 @@
+## setup ----
+
+require(tidyverse)
+require(qualtRics)
+
+## get inquiries from qualtrics ----
+
+inquiries_raw <- fetch_survey("SV_cx7HTf5yYOwaYrs",
+             force_request = TRUE,
+             label = TRUE)
+
+inquiries <- inquiries_raw %>% 
+  filter(consent == "YES, I would like to continue.",
+         interested == "Yes",
+         !is.na(email)) %>% 
+  select(public_id = ResponseId, email) %>% 
+  mutate(name = public_id,
+         group = "")
+
+write_csv(inquiries, here::here("ignore", "running_subjs", "participants_gorilla_upload.csv"))
+
+## read in completion status from gorilla manual download ----
+
+completions_raw <- read_csv(here::here("ignore", "running_subjs", "participants_gorilla_download.csv"))
+
+completions <- completions_raw %>% 
+  select(email = `Email Address`,
+         checkpoint = Checkpoint,
+         current_node = `Current Node`,
+         status = Status)
+
+## write out email addresses for next tango card payment batch ----
+
+# By reading in previous pay files, should be able to ID who's been paid to avoid double paying
+
+payments_past <- tibble(file = list.files(here::here("ignore", "running_subjs"),
+                            full.names = TRUE)) %>% 
+  filter(grepl("tango", file)) %>% 
+  mutate(payment_date = lubridate::ymd(str_sub(file, -12L, -5L)),
+         data = map(file, read_csv)) %>% 
+  unnest(data)
+
+payments <- completions %>% 
+  filter(status == "Complete") %>% 
+  anti_join(payments_past, by = "email") %>% 
+  select(email) %>% 
+  mutate(etid = "E029217",
+         firstname = "Participant",
+         lastname = NA,
+         utid = "U579023",
+         amt = 30,
+         notes = NA,
+         dnc = NA,
+         message = NA,
+         sender_name = "Columbia Aly Lab") %>% 
+  select(etid, email, everything())
+
+# Write out only one pay file per pay batch (with pay date as identifier)
+
+write_csv(payments, here::here("ignore",
+                               "running_subjs",
+                               glue::glue("participants_tango_upload_{str_remove_all(Sys.Date(), '-')}.csv")),
+          na = "")

### 2021-06-30 R/study_sims.Rmd
move file, reorganize large bootstrap

---
title: "scratch simulations"
author: "Monica Thieu"
date: "4/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(magrittr)
j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv"))

j_exp <- j_recall %>% 
  group_by(subj_num) %>% 
  summarize(j_score = mean(acc_recall))

j_recall %<>%
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))

j_meta <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_states.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
j_meta_desc <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_descriptions.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
encoding <- read_csv(here::here("ignore", "data", "task_encoding.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
r_facts <- read_csv(here::here("ignore", "data", "task_retrieval_facts.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
r_pics <- read_csv(here::here("ignore", "data", "task_retrieval_pics.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
r_source <- read_csv(here::here("ignore", "data", "task_retrieval_source.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
q_demos  <- read_csv(here::here("ignore", "data", "q_trivia_demos.csv")) %>% 
  left_join(j_exp, by = "subj_num") %>% 
  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))

retrieval <- r_facts %>%
  select(subj_num, j_score, group, group_trial_num, retrieval_block, ep_is_same, sem_is_same, retrieval_trial_num, category, acc_recall, rt_start_recall = rt_start, rt_end_recall = rt_end) %>% 
  left_join(r_pics %>% 
              select(subj_num, group, group_trial_num, category, resp_pic = resp, rt_pic = rt)) %>% 
  left_join(r_source %>%
              select(subj_num, group, group_trial_num, category, resp_source = resp, rt_source = rt)) %>%
  left_join(encoding %>% 
              select(subj_num, group, group_trial_num, category, interest = resp)) %>% 
  mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
                                          retrieval_block <= 8 ~ "ep_same_sem_diff",
                                          retrieval_block <= 12 ~ "ep_diff_sem_same",
                                          retrieval_block <= 16 ~ "ep_diff_sem_diff",
                                          TRUE ~ NA_character_))
```

```{r}
stuff <- tibble(id = 1:20) %>%
  mutate(if_else(id %% 2 == 0, "trivia", "control"))
```

# Just Jeopardy pre-test expertise

## Parameter recovery within subject

```{r}
j_recall %>% 
  ggplot(aes(x = resp_conf)) +
  geom_histogram() +
  facet_wrap(~subj_num)
```

```{r}
j_recall %>% 
  mutate(acc_recall = as.integer(acc_recall),
         resp_conf = resp_conf / 100) %>% 
  nest(data = -c(subj_num, j_score)) %>% 
  mutate(coefs = map(data, ~glm(acc_recall ~ resp_conf, family = binomial(link = "logit"), data = .) %>% 
                       broom::tidy()
                       )) %>% 
  select(-data) %>% 
  unnest(coefs) %>% 
  select(-statistic, -p.value) %>% 
  mutate(term = recode(term, `(Intercept)` = "intercept"))
```

# Museum task

## Interest ratings

### INTERACTION: Does retrieval ~ encoding interest depend on expertise?

```{r}
retrieval %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  ggplot(aes(x = interest, y = acc_recall, color = j_score, fill = j_score)) + 
  geom_jitter(alpha = 0.3, height = 0.05) + 
  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
  scale_color_viridis_c() +
  scale_fill_viridis_c() +
  labs(x = "Interest in fact at encoding", y = "Fact recall accuracy (generous)") +
  theme_bw()
```

```{r}
retrieval %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall),
         interest = (interest - 50) / 100) %>% 
  nest(data = -c(subj_num, j_score)) %>% 
  mutate(model = map(data, ~glm(acc_recall ~ interest, family = binomial(link = "logit"), data = .)),
         coefs = map(model, broom::tidy)) %>% 
  select(subj_num, j_score, coefs) %>% 
  unnest() %>% 
  select(-statistic, -p.value) %>% 
  mutate(term = recode(term, `(Intercept)` = "intercept")) %>% 
  pivot_wider(names_from = term, values_from = c(estimate, std.error)) %>% 
  ggplot(aes(x = estimate_interest, y = std.error_interest, color = j_score)) +
  geom_point() +
  scale_colour_viridis_c()
```

```{r}
retrieval %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall),
         interest = (interest - 50) / 100) %>% 
  nest(data = -c(subj_num, j_score)) %>% 
  mutate(model = map(data, ~glm(acc_recall ~ interest, family = binomial(link = "logit"), data = .)),
         coefs = map(model, broom::tidy)) %>% 
  select(subj_num, j_score, coefs) %>% 
  unnest() %>% 
  select(-statistic, -p.value) %>% 
  mutate(term = recode(term, `(Intercept)` = "intercept")) %>% 
  pivot_wider(names_from = term, values_from = c(estimate, std.error)) %>% 
  ggplot(aes(x = estimate_interest, y = std.error_interest)) +
  geom_point()
```

P(correct recall for given subject) ~ invlogit(intercept fixed + intercept random + interest + j)

```{r}
glmer_retrieval_by_interest_expertise <- retrieval %>% 
  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall),
         interest = (interest - 50) / 100,
         j_score = j_score - 0.5) %>% 
  lme4::glmer(acc_recall ~ interest * j_score + (1 | subj_num),
              family = binomial(link = "logit"),
              data = .)

coefs_retrieval_by_interest_expertise <- glmer_retrieval_by_interest_expertise %>%
  broom.mixed::tidy() %>%
  select(effect:estimate)
```

```{r}

```

###

### 2021-06-30 R/sim_retrieval_by_interest_expertise.R

@@ -1,0 +1,80 @@
+## setup ----
+
+require(tidyverse)
+require(magrittr)
+j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv"))
+
+j_exp <- j_recall %>% 
+  group_by(subj_num) %>% 
+  summarize(j_score = mean(acc_recall))
+
+j_recall %<>%
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+
+encoding <- read_csv(here::here("ignore", "data", "task_encoding.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+r_facts <- read_csv(here::here("ignore", "data", "task_retrieval_facts.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+r_pics <- read_csv(here::here("ignore", "data", "task_retrieval_pics.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+r_source <- read_csv(here::here("ignore", "data", "task_retrieval_source.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+
+retrieval <- r_facts %>%
+  select(subj_num, j_score, group, group_trial_num, retrieval_block, ep_is_same, sem_is_same, retrieval_trial_num, category, acc_recall, rt_start_recall = rt_start, rt_end_recall = rt_end) %>% 
+  left_join(r_pics %>% 
+              select(subj_num, group, group_trial_num, category, resp_pic = resp, rt_pic = rt)) %>% 
+  left_join(r_source %>%
+              select(subj_num, group, group_trial_num, category, resp_source = resp, rt_source = rt)) %>%
+  left_join(encoding %>% 
+              select(subj_num, group, group_trial_num, category, interest = resp)) %>% 
+  mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
+                                          retrieval_block <= 8 ~ "ep_same_sem_diff",
+                                          retrieval_block <= 12 ~ "ep_diff_sem_same",
[…]

### 2021-06-30 slides/exploration.Rmd
some more random ass graphs

@@
 require(magrittr)
-j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv"))
+j_recall <- read_csv(here::here("ignore", "data", "pilot", "task_jeopardy_recall.csv"))
 
@@
 
-j_meta <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_states.csv")) %>% 
+j_meta <- read_csv(here::here("ignore", "data", "pilot", "task_jeopardy_meta_states.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score),
+         resp = fct_relevel(resp, "Learning Memory", after = Inf))
+j_meta_desc <- read_csv(here::here("ignore", "data", "pilot", "task_jeopardy_meta_descriptions.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-j_meta_desc <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_descriptions.csv")) %>% 
+encoding <- read_csv(here::here("ignore", "data", "pilot", "task_encoding.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-encoding <- read_csv(here::here("ignore", "data", "task_encoding.csv")) %>% 
+r_facts <- read_csv(here::here("ignore", "data", "pilot", "task_retrieval_facts.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-r_facts <- read_csv(here::here("ignore", "data", "task_retrieval_facts.csv")) %>% 
+r_pics_oldnew <- read_csv(here::here("ignore", "data", "pilot", "task_retrieval_pics_oldnew.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-r_pics_oldnew <- read_csv(here::here("ignore", "data", "task_retrieval_pics_oldnew.csv")) %>% 
+r_pics_2afc <- read_csv(here::here("ignore", "data", "pilot", "task_retrieval_pics.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-r_pics_2afc <- read_csv(here::here("ignore", "data", "task_retrieval_pics.csv")) %>% 
+r_source <- read_csv(here::here("ignore", "data", "pilot", "task_retrieval_source.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-r_source <- read_csv(here::here("ignore", "data", "task_retrieval_source.csv")) %>% 
+q_demos  <- read_csv(here::here("ignore", "data", "pilot", "q_trivia_demos.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-q_demos  <- read_csv(here::here("ignore", "data", "q_trivia_demos.csv")) %>% 
-  left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-q_posttask  <- read_csv(here::here("ignore", "data", "q_posttask.csv"))
+q_posttask  <- read_csv(here::here("ignore", "data", "pilot", "q_posttask.csv"))
+
+retrieval <- r_facts %>%
+  select(subj_num, j_score, group, group_trial_num, retrieval_block, ep_is_same, sem_is_same, retrieval_trial_num, category, acc_recall, rt_start_recall = rt_start, rt_end_recall = rt_end) %>% 
+  left_join(r_pics_oldnew %>%
+              select(subj_num, group, group_trial_num, category, pic_is_old = is_old, resp_pic = resp, rt_pic = rt) %>% 
+              bind_rows(r_pics_2afc %>% 
+                          select(subj_num, group, group_trial_num, category, resp_pic = resp, rt_pic = rt))) %>% 
+  left_join(r_source %>%
+              select(subj_num, group, group_trial_num, category, resp_source = resp, rt_source = rt)) %>%
+  left_join(encoding %>% 
+              select(subj_num, group, group_trial_num, category, interest = resp)) %>% 
+  mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
+                                          retrieval_block <= 8 ~ "ep_same_sem_diff",
+                                          retrieval_block <= 12 ~ "ep_diff_sem_same",
+                                          retrieval_block <= 16 ~ "ep_diff_sem_diff",
+                                          TRUE ~ NA_character_))
 ```
@@
   labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
+  theme_bw()
+```
+
+---
+
+```{r}
+j_recall %>% 
+  ggplot(aes(x = rt_end_recall, y = as.integer(acc_recall), color = j_score, fill = j_score)) + 
+  geom_jitter(alpha = 0.3, height = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
+  theme_bw()
+```
+
+---
+
+```{r}
+j_recall %>% 
+  ggplot(aes(x = rt_end_recall, y = resp_conf, color = j_score, fill = j_score)) + 
+  geom_jitter(alpha = 0.3, height = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "lm", alpha = 0.05) + 
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Recall submit RT", y = "Recall confidence", color = "Expertise score", fill = "Expertise score") +
   theme_bw()
@@
   cat(sep = "\n\n")
+```
+
+---
+
+class: inverse, middle
+
+# Museum task encoding
+
+---
+
+```{r}
+encoding %>% 
+  ggplot(aes(x = resp, fill = category)) +
+  geom_histogram(position = "identity", alpha = 0.5) +
+  facet_wrap(~subj_num)
+```
+
+---
+
+```{r}
+encoding %>% 
+  ggplot(aes(x = resp, y = rt, color = j_score, fill = j_score)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~subj_num) +
+  scale_colour_viridis_c() +
+  scale_fill_viridis_c()
 ```
@@
 
-```{r}
-retrieval <- r_facts %>%
-  select(subj_num, j_score, group, group_trial_num, retrieval_block, ep_is_same, sem_is_same, retrieval_trial_num, category, acc_recall, rt_start_recall = rt_start, rt_end_recall = rt_end) %>% 
-  left_join(r_pics_oldnew %>%
-              select(subj_num, group, group_trial_num, category, pic_is_old = is_old, resp_pic = resp, rt_pic = rt) %>% 
-              bind_rows(r_pics_2afc %>% 
-                          select(subj_num, group, group_trial_num, category, resp_pic = resp, rt_pic = rt))) %>% 
-  left_join(r_source %>%
-              select(subj_num, group, group_trial_num, category, resp_source = resp, rt_source = rt)) %>%
-  left_join(encoding %>% 
-              select(subj_num, group, group_trial_num, category, interest = resp)) %>% 
-  mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
-                                          retrieval_block <= 8 ~ "ep_same_sem_diff",
-                                          retrieval_block <= 12 ~ "ep_diff_sem_same",
-                                          retrieval_block <= 16 ~ "ep_diff_sem_diff",
-                                          TRUE ~ NA_character_))
-```
-
 ---

### 2021-07-01 slides/data_checking.Rmd
add more, already knew, a huge mess

@@
 
+# Self-report measures
+
+---
+
+```{r}
+q_demos %>%
+  select(subj_num, starts_with("trivia"), j_score) %>% 
+  mutate(j_score = j_score * 100) %>% 
+  pivot_longer(cols = -subj_num, names_to = "var", values_to = "value") %>% 
+  ggplot(aes(x = value)) + geom_histogram() + facet_wrap(~ var)
+```
+
+---
+
+class: inverse, middle
+
 # Museum task encoding
@@
 ```{r}
-r_facts %>% 
+retrieval %>% 
   ggplot(aes(x = retrieval_trial_num, y = acc_recall)) +
-  geom_rect(aes(x = NULL, y = NULL, xmin = xmin, xmax = xmax, fill = interaction(ep_is_same, sem_is_same)),
-            data = r_facts %>%
-              mutate(ep_is_same = recode(ep_is_same,
-                                         `0` = "ep diff",
-                                         `1` = "ep same"),
-                     sem_is_same = recode(sem_is_same,
-                                          `0` = "sem diff",
-                                          `1` = "sem same")) %>% 
-              select(subj_num, retrieval_block, retrieval_trial_num, ep_is_same, sem_is_same) %>%
+  geom_rect(aes(x = NULL, y = NULL, xmin = xmin, xmax = xmax, fill = retrieval_block_type),
+            data = retrieval %>%
+              select(subj_num, retrieval_block, retrieval_trial_num, retrieval_block_type) %>%
               group_by(subj_num, retrieval_block) %>%
@@
   geom_line() +
-  geom_point() +
-  scale_colour_viridis_b() +
+  geom_point(aes(color = already_knew)) +
+  # scale_colour_viridis_b() +
   scale_y_continuous(n.breaks = 3) +
@@
   theme_bw()
+```
+
+---
+
+### Fact recall by already knew status
+
+```{r}
+retrieval %>% 
+  mutate(acc_recall = if_else(acc_recall > 0, 1, 0)) %>% 
+  filter(!is.na(already_knew)) %>% 
+  ggplot(aes(x = subj_num, fill = factor(acc_recall))) +
+  geom_bar() +
+  facet_grid(~already_knew)
+```
+
+---
+
+```{r}
+retrieval %>% 
+  mutate(acc_recall = if_else(acc_recall > 0, 1, 0)) %>% 
+  filter(!is.na(already_knew)) %>% 
+  count(subj_num, acc_recall, already_knew) %>% 
+  group_by(subj_num, already_knew) %>% 
+  mutate(prob = n / sum(n)) %>% 
+  ggplot(aes(x = subj_num, y = prob, fill = factor(acc_recall))) +
+  geom_col() +
+  facet_grid(~already_knew)
 ```
@@
 retrieval %>% 
+  filter(!is.na(already_knew)) %>% 
   mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
@@
   scale_fill_viridis_c() +
+  facet_grid(~already_knew) +
   labs(x = "Photo recognition accuracy", y = "Fact recall accuracy (generous)") +
@@
   ggplot(aes(x = resp_source, y = resp_pic, color = j_score, fill = j_score)) + 
-  geom_point() + 
-  geom_smooth(method = "lm") + 
-  facet_wrap(~subj_num) +
+  geom_point(alpha = 0.3) + 
+  geom_smooth(aes(group = subj_num), method = "lm", se = FALSE) + 
   scale_color_viridis_c() +
@@
   ggplot(aes(x = interest, y = resp_pic, color = j_score, fill = j_score)) + 
-  geom_point() + 
-  geom_smooth(method = "lm") + 
-  facet_wrap(~subj_num) +
+  geom_point(alpha = 0.3) + 
+  geom_smooth(aes(group = subj_num), method = "lm", se = FALSE) + 
   scale_color_viridis_c() +
@@
   ggplot(aes(x = interest, y = resp_source, color = j_score, fill = j_score)) + 
-  geom_point() + 
-  geom_smooth(method = "lm") + 
-  facet_wrap(~subj_num) +
+  geom_point(alpha = 0.3) + 
+  geom_smooth(aes(group = subj_num), method = "lm", se = FALSE) + 
   scale_color_viridis_c() +

### 2021-07-01 slides/data_checking.Rmd
recode already knew

--- 2021-06-30 slides/data_checking.Rmd
@@
   left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score),
+         already_knew = fct_recode(already_knew,
+                               none = "Did not know this before",
+                               some = "Knew some of this before",
+                               all = "Knew all of this before"))
 r_facts <- read_csv(here::here("ignore", "data",  "task_retrieval_facts.csv")) %>% 

### 2021-07-01 slides/data_checking.Rmd
couple more graphs, add encoding trial num to retrieval

@@
                                           retrieval_block <= 16 ~ "ep_diff_sem_diff",
-                                          TRUE ~ NA_character_))
+                                          TRUE ~ NA_character_),
+         encoding_trial_num = if_else(group == "academic",
+                                      group_trial_num * 2 - 1,
+                                      group_trial_num * 2))
 ```
@@
 
+### Fact recall by ENCODING question order
+
+```{r}
+retrieval %>% 
+  nest(data = -subj_num) %>% 
+  sample_n(10) %>% 
+  unnest(data) %>% 
+  mutate(encoding_trial_num = if_else(group == "academic", group_trial_num * 2 - 1, group_trial_num * 2)) %>% 
+  ggplot(aes(x = retrieval_trial_num, y = acc_recall)) +
+  geom_line() +
+  geom_point(aes(color = already_knew)) +
+  # scale_colour_viridis_b() +
+  scale_y_continuous(n.breaks = 3) +
+  facet_grid(subj_num ~ .) +
+  labs(x = "Encoding trial (beginning to end)", y = "Subsequent fact recall accuracy") +
+  theme_bw()
+```
+
+---
+
 ### Photo recognition
@@
 retrieval %>% 
-  filter(!is.na(already_knew)) %>% 
+  # filter(!is.na(already_knew)) %>% 
   mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
@@
   scale_fill_viridis_c() +
-  facet_grid(~already_knew) +
+  # facet_grid(~already_knew) +
   labs(x = "Photo recognition accuracy", y = "Fact recall accuracy (generous)") +

### 2021-07-05 slides/data_checking.Rmd
have general demos now

--- 2021-07-01 slides/data_checking.Rmd
@@
 require(magrittr)
+
+demos_ids <- read_csv(here::here("ignore", "data", "demos_ids.csv"))
+q_google_demos <- read_csv(here::here("ignore", "data", "q_google_demos.csv")) %>% 
+  right_join(demos_ids, by = "demographics_id")
+
 j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv")) %>% 
@@
   left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score),
-         already_knew = fct_recode(already_knew,
-                               none = "Did not know this before",
-                               some = "Knew some of this before",
-                               all = "Knew all of this before"))
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
 r_facts <- read_csv(here::here("ignore", "data",  "task_retrieval_facts.csv")) %>% 
@@
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-q_demos  <- read_csv(here::here("ignore", "data", "q_trivia_demos.csv")) %>% 
+q_trivia_demos  <- read_csv(here::here("ignore", "data", "q_trivia_demos.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+
 q_posttask  <- read_csv(here::here("ignore", "data", "q_posttask.csv"))
@@
   scale_fill_viridis_c() +
+  labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
+  theme_bw()
+```
+
+---
+
+```{r}
+j_recall %>% 
+  left_join(q_google_demos %>% mutate(subj_num = factor(subj_num)), by = "subj_num") %>% 
+  ggplot(aes(x = resp_conf, y = as.integer(acc_recall), color = gender, fill = gender)) + 
+  geom_jitter(alpha = 0.3, height = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), se = FALSE) +
   labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
@@
   geom_point() +
-  geom_smooth(method = "lm") +
-  facet_wrap(~subj_num) +
+  geom_smooth(aes(group = subj_num), method = "lm", se = FALSE) +
   scale_colour_viridis_c() +

### 2021-07-05 R/clean_q_google_demos.R

@@ -1,0 +1,35 @@
+## setup ----
+
+require(tidyverse)
+require(magrittr)
+
+googledrive::drive_download(as_id("1yW13tK4dVr8MXtJTaZxV_3M8IaD5TqhbzD8QKPuEndM"),
+                            path = here::here("ignore", "data", "raw", "real", "demographics.csv"),
+                            type = "csv",
+                            overwrite = TRUE)
+
+## read n parse ----
+
+# Must do col transforming after dropping unwanted cols
+# col_types and cols_only don't seem to drop cols smoothly
+demos <- read_csv(here::here("ignore", "data", "raw", "real", "demographics.csv")) %>% 
+  select(study_name = "Study Name [***Do Not Edit***]",
+         timestamp = Timestamp,
+         demographics_id = "Participant ID [***Do Not Edit***]",
+         age = Age,
+         edu = "Years of Education",
+         gender = Gender,
+         ethnicity = Ethnicity,
+         race = "Race (check all that apply)") %>% 
+  mutate(timestamp = lubridate::parse_date_time(timestamp, "mdY HMS")) %>% 
+  filter(study_name == "JStudy", timestamp >= "2021-06-23") %>% 
+  mutate(gender = case_when(tolower(gender) %in% c("m", "male") ~ "male",
+                            tolower(gender) %in% c("f", "female") ~ "female",
+                            grepl("nonbinary|genderqueer", gender, ignore.case = T) ~ "genderqueer",
+                            grepl("male", gender, ignore.case = T) & !grepl("female", gender, ignore.case = T) ~ "male",
+                            grepl("female", gender, ignore.case = T)  ~ "female",
+                            grepl("man", gender, ignore.case = T) & !grepl("woman", gender, ignore.case = T) ~ "male",
+                            grepl("woman", gender, ignore.case = T)  ~ "female",
+                            TRUE ~ NA_character_))
+
+write_csv(demos, here::here("ignore", "data", "q_google_demos.csv"))

### 2021-07-05 R/score_expertise.R
sometimes !strict fuzzy !lastname happens now

@@ -51,7 +51,7 @@ scored <- unscored %>%
          acc_recall_grepl_lastname = case_when(answer == "uranium" & grepl("plutonium", resp_recall, ignore.case = T) ~ FALSE,
                                             TRUE ~ acc_recall_grepl_lastname))
 
-stopifnot(scored %>% filter(!acc_recall_grepl_strict, acc_recall_grepl_fuzzy, !acc_recall_grepl_lastname) %>% nrow() == 0)
+# stopifnot(scored %>% filter(!acc_recall_grepl_strict, acc_recall_grepl_fuzzy, !acc_recall_grepl_lastname) %>% nrow() == 0)
 
 ## hand scoring interactively ----
 
@@ -98,6 +98,8 @@ scored %<>%
     !is.na(acc_recall_byhand) ~ acc_recall_byhand,
     # !strict, !fuzzy, !lastname: all wrong, totally wrong
     !acc_recall_grepl_strict & !acc_recall_grepl_fuzzy & !acc_recall_grepl_lastname ~ FALSE,
+    # !strict, fuzzy, !lastname: matches part of the answer but not the key part (e.g. "rebellion" but not "boxer")
+    !acc_recall_grepl_strict & acc_recall_grepl_fuzzy & !acc_recall_grepl_lastname ~ FALSE,
     # strict, !fuzzy, !lastname: all wrong, too short
     acc_recall_grepl_strict & !acc_recall_grepl_fuzzy & !acc_recall_grepl_lastname ~ FALSE,
     # strict, !fuzzy, lastname: all right, last name only spelled correctly

### 2021-07-12 slides/data_checking.Rmd
graph expertise conf ~ recall

@@
 ```{r}
-q_demos %>% 
+q_trivia_demos %>% 
   ggplot(aes(x = trivia_skill_self, y = j_score)) +
@@
   labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
+  theme_bw()
+```
+
+---
+
+```{r}
+j_recall %>% 
+  ggplot(aes(x = acc_recall, y = resp_conf, color = j_score, fill = j_score)) + 
+  geom_jitter(alpha = 0.3, width = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "lm", formula = y ~ x, se = FALSE) + 
+  scale_color_viridis_c() +
+  scale_fill_viridis_c() +
+  labs(x = "Recall accuracy (strict)", y = "Recall confidence", color = "Expertise score", fill = "Expertise score") +
   theme_bw()
@@
 ```{r}
-q_demos %>%
+q_trivia_demos %>%
   select(subj_num, starts_with("trivia"), j_score) %>% 

### 2021-07-21 R/clean_q_google_demos.R
add googledrive::as_id bc not libraryed

@@ -3,7 +3,7 @@
 require(tidyverse)
 require(magrittr)
 
-googledrive::drive_download(as_id("1yW13tK4dVr8MXtJTaZxV_3M8IaD5TqhbzD8QKPuEndM"),
+googledrive::drive_download(googledrive::as_id("1yW13tK4dVr8MXtJTaZxV_3M8IaD5TqhbzD8QKPuEndM"),
                             path = here::here("ignore", "data", "raw", "real", "demographics.csv"),
                             type = "csv",
                             overwrite = TRUE)

### 2021-07-21 R/score_expertise.R
add ok spellings for distill and speaker of the house

@@ -6,7 +6,7 @@ require(magrittr)
 unscored <- read_csv(here::here("ignore", "data", "task_jeopardy_recall_unscored.csv"))
 
 if (FALSE) {
-  googledrive::drive_download(file = as_id("1e7R4CSDjSA5trC820aiwUbe7szjn7DTfMiZPI4my8Rk"),
+  googledrive::drive_download(file = googledrive::as_id("1e7R4CSDjSA5trC820aiwUbe7szjn7DTfMiZPI4my8Rk"),
                               path = here::here("stim_stuff", "jeopardy_spreadsheet.csv"),
                               type = "csv",
                               overwrite = TRUE)
@@ -34,7 +34,7 @@ scored <- unscored %>%
          # Particular very common misspellings that get special treatment
          acc_recall_grepl_strict = case_when(answer == "Spanish-American War" & grepl("spanish american", resp_recall, ignore.case = T) ~ TRUE,
                                              answer == "Andrea Bocelli" & grepl("andrea boccelli", resp_recall, ignore.case = T) ~ TRUE,
-                                             answer == "distillation" & startsWith(tolower(resp_recall), "distill") ~ TRUE,
+                                             answer == "distillation" & grepl("^distill|^destill", resp_recall, ignore.case = T) ~ TRUE,
                                              answer == "uranium" & grepl("plutonium", resp_recall, ignore.case = T) ~ FALSE,
                                              TRUE ~ acc_recall_grepl_strict),
          acc_recall_grepl_fuzzy = map2_lgl(resp_recall, answer,
@@ -45,6 +45,7 @@ scored <- unscored %>%
                                              agrepl(b, a, max.distance = 0.25, ignore.case = T)
                                            }),
          acc_recall_grepl_fuzzy = case_when(answer == "uranium" & grepl("plutonium", resp_recall, ignore.case = T) ~ FALSE,
+                                            answer == "Speaker of the House" & tolower(resp_recall) == "house speaker" ~ TRUE,
                                             TRUE ~ acc_recall_grepl_fuzzy),
          acc_recall_grepl_lastname = map2_lgl(resp_recall, answer_short,
                                               ~agrepl(.y, .x, max.distance = 0.25, ignore.case = T)),

### 2021-07-21 slides/data_checking.Rmd
add lmer for resp_conf ~ acc_recall * j_score
add couple demos graphs

@@
 q_google_demos <- read_csv(here::here("ignore", "data", "q_google_demos.csv")) %>% 
-  right_join(demos_ids, by = "demographics_id")
+  right_join(demos_ids, by = "demographics_id") %>% 
+  mutate(subj_num = factor(subj_num))
 
@@
 
+# Demographics
+
+---
+
+### What is the age and gender breakdown?
+
+```{r}
+q_google_demos %>% 
+  ggplot(aes(x = age, fill = gender)) +
+  geom_histogram(position = "identity", alpha = 0.5)
+```
+
+---
+
+class: inverse, middle
+
 # Trivia expertise assessment
@@
 q_trivia_demos %>% 
+  left_join(q_google_demos, by = "subj_num") %>% 
   ggplot(aes(x = trivia_skill_self, y = j_score)) +
-  geom_abline(slope = .01, intercept = 0, linetype = "dotted") +
-  geom_point(size = 3) +
+  # geom_abline(slope = .01, intercept = 0, linetype = "dotted") +
+  geom_vline(xintercept = 75, linetype = "dotted") +
+  geom_hline(yintercept = 0.7, linetype = "dotted") +
+  geom_point(aes(color = gender), size = 2, alpha = 0.7) +
+  geom_smooth(method = "lm", formula = y ~ x) +
   expand_limits(y = 0) +
@@
 j_recall %>% 
-  left_join(q_google_demos %>% mutate(subj_num = factor(subj_num)), by = "subj_num") %>% 
+  mutate(acc_recall = as.integer(acc_recall),
+         j_score = j_score - 0.5) %>% 
+  lme4::lmer(resp_conf ~ acc_recall * j_score + (1 + acc_recall | subj_num), data = .) %>% 
+  summary()
+```
+
+---
+
+```{r}
+j_recall %>% 
+  left_join(q_google_demos, by = "subj_num") %>% 
   ggplot(aes(x = resp_conf, y = as.integer(acc_recall), color = gender, fill = gender)) + 
@@
   labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
+  theme_bw()
+```
+
+---
+
+```{r}
+j_recall %>% 
+  left_join(q_google_demos, by = "subj_num") %>% 
+  ggplot(aes(x = acc_recall, y = resp_conf, color = gender)) + 
+  geom_jitter(alpha = 0.3, width = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "lm", formula = y ~ x, se = FALSE, size = 0.5) + 
+  labs(x = "Recall accuracy (strict)", y = "Recall confidence", color = "Expertise score", fill = "Expertise score") +
   theme_bw()

### 2021-07-21 slides/data_checking.Rmd

@@
   mutate(acc_recall = as.integer(acc_recall),
+         # so 0.5 is centered
          j_score = j_score - 0.5) %>% 

### 2021-08-16 R/score_expertise.R
change agrepl implementation for more sensible scores

@@ -42,13 +42,13 @@ scored <- unscored %>%
                                              # so titles starting with The don't get disadvantaged
                                              # by the cost dividing by whole string length
                                              b <- str_remove(b, "^The ")
-                                             agrepl(b, a, max.distance = 0.25, ignore.case = T)
+                                             agrepl(b, a, max.distance = 0.18, ignore.case = T)
                                            }),
          acc_recall_grepl_fuzzy = case_when(answer == "uranium" & grepl("plutonium", resp_recall, ignore.case = T) ~ FALSE,
                                             answer == "Speaker of the House" & tolower(resp_recall) == "house speaker" ~ TRUE,
                                             TRUE ~ acc_recall_grepl_fuzzy),
          acc_recall_grepl_lastname = map2_lgl(resp_recall, answer_short,
-                                              ~agrepl(.y, .x, max.distance = 0.25, ignore.case = T)),
+                                              ~agrepl(.y, .x, max.distance = 0.18, ignore.case = T)),
          acc_recall_grepl_lastname = case_when(answer == "uranium" & grepl("plutonium", resp_recall, ignore.case = T) ~ FALSE,
                                             TRUE ~ acc_recall_grepl_lastname))
 
@@ -65,7 +65,7 @@ scored %<>% left_join(byhand)
 #scored$acc_recall_byhand <- NA
 for (i in 1:nrow(scored)) {
   # if strict is false, and at least one of fuzzy or lastname is true
-  if (is.na(scored$acc_recall_byhand[i]) & !scored$acc_recall_grepl_strict[i] & (scored$acc_recall_grepl_fuzzy[i] | scored$acc_recall_grepl_lastname[i])) {
+  if (is.na(scored$acc_recall_byhand[i]) & nchar(scored$resp_recall[i]) > 2 & scored$acc_recall_grepl_strict[i] != (scored$acc_recall_grepl_fuzzy[i] | scored$acc_recall_grepl_lastname[i])) {
     
     cat("\nCorrect answer:", crayon::green(scored$answer[i]),
         " Response:", crayon::yellow(scored$resp_recall[i]))
@@ -105,6 +105,8 @@ scored %<>%
     acc_recall_grepl_strict & !acc_recall_grepl_fuzzy & !acc_recall_grepl_lastname ~ FALSE,
     # strict, !fuzzy, lastname: all right, last name only spelled correctly
[…]

### 2021-08-16 R/score_retrieval_facts.R

@@ -3,6 +3,10 @@
 require(tidyverse)
 require(magrittr)
 
+my_agrepl <- function (pattern, x, max.distance = 0.24, ignore.case = T) {
+  return (coalesce(c(adist(pattern, x, ignore.case = ignore.case)) / nchar(pattern) <= max.distance, FALSE))
+}
+
 unscored <- read_csv(here::here("ignore", "data", "task_retrieval_facts_unscored.csv"))
 
 ## grepl scoring first pass----
@@ -24,6 +28,7 @@ scored <- unscored %>%
            group_trial_num == 13 & category == "musi" & tolower(resp) == "hurdy gurdy" ~ TRUE,
            group_trial_num == 37 & category == "cook" & grepl("orchid", resp, ignore.case = T) ~ TRUE,
            group_trial_num == 38 & category == "cook" & grepl("hen-of-the-woods", resp, ignore.case = T) ~ TRUE,
+           group_trial_num == 16 & category == "dino" & tolower(resp) == "nose" ~ TRUE,
            group_trial_num == 21 & category == "dino" & grepl("medullary", resp, ignore.case = T) ~ TRUE,
            group_trial_num == 36 & category == "dino" & grepl("saw fish", resp, ignore.case = T) ~ TRUE,
            TRUE ~ acc_recall_grepl_strict
@@ -33,39 +38,51 @@ scored <- unscored %>%
                                              # trim non alpha nums so they don't artificially pad the resp length
                                              a <- str_remove_all(a, "[^a-zA-Z\\d\\s-]")
                                              if (b == "medullary bone") b <- "medullary"
-                                             out <- agrepl(b, a, max.distance = 0.3, ignore.case = T)
+                                             out <- my_agrepl(b, a)
                                              return (out)
                                            }
          ),
          # exact spellings of short versions that should get fuzzy credit as well
          # or certain phrases to flag for visual inspection for partial credit
          acc_recall_grepl_fuzzy = case_when(
-           group_trial_num == 1 & category == "gems" & tolower(resp)  %in% c("cleave", "cleavage") ~ TRUE,
-           group_trial_num == 10 & category == "gems" & tolower(resp)  == "knoop" ~ TRUE,
[…]

### 2021-08-16 slides/data_checking.Rmd
just a couple more shits

--- 2021-07-21 slides/data_checking.Rmd
@@
 j_recall %>% 
+  left_join(q_google_demos, by = "subj_num") %>% 
   mutate(acc_recall = as.integer(acc_recall),
-         j_score = j_score - 0.5) %>% 
-  lme4::lmer(resp_conf ~ acc_recall * j_score + (1 + acc_recall | subj_num), data = .) %>% 
+         # so 0.5 is centered
+         j_score = j_score - 0.5,
+         is_male = gender == "male") %>% 
+  lme4::lmer(resp_conf ~ acc_recall * j_score + is_male + (1 + acc_recall | subj_num), data = .) %>% 
   summary()
@@
   ggplot(aes(x = resp, fill = category)) +
-  geom_histogram(position = "identity", alpha = 0.5) +
-  facet_wrap(~subj_num)
+  geom_histogram(position = "identity", binwidth = 5, alpha = 0.5)
+```
+
+---
+
+```{r}
+encoding %>% 
+  ggplot(aes(x = j_score, y = resp, color = category, fill = category)) +
+  geom_jitter(alpha = 0.5) +
+  geom_smooth(formula = y ~ x, method = "lm")
 ```
@@
 encoding %>% 
-  mutate(already_knew = fct_relevel(already_knew, "Did not know this before", "Knew some of this before")) %>% 
+  mutate(already_knew = fct_relevel(already_knew, "none", "some")) %>% 
   ggplot(aes(x = subj_num, fill = already_knew)) +
@@
 
+```{r}
+retrieval %>% 
+  filter(already_knew == "none") %>% 
+  mutate(acc_recall = as.numeric(acc_recall > 0),
+         interest = (interest / 100) - 0.5,
+         j_score = j_score - 0.5) %>% 
+  lme4::glmer(acc_recall ~ interest * j_score + (1 | subj_num), data = ., family = "binomial") %>% 
+  summary()
+```
+
+---
+
 ### Does _source_ retrieval predict _fact_ retrieval?

### 2021-10-12 slides/data_checking.Rmd
needs to be cleaned up but started

@@
   ggplot(aes(x = age, fill = gender)) +
-  geom_histogram(position = "identity", alpha = 0.5)
+  geom_histogram(position = "identity", alpha = 0.5, binwidth = 2)
 ```
@@
 # Trivia expertise assessment
+
+---
+
+### What is our sample spread of trivia expertise?
+
+```{r}
+j_exp %>% 
+  ggplot(aes(x = j_score)) +
+  geom_histogram() +
+  geom_vline(xintercept = 0.7, linetype = "dotted")
+```
 
@@
   scale_fill_viridis_c() +
-  labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
+  labs(x = "Recall confidence",
+       y = "Recall accuracy (strict)",
+       color = "Expertise score",
+       fill = "Expertise score") +
   theme_bw()
@@
 
+### Better experts tend to be more confident
+
+This effect does not necessarily imply that better experts are _overconfident._ Rather, it is consistent with better experts tending to have higher latent knowledge for each question, and thus being likely to be more confident overall, even when the answer turns out to be wrong.
+
 ```{r}
 j_recall %>% 
-  ggplot(aes(x = acc_recall, y = resp_conf, color = j_score, fill = j_score)) + 
-  geom_jitter(alpha = 0.3, width = 0.05) + 
-  geom_smooth(aes(group = subj_num), method = "lm", formula = y ~ x, se = FALSE) + 
+  group_by(subj_num, j_score) %>% 
+  summarize(conf_q500 = median(resp_conf, na.rm = TRUE),
+            conf_q250 = quantile(resp_conf, .25, na.rm = TRUE),
+            conf_q750 = quantile(resp_conf, .75, na.rm = TRUE),
+            conf_q025 = quantile(resp_conf, .025, na.rm = TRUE),
+            conf_q975 = quantile(resp_conf, .975, na.rm = TRUE)) %>% 
+  ggplot(aes(x = subj_num, y = conf_q500, color = j_score)) +
+  # geom_errorbar(aes(ymin = conf_q025, ymax = conf_q975), width = 0, size = 0.5) +
+  geom_errorbar(aes(ymin = conf_q250, ymax = conf_q750), width = 0, size = 1) +
+  geom_point(size = 3) +
+  coord_flip() +
   scale_color_viridis_c() +
-  scale_fill_viridis_c() +
-  labs(x = "Recall accuracy (strict)", y = "Recall confidence", color = "Expertise score", fill = "Expertise score") +
-  theme_bw()
+  theme_bw() +
+  theme(axis.text.y = element_blank())
 ```
@@
 ---
-
-```{r}
-j_recall %>% 
-  left_join(q_google_demos, by = "subj_num") %>% 
-  mutate(acc_recall = as.integer(acc_recall),
-         # so 0.5 is centered
-         j_score = j_score - 0.5,
-         is_male = gender == "male") %>% 
-  lme4::lmer(resp_conf ~ acc_recall * j_score + is_male + (1 + acc_recall | subj_num), data = .) %>% 
-  summary()
-```
-
----
-
-```{r}
-j_recall %>% 
-  left_join(q_google_demos, by = "subj_num") %>% 
-  ggplot(aes(x = resp_conf, y = as.integer(acc_recall), color = gender, fill = gender)) + 
-  geom_jitter(alpha = 0.3, height = 0.05) + 
-  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), se = FALSE) +
-  labs(x = "Recall confidence", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
-  theme_bw()
-```
-
----
-
-```{r}
-j_recall %>% 
-  left_join(q_google_demos, by = "subj_num") %>% 
-  ggplot(aes(x = acc_recall, y = resp_conf, color = gender)) + 
-  geom_jitter(alpha = 0.3, width = 0.05) + 
-  geom_smooth(aes(group = subj_num), method = "lm", formula = y ~ x, se = FALSE, size = 0.5) + 
-  labs(x = "Recall accuracy (strict)", y = "Recall confidence", color = "Expertise score", fill = "Expertise score") +
-  theme_bw()
-```
 
@@
   geom_jitter(alpha = 0.3, height = 0.05) + 
-  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), se = FALSE) + 
   scale_color_viridis_c() +
@@
   theme_bw()
+```
+
+---
+
+### Better experts tend to respond faster
+
+Again, this is consistent with an across-participants tendency to respond faster for subsequently correct answers.
+Better experts who are giving more correct answers are thus more likely to have shorter RTs.
+
+```{r}
+j_recall %>% 
+  group_by(subj_num, j_score) %>% 
+  summarize(rt_q500 = median(rt_end_recall, na.rm = TRUE),
+            rt_q250 = quantile(rt_end_recall, .25, na.rm = TRUE),
+            rt_q750 = quantile(rt_end_recall, .75, na.rm = TRUE),
+            rt_q025 = quantile(rt_end_recall, .025, na.rm = TRUE),
+            rt_q975 = quantile(rt_end_recall, .975, na.rm = TRUE),
+            rt_mean = mean(rt_end_recall, na.rm = TRUE),
+            rt_sd = sd(rt_end_recall, na.rm = TRUE)) %>% 
+  ggplot(aes(x = subj_num, y = rt_mean, color = j_score)) +
+  geom_errorbar(aes(ymin = rt_mean - rt_sd/2, ymax = rt_mean + rt_sd/2), width = 0, size = 1) +
+  geom_point(size = 3) +
+  coord_flip() +
+  scale_color_viridis_c() +
+  theme_bw() +
+  theme(axis.text.y = element_blank())
 ```
@@
 retrieval %>% 
-  # filter(!is.na(already_knew)) %>% 
+  filter(already_knew == "none") %>% 
   mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
@@
   geom_jitter(alpha = 0.3, height = 0.05) + 
-  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
+  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.02) + 
   scale_color_viridis_c() +
@@
   filter(already_knew == "none") %>% 
+  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
+  ggplot(aes(x = resp_pic, y = acc_recall, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) + 
+  geom_jitter(alpha = 0.3, height = 0.05) + 
+  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
+  labs(x = "Photo recognition accuracy", y = "Fact recall accuracy (generous)") +
+  theme_bw()
+```
+
+---
+
+```{r}
+retrieval %>% 
+  filter(already_knew == "none") %>% 
   mutate(acc_recall = as.numeric(acc_recall > 0),
-         interest = (interest / 100) - 0.5,
+         resp_pic = resp_pic / 100,
          j_score = j_score - 0.5) %>% 
-  lme4::glmer(acc_recall ~ interest * j_score + (1 | subj_num), data = ., family = "binomial") %>% 
+  lme4::glmer(acc_recall ~ resp_pic * j_score + (1 | subj_num), data = ., family = "binomial") %>% 
   summary()
@@
 
+```{r}
+retrieval %>% 
+  filter(already_knew == "none") %>% 
+  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall),
+         j_score_binary = j_score > 0.72) %>%
+  ggplot(aes(x = resp_source, y = acc_recall, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
+  geom_jitter(alpha = 0.3, height = 0.05) + 
+  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
+  labs(x = "Source recognition accuracy", y = "Fact recall accuracy (generous)") +
+  theme_bw()
+```
+
+---
+
+```{r}
+retrieval %>% 
+  filter(already_knew == "none") %>% 
+  mutate(acc_recall = as.numeric(acc_recall > 0),
+         resp_source = resp_source / 100,
+         j_score = j_score - 0.5) %>% 
+  lme4::glmer(acc_recall ~ resp_source * j_score + (1 | subj_num), data = ., family = "binomial") %>% 
+  summary()
+```
+
+---
+
 ### Does _source_ retrieval predict _photo_ retrieval?
@@
   scale_fill_viridis_c() +
+  labs(x = "Source recognition accuracy", y = "Photo recognition accuracy") +
+  theme_bw()
+```
+
+---
+
+```{r}
+retrieval %>% 
+  filter(already_knew == "none") %>% 
+  ggplot(aes(x = resp_source, y = resp_pic, color = cut_number(j_score, 5), fill = cut_number(j_score, 5))) + 
+  geom_point(alpha = 0.1) + 
+  geom_smooth( method = "lm", alpha = 0.2) + 
   labs(x = "Source recognition accuracy", y = "Photo recognition accuracy") +
@@
 
+```{r}
+retrieval %>% 
+  filter(already_knew == "none") %>% 
+  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
+  ggplot(aes(x = interest, y = acc_recall, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
+  geom_jitter(alpha = 0.3, height = 0.05) + 
+  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
+  labs(x = "Interest in fact at encoding", y = "Fact recall accuracy (generous)") +
+  theme_bw()
+```
+
+---
+
 ### Does interest at encoding predict _photo_ retrieval?
@@
 retrieval %>% 
-  ggplot(aes(x = interest, y = resp_pic, color = j_score, fill = j_score)) + 
-  geom_point(alpha = 0.3) + 
-  geom_smooth(aes(group = subj_num), method = "lm", se = FALSE) + 
-  scale_color_viridis_c() +
-  scale_fill_viridis_c() +
+  # filter(already_knew == "none") %>% 
+  ggplot(aes(x = interest, y = resp_pic, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
+  geom_point(alpha = 0.1) + 
+  geom_smooth(method = "lm", alpha = 0.2) + 
   labs(x = "Interest in fact at encoding", y = "Photo recognition accuracy") +
@@
 retrieval %>% 
-  ggplot(aes(x = interest, y = resp_source, color = j_score, fill = j_score)) + 
-  geom_point(alpha = 0.3) + 
-  geom_smooth(aes(group = subj_num), method = "lm", se = FALSE) + 
-  scale_color_viridis_c() +
-  scale_fill_viridis_c() +
+  filter(already_knew == "none") %>% 
+  ggplot(aes(x = interest, y = resp_source, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
+  geom_point(alpha = 0.1) + 
+  geom_smooth(method = "lm", alpha = 0.2) + 
   labs(x = "Interest in fact at encoding", y = "Source recognition accuracy") +

### 2021-10-14 slides/data_checking.Rmd
remove setup data loading to helper script

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, dev = "svglite", message = FALSE, warning = FALSE, fig.asp = 3/4)
-require(tidyverse)
-require(magrittr)
+knitr::opts_chunk$set(echo = FALSE,
+                      dev = "svglite",
+                      message = FALSE,
+                      warning = FALSE,
+                      fig.asp = 3/4)
 
-demos_ids <- read_csv(here::here("ignore", "data", "demos_ids.csv"))
-q_google_demos <- read_csv(here::here("ignore", "data", "q_google_demos.csv")) %>% 
-  right_join(demos_ids, by = "demographics_id") %>% 
-  mutate(subj_num = factor(subj_num))
-
-j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv")) %>% 
-  mutate(resp_conf = if_else(is.na(resp_recall), NA_real_, resp_conf))
-
-j_exp <- j_recall %>% 
-  group_by(subj_num) %>% 
-  summarize(j_score = mean(acc_recall))
-
-j_recall %<>%
-  left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-
-j_meta <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_states.csv")) %>% 
-  left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score),
-         resp = fct_relevel(resp, "Learning Memory", after = Inf))
-j_meta_desc <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_descriptions.csv")) %>% 
-  left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-encoding <- read_csv(here::here("ignore", "data", "task_encoding.csv")) %>% 
-  left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score),
-         already_knew = fct_recode(already_knew,
-                               none = "Did not know this before",
-                               some = "Knew some of this before",
-                               all = "Knew all of this before"))
-r_facts <- read_csv(here::here("ignore", "data",  "task_retrieval_facts.csv")) %>% 
-  left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-r_pics <- read_csv(here::here("ignore", "data", "task_retrieval_pics.csv")) %>% 
-  left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-r_source <- read_csv(here::here("ignore", "data", "task_retrieval_source.csv")) %>% 
-  left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-q_trivia_demos  <- read_csv(here::here("ignore", "data", "q_trivia_demos.csv")) %>% 
-  left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
-
-q_posttask  <- read_csv(here::here("ignore", "data", "q_posttask.csv"))
-
-retrieval <- r_facts %>%
-  select(subj_num, j_score, group, group_trial_num, retrieval_block, ep_is_same, sem_is_same, retrieval_trial_num, category, acc_recall, rt_start_recall = rt_start, rt_end_recall = rt_end) %>% 
-  left_join(r_pics %>% 
-              select(subj_num, group, group_trial_num, category, resp_pic = resp, rt_pic = rt)) %>% 
-  left_join(r_source %>%
-              select(subj_num, group, group_trial_num, category, resp_source = resp, rt_source = rt)) %>%
-  left_join(encoding %>% 
-              select(subj_num, group, group_trial_num, category, interest = resp, already_knew)) %>% 
-  mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
-                                          retrieval_block <= 8 ~ "ep_same_sem_diff",
-                                          retrieval_block <= 12 ~ "ep_diff_sem_same",
-                                          retrieval_block <= 16 ~ "ep_diff_sem_diff",
-                                          TRUE ~ NA_character_),
-         encoding_trial_num = if_else(group == "academic",
-                                      group_trial_num * 2 - 1,
-                                      group_trial_num * 2))
+source(here::here("R", "get_cleaned_data.R"))
 ```
@@
   ggplot(aes(x = j_score)) +
-  geom_histogram() +
+  geom_histogram(binwidth = .05) +
   geom_vline(xintercept = 0.7, linetype = "dotted")
+```
+
+---
+
+### Are men and women participants balanced on trivia expertise?
+
+```{r}
+j_exp %>% 
+  mutate(subj_num = factor(subj_num)) %>% 
+  left_join(q_google_demos, by = "subj_num") %>% 
+  ggplot(aes(x = j_score, fill = gender)) +
+  geom_histogram(binwidth = .05, position = "identity", alpha = 0.5) +
+  geom_vline(xintercept = 0.7, linetype = "dotted")
+```
+
+---
+
+### Do older participants know more trivia?
+
+```{r}
+j_exp %>% 
+  mutate(subj_num = factor(subj_num)) %>% 
+  left_join(q_google_demos, by = "subj_num") %>% 
+  ggplot(aes(x = age, y = j_score)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  geom_hline(yintercept = 0.7, linetype = "dotted")
 ```
@@
 
+```{r}
+j_recall %>% 
+  mutate(resp_conf = coalesce(resp_conf, 0), 
+         resp_conf_bin = cut_interval(resp_conf, length = 25, labels = FALSE)) %>% 
+  group_by(subj_num, j_score, resp_conf_bin) %>% 
+  summarize(acc = mean(acc_recall), n_trials = n()) %>% 
+  ggplot(aes(x = resp_conf_bin, y = acc, color = j_score)) + 
+  geom_line(aes(group = subj_num), alpha = 0.5) + 
+  geom_point(aes(size = n_trials), alpha = 0.5) + 
+  scale_color_viridis_c()
+```
+
+---
+
 ### Trivia recall by confidence
+
+I still haven't sorted out the best way to think about this, or how important it really is, we see a vaguely Dunning-Krugery effect where participants with lower overall scores tend to be more wrong at higher confidence.
 
@@
   theme_bw()
-```
-
----
-
-### Better experts tend to be more confident
-
-This effect does not necessarily imply that better experts are _overconfident._ Rather, it is consistent with better experts tending to have higher latent knowledge for each question, and thus being likely to be more confident overall, even when the answer turns out to be wrong.
-
-```{r}
-j_recall %>% 
-  group_by(subj_num, j_score) %>% 
-  summarize(conf_q500 = median(resp_conf, na.rm = TRUE),
-            conf_q250 = quantile(resp_conf, .25, na.rm = TRUE),
-            conf_q750 = quantile(resp_conf, .75, na.rm = TRUE),
-            conf_q025 = quantile(resp_conf, .025, na.rm = TRUE),
-            conf_q975 = quantile(resp_conf, .975, na.rm = TRUE)) %>% 
-  ggplot(aes(x = subj_num, y = conf_q500, color = j_score)) +
-  # geom_errorbar(aes(ymin = conf_q025, ymax = conf_q975), width = 0, size = 0.5) +
-  geom_errorbar(aes(ymin = conf_q250, ymax = conf_q750), width = 0, size = 1) +
-  geom_point(size = 3) +
-  coord_flip() +
-  scale_color_viridis_c() +
-  theme_bw() +
-  theme(axis.text.y = element_blank())
 ```

### 2021-10-14 R/get_cleaned_data.R

@@ -1,0 +1,64 @@
+require(tidyverse)
+require(magrittr)
+
+demos_ids <- read_csv(here::here("ignore", "data", "demos_ids.csv"))
+q_google_demos <- read_csv(here::here("ignore", "data", "q_google_demos.csv")) %>% 
+  right_join(demos_ids, by = "demographics_id") %>% 
+  mutate(subj_num = factor(subj_num))
+
+j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv")) %>% 
+  mutate(resp_conf = if_else(is.na(resp_recall), NA_real_, resp_conf))
+
+j_exp <- j_recall %>% 
+  group_by(subj_num) %>% 
+  summarize(j_score = mean(acc_recall))
+
+j_recall %<>%
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+
+j_meta <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_states.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score),
+         resp = fct_relevel(resp, "Learning Memory", after = Inf))
+j_meta_desc <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_descriptions.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+encoding <- read_csv(here::here("ignore", "data", "task_encoding.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score),
+         already_knew = fct_recode(already_knew,
+                                   none = "Did not know this before",
+                                   some = "Knew some of this before",
+                                   all = "Knew all of this before"))
+r_facts <- read_csv(here::here("ignore", "data",  "task_retrieval_facts.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+r_pics <- read_csv(here::here("ignore", "data", "task_retrieval_pics.csv")) %>% 
+  left_join(j_exp, by = "subj_num") %>% 
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
[…]

### 2021-10-18 slides/data_checking.Rmd
even more cleaning for mariam mtg today

@@
   geom_histogram(binwidth = .05) +
-  geom_vline(xintercept = 0.7, linetype = "dotted")
+  geom_vline(xintercept = 0.7, linetype = "dotted") +
+  labs(x = "Expertise score")
 ```
@@
   geom_histogram(binwidth = .05, position = "identity", alpha = 0.5) +
-  geom_vline(xintercept = 0.7, linetype = "dotted")
+  geom_vline(xintercept = 0.7, linetype = "dotted") +
+  labs(x = "Expertise score")
 ```
@@
   geom_smooth(method = "lm") +
-  geom_hline(yintercept = 0.7, linetype = "dotted")
+  geom_hline(yintercept = 0.7, linetype = "dotted") +
+  labs(y = "Expertise score")
 ```
@@
 
----
-
-```{r}
-j_recall %>% 
-  ggplot(aes(x = rt_end_recall, y = as.integer(acc_recall), color = j_score, fill = j_score)) + 
-  geom_jitter(alpha = 0.3, height = 0.05) + 
-  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), se = FALSE) + 
-  scale_color_viridis_c() +
-  scale_fill_viridis_c() +
-  labs(x = "Recall submit RT", y = "Recall accuracy (strict)", color = "Expertise score", fill = "Expertise score") +
-  theme_bw()
-```
-
----
-
-### Better experts tend to respond faster
-
-Again, this is consistent with an across-participants tendency to respond faster for subsequently correct answers.
-Better experts who are giving more correct answers are thus more likely to have shorter RTs.
-
-```{r}
-j_recall %>% 
-  group_by(subj_num, j_score) %>% 
-  summarize(rt_q500 = median(rt_end_recall, na.rm = TRUE),
-            rt_q250 = quantile(rt_end_recall, .25, na.rm = TRUE),
-            rt_q750 = quantile(rt_end_recall, .75, na.rm = TRUE),
-            rt_q025 = quantile(rt_end_recall, .025, na.rm = TRUE),
-            rt_q975 = quantile(rt_end_recall, .975, na.rm = TRUE),
-            rt_mean = mean(rt_end_recall, na.rm = TRUE),
-            rt_sd = sd(rt_end_recall, na.rm = TRUE)) %>% 
-  ggplot(aes(x = subj_num, y = rt_mean, color = j_score)) +
-  geom_errorbar(aes(ymin = rt_mean - rt_sd/2, ymax = rt_mean + rt_sd/2), width = 0, size = 1) +
-  geom_point(size = 3) +
-  coord_flip() +
-  scale_color_viridis_c() +
-  theme_bw() +
-  theme(axis.text.y = element_blank())
-```
-
----
-
-```{r}
-j_recall %>% 
-  ggplot(aes(x = rt_end_recall, y = resp_conf, color = j_score, fill = j_score)) + 
-  geom_jitter(alpha = 0.3, height = 0.05) + 
-  geom_smooth(aes(group = subj_num), method = "lm", alpha = 0.05) + 
-  scale_color_viridis_c() +
-  scale_fill_viridis_c() +
-  labs(x = "Recall submit RT", y = "Recall confidence", color = "Expertise score", fill = "Expertise score") +
-  theme_bw()
-```
-
----
-
 ### Metamemory state counts
@@
   left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
-  mutate(acc_recall = recode(as.character(acc_recall),
-                             `FALSE` = "incorrect",
-                             `TRUE` = "correct")) %>% 
+  filter(acc_recall) %>% 
   ggplot(aes(x = subj_num, fill = resp)) +
   geom_bar() +
-  scale_x_discrete(guide = guide_axis(angle = 30)) +
-  facet_grid(~acc_recall) +
   labs(x = "Participant", y = "# facts labeled with that memory state", fill = "Memory state") +
-  theme_bw()
+  theme_bw() +
+  theme(axis.text.x = element_blank(),
+        legend.position = 0:1,
+        legend.justification = 0:1,
+        legend.background = element_blank())
 ```
@@
   left_join(j_recall %>% select(subj_num, answer, acc_recall)) %>% 
-  mutate(acc_recall = recode(as.character(acc_recall),
-                             `FALSE` = "incorrect",
-                             `TRUE` = "correct")) %>% 
-  count(subj_num, acc_recall, resp) %>% 
-  group_by(subj_num, acc_recall) %>% 
+  filter(acc_recall) %>% 
+  count(subj_num, resp) %>% 
+  group_by(subj_num) %>% 
   mutate(prob = n / sum(n)) %>% 
@@
   geom_col() +
-  scale_x_discrete(guide = guide_axis(angle = 30)) +
-  facet_grid(~acc_recall) +
   labs(x = "Participant", y = "Percent facts labeled with that memory state", fill = "Memory state") +
-  theme_bw()
-```
-
----
-
-### Metamemory descriptions: Guess
-
-```{r, results = "asis"}
-j_meta_desc %>%
-  filter(question == "Guess") %>% 
-  arrange(subj_num) %>% 
-  pull(resp) %>% 
-  paste0(">", .) %>% 
-  cat(sep = "\n\n")
-```
-
----
-
-### Metamemory descriptions: Just Know
-
-```{r, results = "asis"}
-j_meta_desc %>%
-  filter(question == "Just Know") %>% 
-  arrange(subj_num) %>% 
-  pull(resp) %>% 
-  paste0(">", .) %>% 
-  cat(sep = "\n\n")
-```
-
----
-
-### Metamemory descriptions: Related Memory
-
-```{r, results = "asis"}
-j_meta_desc %>%
-  filter(question == "Related Memory") %>% 
-  arrange(subj_num) %>% 
-  pull(resp) %>% 
-  paste0(">", .) %>% 
-  cat(sep = "\n\n")
-```
-
----
-
-### Metamemory descriptions: Learning Memory
-
-```{r, results = "asis"}
-j_meta_desc %>%
-  filter(question == "Learning Memory") %>% 
-  arrange(subj_num) %>% 
-  pull(resp) %>% 
-  paste0(">", .) %>% 
-  cat(sep = "\n\n")
+  theme_bw() +
+  theme(axis.text.x = element_blank())
 ```
@@
   pivot_longer(cols = -subj_num, names_to = "var", values_to = "value") %>% 
-  ggplot(aes(x = value)) + geom_histogram() + facet_wrap(~ var)
+  ggplot(aes(x = value)) + 
+  geom_histogram() + 
+  facet_wrap(~ var)
 ```
@@
 
+### How many people got which categories?
+
 ```{r}
 encoding %>% 
-  ggplot(aes(x = resp, fill = category)) +
-  geom_histogram(position = "identity", binwidth = 5, alpha = 0.5)
+  distinct(subj_num, group, category) %>% 
+  mutate(category = fct_relevel(category, "arms", "gems", "musi")) %>% 
+  ggplot(aes(x = category, fill = group)) +
+  geom_bar() +
+  theme(legend.position = 0:1, legend.justification = 0:1, legend.background = element_blank())
+```
+
+---
+
+### Are some categories more interesting than others?
+
+```{r}
+encoding %>% 
+  group_by(group_trial_num, category) %>% 
+  summarize(interest_mean = mean(resp), interest_sd = sd(resp)) %>% 
+  ggplot(aes(x = interest_mean, fill = category)) +
+  geom_density(alpha = 0.5) +
+  labs(x = "Mean (across Ps) interest rating for each fact") +
+  theme(legend.position = 0:1,
+        legend.justification = 0:1,
+        legend.background = element_blank(),
+        legend.direction = "horizontal")
+```
+
+---
+
+### Are trivia experts more interested overall?
+
+```{r}
+encoding %>% 
+  group_by(subj_num, j_score) %>% 
+  summarize(resp = mean(resp)) %>% 
+  ggplot(aes(x = j_score, y = resp)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  labs(x = "Expertise score",
+       y = "P's mean interest (across facts)")
 ```
@@
 encoding %>% 
-  ggplot(aes(x = j_score, y = resp, color = category, fill = category)) +
-  geom_jitter(alpha = 0.5) +
-  geom_smooth(formula = y ~ x, method = "lm")
-```
-
----
-
-```{r}
-encoding %>% 
-  ggplot(aes(x = resp, y = rt, color = j_score, fill = j_score)) +
-  geom_point() +
-  geom_smooth(aes(group = subj_num), method = "lm", se = FALSE) +
-  scale_colour_viridis_c() +
-  scale_fill_viridis_c()
-```
-
----
-
-```{r}
-encoding %>% 
-  mutate(already_knew = fct_relevel(already_knew, "none", "some")) %>% 
-  ggplot(aes(x = subj_num, fill = already_knew)) +
+  ggplot(aes(x = subj_num, fill = fct_rev(already_knew))) +
   geom_bar() +
+  geom_hline(yintercept = 40, linetype = "dotted") +
   scale_x_discrete(guide = guide_axis(angle = 30)) +
-  labs(x = "Participant", y = "# facts already knew", fill = "Prior knowledge") +
-  theme_bw()
+  labs(x = "Participant (expertise low to high)", y = "# facts already knew", fill = "Prior knowledge") +
+  theme_bw() +
+  theme(axis.text.x = element_blank())
 ```
@@
 ```{r}
-retrieval %>% 
+retrieval_temp <- retrieval %>% 
+  nest(data = -subj_num) %>% 
+  slice_sample(n = 8) %>% 
+  unnest(data)
+
+retrieval_temp %>% 
   ggplot(aes(x = retrieval_trial_num, y = acc_recall)) +
   geom_rect(aes(x = NULL, y = NULL, xmin = xmin, xmax = xmax, fill = retrieval_block_type),
-            data = retrieval %>%
+            data = retrieval_temp %>%
               select(subj_num, retrieval_block, retrieval_trial_num, retrieval_block_type) %>%
@@
 
-### Fact recall by already knew status
+### Is recall higher when people already know (some of) the facts?
 
@@
 retrieval %>% 
-  mutate(acc_recall = if_else(acc_recall > 0, 1, 0)) %>% 
   filter(!is.na(already_knew)) %>% 
-  ggplot(aes(x = subj_num, fill = factor(acc_recall))) +
-  geom_bar() +
-  facet_grid(~already_knew)
-```
-
----
-
-```{r}
-retrieval %>% 
-  mutate(acc_recall = if_else(acc_recall > 0, 1, 0)) %>% 
-  filter(!is.na(already_knew)) %>% 
-  count(subj_num, acc_recall, already_knew) %>% 
   group_by(subj_num, already_knew) %>% 
-  mutate(prob = n / sum(n)) %>% 
-  ggplot(aes(x = subj_num, y = prob, fill = factor(acc_recall))) +
-  geom_col() +
-  facet_grid(~already_knew)
-```
-
----
-
-### Fact recall by ENCODING question order
-
-```{r}
-retrieval %>% 
-  nest(data = -subj_num) %>% 
-  sample_n(10) %>% 
-  unnest(data) %>% 
-  mutate(encoding_trial_num = if_else(group == "academic", group_trial_num * 2 - 1, group_trial_num * 2)) %>% 
-  ggplot(aes(x = retrieval_trial_num, y = acc_recall)) +
-  geom_line() +
-  geom_point(aes(color = already_knew)) +
-  # scale_colour_viridis_b() +
-  scale_y_continuous(n.breaks = 3) +
-  facet_grid(subj_num ~ .) +
-  labs(x = "Encoding trial (beginning to end)", y = "Subsequent fact recall accuracy") +
-  theme_bw()
+  summarize(acc_recall = mean(acc_recall)) %>% 
+  ggplot(aes(x = already_knew, y = acc_recall)) +
+  geom_violin() +
+  labs(x = "Fact prior knowledge at encoding", y = "% correct recall")
 ```
@@
 
-Current setup: A-A' 2AFC with similar lure
+A-A' 2AFC with similar lure
 
@@
 r_pics %>%
-  ggplot(aes(x = factor(subj_num), y = resp, color = j_score)) +
-  geom_hline(yintercept = 0, linetype = "dotted") +
-  geom_boxplot() +
-  scale_colour_viridis_c() +
-  guides(color = FALSE) +
-  labs(x = "Participant", y = "Accuracy with confidence (positive = correct)") +
-  theme_bw()
+  group_by(subj_num, j_score) %>% 
+  mutate(acc = mean(resp)) %>% 
+  ggplot(aes(x = j_score, y = acc)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  labs(x = "Expertise score", y = " Mean accuracy with confidence")
 ```
@@
 r_source %>%
-  ggplot(aes(x = factor(subj_num), y = resp, color = j_score)) +
-  geom_hline(yintercept = 0, linetype = "dotted") +
-  geom_boxplot() +
-  scale_colour_viridis_c() +
-  guides(color = FALSE) +
-  labs(x = "Participant", y = "Accuracy with confidence (positive = correct)") +
-  theme_bw()
+  group_by(subj_num, j_score) %>% 
+  mutate(acc = mean(resp)) %>% 
+  ggplot(aes(x = j_score, y = acc)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  labs(x = "Expertise score", y = " Mean accuracy with confidence")
 ```
@@
   mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
-  ggplot(aes(x = resp_pic, y = acc_recall, color = j_score, fill = j_score)) + 
+  ggplot(aes(x = resp_pic, y = acc_recall, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) + 
   geom_jitter(alpha = 0.3, height = 0.05) + 
-  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.02) + 
-  scale_color_viridis_c() +
-  scale_fill_viridis_c() +
-  # facet_grid(~already_knew) +
-  labs(x = "Photo recognition accuracy", y = "Fact recall accuracy (generous)") +
-  theme_bw()
+  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
+  labs(x = "Photo recognition accuracy",
+       y = "Fact recall accuracy (generous)",
+       color = "Expertise tertile",
+       fill = "Expertise tertile") +
+  theme(legend.position = c(0, 0.75),
+        legend.justification = c(0, 0.75),
+        legend.background = element_blank())
 ```
@@
 
-```{r}
-retrieval %>% 
-  filter(already_knew == "none") %>% 
-  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
-  ggplot(aes(x = resp_pic, y = acc_recall, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) + 
-  geom_jitter(alpha = 0.3, height = 0.05) + 
-  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
-  labs(x = "Photo recognition accuracy", y = "Fact recall accuracy (generous)") +
-  theme_bw()
-```
-
----
+### Does _photo_ retrieval predict _fact_ retrieval?
 
@@
          resp_pic = resp_pic / 100,
-         j_score = j_score - 0.5) %>% 
-  lme4::glmer(acc_recall ~ resp_pic * j_score + (1 | subj_num), data = ., family = "binomial") %>% 
+         j_score = j_score - 0.7) %>% 
+  lme4::glmer(acc_recall ~ resp_pic * j_score + (1 + resp_pic | subj_num), data = ., family = "binomial") %>%
   summary()
@@
 retrieval %>% 
+  filter(already_knew == "none") %>% 
   mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
-  ggplot(aes(x = resp_source, y = acc_recall, color = j_score, fill = j_score)) + 
+  ggplot(aes(x = resp_source,
+             y = acc_recall,
+             color = cut_number(j_score, 3),
+             fill = cut_number(j_score, 3))) + 
   geom_jitter(alpha = 0.3, height = 0.05) + 
-  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
-  scale_color_viridis_c() +
-  scale_fill_viridis_c() +
-  labs(x = "Source recognition accuracy", y = "Fact recall accuracy (generous)") +
-  theme_bw()
+  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
+  labs(x = "Source recognition accuracy",
+       y = "Fact recall accuracy (generous)",
+       color = "Expertise tertile",
+       fill = "Expertise tertile") +
+  theme(legend.position = c(0, 0.75),
+        legend.justification = c(0, 0.75),
+        legend.background = element_blank())
 ```
@@
 
-```{r}
-retrieval %>% 
-  filter(already_knew == "none") %>% 
-  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall),
-         j_score_binary = j_score > 0.72) %>%
-  ggplot(aes(x = resp_source, y = acc_recall, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
-  geom_jitter(alpha = 0.3, height = 0.05) + 
-  geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
-  labs(x = "Source recognition accuracy", y = "Fact recall accuracy (generous)") +
-  theme_bw()
-```
-
----
+### Does _source_ retrieval predict _fact_ retrieval?
 
@@
          resp_source = resp_source / 100,
-         j_score = j_score - 0.5) %>% 
-  lme4::glmer(acc_recall ~ resp_source * j_score + (1 | subj_num), data = ., family = "binomial") %>% 
+         j_score = j_score - 0.7) %>% 
+  lme4::glmer(acc_recall ~ resp_source * j_score + (1 + resp_source | subj_num),
+              data = ., family = "binomial") %>% 
   summary()
@@
 retrieval %>% 
-  ggplot(aes(x = resp_source, y = resp_pic, color = j_score, fill = j_score)) + 
-  geom_point(alpha = 0.3) + 
-  geom_smooth(aes(group = subj_num), method = "lm", se = FALSE) + 
-  scale_color_viridis_c() +
-  scale_fill_viridis_c() +
-  labs(x = "Source recognition accuracy", y = "Photo recognition accuracy") +
-  theme_bw()
+  filter(already_knew == "none") %>% 
+  ggplot(aes(x = resp_source, y = resp_pic, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) +
+  geom_point(alpha = 0.1) + 
+  geom_smooth( method = "lm", alpha = 0.2) + 
+  labs(x = "Source recognition accuracy",
+       y = "Photo recognition accuracy",
+       color = "Expertise tertile",
+       fill = "Expertise tertile") +
+  theme(legend.position = c(0, 0.5),
+        legend.justification = c(0, 0.5),
+        legend.background = element_blank())
 ```
@@
 
+### Does _source_ retrieval predict _photo_ retrieval?
+
 ```{r}
@@
   filter(already_knew == "none") %>% 
-  ggplot(aes(x = resp_source, y = resp_pic, color = cut_number(j_score, 5), fill = cut_number(j_score, 5))) + 
-  geom_point(alpha = 0.1) + 
-  geom_smooth( method = "lm", alpha = 0.2) + 
-  labs(x = "Source recognition accuracy", y = "Photo recognition accuracy") +
-  theme_bw()
+  mutate(resp_pic = resp_pic / 100,
+         resp_source = resp_source / 100,
+         j_score = j_score - 0.7) %>% 
+  lme4::lmer(resp_pic ~ resp_source * j_score + (1 + resp_source | subj_num),
+              data = .) %>% 
+  summary()
 ```
@@
 retrieval %>% 
-  mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
-  ggplot(aes(x = interest, y = acc_recall, color = j_score, fill = j_score)) + 
-  geom_jitter(alpha = 0.3, height = 0.05) + 
-  geom_smooth(aes(group = subj_num), method = "glm", method.args = list(family = "binomial"), alpha = 0.05) + 
-  scale_color_viridis_c() +
-  scale_fill_viridis_c() +
-  labs(x = "Interest in fact at encoding", y = "Fact recall accuracy (generous)") +
-  theme_bw()
-```
-
----
-
-```{r}
-retrieval %>% 
   filter(already_knew == "none") %>% 
   mutate(acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
-  ggplot(aes(x = interest, y = acc_recall, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
+  ggplot(aes(x = interest, y = acc_recall, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) + 
   geom_jitter(alpha = 0.3, height = 0.05) + 
   geom_smooth( method = "glm", method.args = list(family = "binomial"), alpha = 0.2) + 
-  labs(x = "Interest in fact at encoding", y = "Fact recall accuracy (generous)") +
-  theme_bw()
+  labs(x = "Interest in fact at encoding",
+       y = "Fact recall accuracy (generous)",
+       color = "Expertise tertile",
+       fill = "Expertise tertile") +
+  theme(legend.position = c(0, 0.75),
+        legend.justification = c(0, 0.75),
+        legend.background = element_blank())
 ```
@@
 retrieval %>% 
-  # filter(already_knew == "none") %>% 
-  ggplot(aes(x = interest, y = resp_pic, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
+  filter(already_knew == "none") %>% 
+  ggplot(aes(x = interest, y = resp_pic, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) + 
   geom_point(alpha = 0.1) + 
   geom_smooth(method = "lm", alpha = 0.2) + 
-  labs(x = "Interest in fact at encoding", y = "Photo recognition accuracy") +
-  theme_bw()
+  labs(x = "Interest in fact at encoding",
+       y = "Photo recognition accuracy",
+       color = "Expertise tertile",
+       fill = "Expertise tertile") +
+  theme(legend.position = c(0, 0.5),
+        legend.justification = c(0, 0.5),
+        legend.background = element_blank())
 ```
@@
   filter(already_knew == "none") %>% 
-  ggplot(aes(x = interest, y = resp_source, color = cut_number(j_score, 4), fill = cut_number(j_score, 4))) + 
+  ggplot(aes(x = interest, y = resp_source, color = cut_number(j_score, 3), fill = cut_number(j_score, 3))) + 
   geom_point(alpha = 0.1) + 
   geom_smooth(method = "lm", alpha = 0.2) + 
-  labs(x = "Interest in fact at encoding", y = "Source recognition accuracy") +
-  theme_bw()
+  labs(x = "Interest in fact at encoding",
+       y = "Source recognition accuracy",
+       color = "Expertise tertile",
+       fill = "Expertise tertile") +
+  theme(legend.position = c(0, 0.5),
+        legend.justification = c(0, 0.5),
+        legend.background = element_blank())
 ```
-
----
-
-class: inverse, middle
-
-# STOP! Dirty graphs ahead
-
----
-
-```{r}
-retrieval %>% 
-  ggplot(aes(x = log(rt_pic), y = resp_pic)) + 
-  geom_point() + 
-  geom_smooth(method = "lm") + 
-  facet_wrap(~subj_num, scales = "free_x")
-```
-
-```{r}
-retrieval %>% 
-  ggplot(aes(x = log(rt_source), y = resp_source)) + 
-  geom_point() + 
-  geom_smooth(method = "lm") + 
-  facet_wrap(~subj_num, scales = "free_x")
-```

### 2021-10-18 R/get_cleaned_data.R
move general cleaned data loading to own script

@@ -24,13 +24,16 @@ j_meta <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_states.csv")
 j_meta_desc <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_descriptions.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
+
 encoding <- read_csv(here::here("ignore", "data", "task_encoding.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score),
          already_knew = fct_recode(already_knew,
                                    none = "Did not know this before",
                                    some = "Knew some of this before",
-                                   all = "Knew all of this before"))
+                                   all = "Knew all of this before"),
+         already_knew = fct_relevel(already_knew, "all", after = Inf))
+
 r_facts <- read_csv(here::here("ignore", "data",  "task_retrieval_facts.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
   mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
@@ -54,11 +57,16 @@ retrieval <- r_facts %>%
               select(subj_num, group, group_trial_num, category, resp_source = resp, rt_source = rt)) %>%
   left_join(encoding %>% 
               select(subj_num, group, group_trial_num, category, interest = resp, already_knew)) %>% 
-  mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
-                                          retrieval_block <= 8 ~ "ep_same_sem_diff",
-                                          retrieval_block <= 12 ~ "ep_diff_sem_same",
-                                          retrieval_block <= 16 ~ "ep_diff_sem_diff",
+  mutate(retrieval_block_type = case_when(ep_is_same == 1 & sem_is_same == 1 ~ "ep_same_sem_same",
+                                          ep_is_same == 1 & sem_is_same == 0 ~ "ep_same_sem_diff",
+                                          ep_is_same == 0 & sem_is_same == 1 ~ "ep_diff_sem_same",
+                                          ep_is_same == 0 & sem_is_same == 0 ~ "ep_diff_sem_diff",
                                           TRUE ~ NA_character_),
+  #mutate(retrieval_block_type = case_when(retrieval_block <= 4 ~ "ep_same_sem_same",
+   #                                       retrieval_block <= 8 ~ "ep_same_sem_diff",
[…]

### 2022-07-01 slides/data_checking.Rmd

@@
                       warning = FALSE,
-                      fig.asp = 3/4)
+                      fig.asp = 7/10)
 
@@
 
+???
+
+Check whether category assignment is related to expertise
+
 ---
@@
 
+Now filtered to include only not-previously-known facts
+
 ```{r}
-r_facts %>% 
+retrieval %>% 
+  filter(already_knew == "none") %>% 
   mutate(ep_is_same = recode(ep_is_same,
@@
 ```
+
+???
+
+Fix this graph to filter for didn't already know
+
+Look at RT measures as a function of chunk type! Difference between start and finish normalized by answer length?
 
@@
 ```{r}
+this_cor <- r_pics %>%
+  group_by(subj_num, j_score) %>% 
+  summarize(acc = mean(resp)) %$% 
+  cor(j_score, acc) %>% 
+  round(2)
+```
+
+Pearson correlation shown: `r this_cor`
+
+```{r}
 r_pics %>%
   group_by(subj_num, j_score) %>% 
-  mutate(acc = mean(resp)) %>% 
+  summarize(acc = mean(resp)) %>% 
   ggplot(aes(x = j_score, y = acc)) +
@@
   geom_smooth(method = "lm") +
-  labs(x = "Expertise score", y = " Mean accuracy with confidence")
+  labs(x = "Expertise score", y = " Mean accuracy WITH confidence (-50 to 50)")
+```
+
+---
+
+### Photo recognition
+
+A-A' 2AFC with similar lure
+
+```{r}
+this_cor <- r_pics %>%
+  group_by(subj_num, j_score) %>% 
+  summarize(acc = mean(resp_binary)) %$% 
+  cor(j_score, acc) %>% 
+  round(2)
+```
+
+Pearson correlation shown: `r this_cor`
+
+```{r}
+r_pics %>%
+  group_by(subj_num, j_score) %>% 
+  summarize(acc = mean(resp_binary)) %>% 
+  ggplot(aes(x = j_score, y = acc)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)")
 ```
@@
 ```{r}
+this_cor <- r_source %>%
+  group_by(subj_num, j_score) %>% 
+  summarize(acc = mean(resp)) %$% 
+  cor(j_score, acc) %>% 
+  round(2)
+```
+
+Pearson correlation shown: `r this_cor`
+
+```{r}
 r_source %>%
   group_by(subj_num, j_score) %>% 
-  mutate(acc = mean(resp)) %>% 
+  summarize(acc = mean(resp)) %>% 
   ggplot(aes(x = j_score, y = acc)) +
@@
   geom_smooth(method = "lm") +
-  labs(x = "Expertise score", y = " Mean accuracy with confidence")
+  labs(x = "Expertise score", y = " Mean accuracy WITH confidence (-50 to 50)")
+```
+
+---
+
+### Source memory for which museum
+
+```{r}
+this_cor <- r_source %>%
+  group_by(subj_num, j_score) %>% 
+  summarize(acc = mean(resp_binary)) %$% 
+  cor(j_score, acc) %>% 
+  round(2)
+```
+
+Pearson correlation shown: `r this_cor`
+
+```{r}
+r_source %>%
+  group_by(subj_num, j_score) %>% 
+  summarize(acc = mean(resp_binary)) %>% 
+  ggplot(aes(x = j_score, y = acc)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)")
 ```
@@
 ```
+
+???
+
+Sanity check these against the apparent effect where high experts seem to be doing worse on photo memory?
 
@@
 ```
+
+???
+
+Sanity check this one as well
 
@@
 
+???
+
+Include interest in the other models
+
 ---

### 2022-07-05 slides/data_checking.Rmd
update pkgs for prelim results slides

@@
   mutate(category = fct_relevel(category, "arms", "gems", "musi")) %>% 
-  ggplot(aes(x = category, fill = group)) +
+  ggplot(aes(x = group, fill = category)) +
   geom_bar() +
+  geom_text(aes(label = category), stat = "count", vjust = 1.5, colour = "white") +
   theme(legend.position = 0:1, legend.justification = 0:1, legend.background = element_blank())
@@
   group_by(subj_num, j_score) %>% 
-  summarize(resp = mean(resp)) %>% 
+  summarize(resp = median(resp)) %>% 
   ggplot(aes(x = j_score, y = resp)) +
@@
   labs(x = "Expertise score",
-       y = "P's mean interest (across facts)")
+       y = "P's median interest (across facts)")
 ```
@@
 
-Pearson correlation shown: `r this_cor`
-
 ```{r}
@@
   geom_smooth(method = "lm") +
-  labs(x = "Expertise score", y = " Mean accuracy WITH confidence (-50 to 50)")
+  labs(x = "Expertise score", y = "Mean accuracy WITH confidence (-50 to 50)",
+       title = paste("Pearson correlation:", this_cor))
 ```
@@
   geom_smooth(method = "lm") +
-  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)")
+  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)",
+       title = paste("Pearson correlation:", this_cor))
 ```
@@
   geom_smooth(method = "lm") +
-  labs(x = "Expertise score", y = " Mean accuracy WITH confidence (-50 to 50)")
+  labs(x = "Expertise score", y = " Mean accuracy WITH confidence (-50 to 50)",
+       title = paste("Pearson correlation:", this_cor))
 ```

### 2022-07-05 slides/results.Rmd
update pkgs for prelim results slides

---
title: "Preliminary (quick and dirty) results"
subtitle: "J-Study"  
author: 
  - "Monica Thieu"
  - "Lauren Wilkins"
institute: "Columbia University Dept of Psychology"
date: 'Updated: `r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  dev = "svglite", fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)

require(xaringanthemer)
source(here::here("R", "get_cleaned_data.R"))
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
style_mono_accent(
  base_color = "#0046a6"
)
```

class: inverse, middle

# Demographics

---

### More men than women, but age does not appear correlated with gender

```{r}
q_google_demos %>% 
  ggplot(aes(x = age, fill = gender)) +
  geom_histogram(position = "identity", alpha = 0.5, binwidth = 2) +
  scale_y_continuous(breaks = scales::breaks_extended(6))
```

---

### What is our sample spread of trivia expertise?

```{r}
j_exp %>% 
  ggplot(aes(x = j_score)) +
  geom_histogram(binwidth = .05) +
  geom_vline(xintercept = 0.7, linetype = "dotted") +
  annotate("text",
           x = .67,
           y = 20,
           label = "Approx cutoff for Jeopardy callback",
           hjust = 1) +
  labs(x = "Expertise score (fraction correct out of 50 questions)",
       y = "count")
```

---

class: inverse, middle

# Encoding

---

### Trivia experts tend to know more encoding facts already

```{r}
encoding %>% 
  group_by(subj_num, j_score, group) %>% 
  summarize(pct_novel = sum(!is.na(already_knew) & already_knew == "none")) %>% 
  ggplot(aes(x = j_score, y = pct_novel, color = group, fill = group)) +
  geom_hline(yintercept = 40, linetype = "dotted") +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Trivia expertise", y = "# museum facts rated as novel") +
  theme_bw()
```

---

### Trivia experts might be more interested at encoding, but not by much

```{r}
this_cor <- encoding %>%
  group_by(subj_num, j_score) %>% 
  summarize(interest = median(resp)) %$% 
  cor(j_score, interest) %>% 
  round(2)
```

```{r}
encoding %>% 
  group_by(subj_num, j_score) %>% 
  summarize(resp_median = median(resp),
            q25 = quantile(resp, .25),
            q75 = quantile(resp, .75)) %>% 
  ggplot(aes(x = j_score, y = resp_median)) +
  geom_errorbar(aes(ymin = q25, ymax = q75), width = 0, alpha = 0.5) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score",
       y = "P's median interest (across facts)") +
  theme_bw()
```

---

### Trivia experts might be more interested at encoding, but not by much

Quick and dirty maximum-likelihood linear regression

Formula: `interest ~ j_score + already_knew + (1 | subj_num)`

```{r}
encoding %>% 
  mutate(j_score = j_score - 0.7) %>% 
  lme4::lmer(resp ~ j_score + already_knew + (1 | subj_num), data = .) %>% 
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

---

class: inverse, middle

# Retrieval

---

### Recall is higher when people already know the facts (duh)

Accordingly, all subsequent results involving fact retrieval are shown only for facts rated as novel at encoding.

Excluding facts known at encoding should not introduce collider bias into the retrieval results, because recall cannot cause prior knowledge at encoding.

```{r}
retrieval %>% 
  filter(!is.na(already_knew)) %>% 
  group_by(subj_num, already_knew) %>% 
  summarize(acc_recall = mean(acc_recall)) %>% 
  ggplot(aes(x = already_knew, y = acc_recall)) +
  geom_violin() +
  labs(x = "Fact prior knowledge at encoding", y = "% correct recall") +
  theme_bw()
```

---

### Trivia experts show better recall for novel facts

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  group_by(subj_num, j_score) %>% 
  summarize(acc_recall = mean(acc_recall)) %>% 
  ggplot(aes(x = j_score, y = acc_recall)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = "% correct recall for novel facts") +
  theme_bw()
```

---

### Trivia experts' fact recall is _not_ driven by interest at encoding

.pull-left[

Formula: `acc_recall ~ j_score + (1 | subj_num)`

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         j_score = j_score - 0.7) %>% 
  lme4::glmer(acc_recall ~ j_score + (1 | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

]

.pull-right[

Formula: `acc_recall ~ j_score + interest + (1 + interest | subj_num)`

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         j_score = j_score - 0.7,
         interest = (interest / 100) - 0.5) %>% 
  lme4::glmer(acc_recall ~ j_score + interest + (1 + interest | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

]

---

### Trivia experts _don't_ show better photo memory

```{r}
retrieval %>%
  mutate(across(c(resp_pic, resp_source),
                ~if_else(. > 0, 1L, 0L))) %>% 
  group_by(subj_num, j_score) %>% 
  summarize(acc_pic = mean(resp_pic),
            acc_source = mean(resp_source)) %>% 
  pivot_longer(cols = starts_with("acc"),
               names_to = "memory_type",
               values_to = "acc",
               names_prefix = "acc_") %>% 
  ggplot(aes(x = j_score, y = acc, color = memory_type, fill = memory_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)") +
  theme_bw()
```

---

### _Photo_ recognition predicts _fact_ recall, slightly more so for experts

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  group_by(subj_num, j_score, resp_pic) %>%
  summarize(acc_recall = mean(acc_recall)) %>% 
  ggplot(aes(x = resp_pic, y = acc_recall, color = fct_rev(cut_number(j_score, 3)), fill = fct_rev(cut_number(j_score, 3)))) + 
  geom_line(aes(group = subj_num), alpha = 0.1) +
  geom_smooth(method = "lm", alpha = 0.2) + 
  scale_x_continuous(breaks = 0:1) +
  scale_color_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
  scale_fill_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
  labs(x = "Photo recognition accuracy",
       y = "Fact recall accuracy (generous)",
       color = "Expertise tertile",
       fill = "Expertise tertile") +
  theme_bw()
```

---

### _Photo_ recognition predicts _fact_ recall, slightly more so for experts

Quick and dirty maximum-likelihood logistic regression

Formula: `acc_recall ~ resp_pic * j_score + (1 + resp_pic | subj_num)`

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         j_score = j_score - 0.7) %>% 
  lme4::glmer(acc_recall ~ resp_pic * j_score + (1 + resp_pic | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

---

### _Source_ recognition predicts _fact_ recall for everyone

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  group_by(subj_num, j_score, resp_source) %>%
  summarize(acc_recall = mean(acc_recall)) %>% 
  ggplot(aes(x = resp_source, y = acc_recall, color = fct_rev(cut_number(j_score, 3)), fill = fct_rev(cut_number(j_score, 3)))) + 
  geom_line(aes(group = subj_num), alpha = 0.1) +
  geom_smooth(method = "lm", alpha = 0.2) + 
  scale_x_continuous(breaks = 0:1) +
  scale_color_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
  scale_fill_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
  labs(x = "Source recognition accuracy",
       y = "Fact recall accuracy (generous)",
       color = "Expertise tertile",
       fill = "Expertise tertile") +
  theme_bw()
```

---

### _Source_ recognition predicts _fact_ recall for everyone

Quick and dirty maximum-likelihood logistic regression

Formula: `acc_recall ~ resp_source * j_score + (1 + resp_source | subj_num)`

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         j_score = j_score - 0.7) %>% 
  lme4::glmer(acc_recall ~ resp_source * j_score + (1 + resp_source | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

### 2022-07-06 slides/data_checking.Rmd
add j recall acc by metamemory state per pereverseff

@@
 
-### Metamemory state counts
+### Metamemory state counts (correct trials only!)
 
@@
   geom_bar() +
-  labs(x = "Participant", y = "# facts labeled with that memory state", fill = "Memory state") +
+  labs(x = "Participant", y = "# correctly recalled facts labeled with that memory state", fill = "Memory state") +
   theme_bw() +
@@
         legend.background = element_blank())
+```
+
+---
+
+### Recall accuracy by metamemory state
+
+```{r}
+j_recall %>%
+  select(subj_num, j_score, question, answer, acc_recall) %>%
+  left_join(j_meta %>% select(subj_num, question, answer, metamemory = resp),
+            by = c("subj_num", "question", "answer")) %>%
+  mutate(metamemory = coalesce(metamemory, "Don't Know")) %>%
+  group_by(subj_num, metamemory) %>%
+  summarize(acc = mean(acc_recall),
+            n_trials = n()) %>%
+  ggplot(aes(x = metamemory, y = acc)) +
+  geom_boxplot()
 ```

### 2022-07-06 slides/results.Rmd
update fonts to google fonts from manual theme

@@
 style_mono_accent(
-  base_color = "#0046a6"
+  base_color = "#0046a6",
+  text_font_google = google_font("Lora"),
+  header_font_google = google_font("Nunito"),
+  code_font_google = google_font("Fira Code")
 )
@@
 q_google_demos %>% 
-  ggplot(aes(x = age, fill = gender)) +
+  left_join(q_google_demos %>%
+              count(gender) %>%
+              mutate(gender_n = glue::glue("{gender} (n = {n})")) %>%
+              select(-n),
+            by = "gender") %>% 
+  ggplot(aes(x = age, fill = gender_n)) +
   geom_histogram(position = "identity", alpha = 0.5, binwidth = 2) +
@@
 retrieval %>%
+  # filter(already_knew == "none") %>% 
   mutate(across(c(resp_pic, resp_source),

### 2022-10-13 slides/data_checking.Rmd
catching up on much older work history

@@
 output:
-  xaringan::moon_reader:
-    css: ["theme.css", "fonts.css"]
-    lib_dir: libs
-    nature:
-      highlightStyle: github
-      highlightLines: true
-      countIncrementalSlides: false
+  html_document:
+    toc: true
 ---
@@
 knitr::opts_chunk$set(echo = FALSE,
-                      dev = "svglite",
                       message = FALSE,
-                      warning = FALSE,
-                      fig.asp = 7/10)
+                      warning = FALSE)
 
@@
 
-class: inverse, middle
-
 # Demographics
 
----
-
-### What is the age and gender breakdown?
+What is the age and gender breakdown?
 
@@
 
----
-
-class: inverse, middle
-
 # Trivia expertise assessment
 
----
-
-### What is our sample spread of trivia expertise?
+What is our sample spread of trivia expertise?
 
@@
 
----
-
-### Are men and women participants balanced on trivia expertise?
+Are men and women participants balanced on trivia expertise?
 
@@
 
----
-
-### Do older participants know more trivia?
+Do older participants know more trivia?
 
@@
 
----
-
-### Do Ps accurately assess their own trivia skill?
+Do Ps accurately assess their own trivia skill?
 
@@
 
----
-
 ```{r}
@@
 
----
-
-### Trivia recall by confidence
+## Trivia recall by confidence
 
@@
 
----
+## Trivia recall metamemory
 
-### Metamemory state counts (correct trials only!)
+Metamemory state counts (correct trials only!)
 
@@
 
----
-
-### Recall accuracy by metamemory state
+Recall accuracy by metamemory state
 
@@
 
----
-
-### Metamemory state relative percentages
+Metamemory state relative percentages
 
@@
 
----
-
-class: inverse, middle
-
 # Self-report measures
-
----
 
@@
 
----
-
-class: inverse, middle
-
 # Museum task encoding
 
----
-
-### How many people got which categories?
+How many people got which categories?
 
@@
 
----
-
-### Are some categories more interesting than others?
+Are some categories more interesting than others?
 
@@
 
----
-
-### Are trivia experts more interested overall?
+Are trivia experts more interested overall?
 
@@
 
----
-
-class: inverse, middle
-
 # Museum task retrieval
 
----
-
-### Fact recall by question order/chunk type
+## Fact recall by question order/chunk type
 
@@
 
----
-
-### Fact recall by chunk type
+## Fact recall by chunk type
 
@@
 
----
-
-### Is recall higher when people already know (some of) the facts?
+## Is recall higher when people already know (some of) the facts?
 
@@
 
----
-
-### Photo recognition
+## Photo recognition
 
@@
 
----
-
-### Source memory for which museum
+## Source memory for which museum
 
@@
 ```
-
----
-
-### Source memory for which museum
 
@@
 
-### Does _photo_ retrieval predict _fact_ retrieval?
+## Does _photo_ retrieval predict _fact_ retrieval?
 
@@
 
----
-
-### Does _photo_ retrieval predict _fact_ retrieval?
-
 ```{r}
@@
 
----
-
-### Does _source_ retrieval predict _fact_ retrieval?
+## Does _source_ retrieval predict _fact_ retrieval?
 
@@
 
----
-
-### Does _source_ retrieval predict _fact_ retrieval?
-
 ```{r}
@@
 
----
-
-### Does _source_ retrieval predict _photo_ retrieval?
+## Does _source_ retrieval predict _photo_ retrieval?
 
@@
 
----
-
-### Does _source_ retrieval predict _photo_ retrieval?
-
 ```{r}
@@
 
----
-
-### Does interest at encoding predict _fact_ retrieval?
+## Does interest at encoding predict _fact_ retrieval?
 
@@
 
----
-
-### Does interest at encoding predict _photo_ retrieval?
+## Does interest at encoding predict _photo_ retrieval?
 
@@
 
----
-
-### Does interest at encoding predict _source_ retrieval?
+## Does interest at encoding predict _source_ retrieval?
 

### 2022-10-13 slides/results.Rmd
catching up on much older work history

@@
 ```
+
+class: inverse, middle
+
+# Proposed main figures
+
+---
+
+### _Photo_ recognition predicts _fact_ recall, slightly more so for experts
+
+```{r}
+retrieval %>% 
+  filter(already_knew == "none") %>% 
+  mutate(across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
+         acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
+  group_by(subj_num, j_score, resp_pic) %>%
+  summarize(acc_recall = mean(acc_recall)) %>% 
+  ggplot(aes(x = resp_pic, y = acc_recall, color = fct_rev(cut_number(j_score, 3)), fill = fct_rev(cut_number(j_score, 3)))) + 
+  geom_line(aes(group = subj_num), alpha = 0.1) +
+  geom_smooth(method = "lm", alpha = 0.2) + 
+  scale_x_continuous(breaks = 0:1) +
+  scale_color_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
+  scale_fill_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
+  labs(x = "Photo recognition accuracy",
+       y = "Fact recall accuracy (generous)",
+       color = "Expertise tertile",
+       fill = "Expertise tertile") +
+  theme_bw()
+```
+
+---
 
@@
   mutate(acc_recall = as.numeric(acc_recall > 0),
-         j_score = j_score - 0.7,
-         interest = (interest / 100) - 0.5) %>% 
+         # scaled to units of 0.1
+         j_score = (j_score - 0.7) * 10,
+         interest = (interest / 100) - .5) %>% 
   lme4::glmer(acc_recall ~ j_score + interest + (1 + interest | subj_num), data = ., family = "binomial") %>%
@@
 
-```{r}
-retrieval %>% 
-  filter(already_knew == "none") %>% 
-  mutate(across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
-         acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
-  group_by(subj_num, j_score, resp_pic) %>%
-  summarize(acc_recall = mean(acc_recall)) %>% 
-  ggplot(aes(x = resp_pic, y = acc_recall, color = fct_rev(cut_number(j_score, 3)), fill = fct_rev(cut_number(j_score, 3)))) + 
-  geom_line(aes(group = subj_num), alpha = 0.1) +
-  geom_smooth(method = "lm", alpha = 0.2) + 
-  scale_x_continuous(breaks = 0:1) +
-  scale_color_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
-  scale_fill_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
-  labs(x = "Photo recognition accuracy",
-       y = "Fact recall accuracy (generous)",
-       color = "Expertise tertile",
-       fill = "Expertise tertile") +
-  theme_bw()
-```
-
----
-
-### _Photo_ recognition predicts _fact_ recall, slightly more so for experts
-
 Quick and dirty maximum-likelihood logistic regression
@@
   mutate(acc_recall = as.numeric(acc_recall > 0),
-         across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
+         # across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
+         across(c(resp_pic, resp_source), ~(. / 100)),
+         interest = (interest / 100) - 0.5,
          j_score = j_score - 0.7) %>% 
-  lme4::glmer(acc_recall ~ resp_pic * j_score + (1 + resp_pic | subj_num), data = ., family = "binomial") %>%
+  lme4::glmer(acc_recall ~ resp_pic * j_score + interest + (1 + resp_pic | subj_num), data = ., family = "binomial") %>%
   broom.mixed::tidy() %>%
@@
 ```
+
+---
+
+### _Combined_ recognition predicts _fact_ recall, slightly more so for experts
+
+```{r}
+retrieval %>% 
+  filter(already_knew == "none") %>% 
+  mutate(across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
+         resp_either = resp_pic + resp_source,
+         acc_recall = as.integer(acc_recall > 0)) %>%
+  filter(resp_either > 0) %>% 
+  group_by(subj_num, j_score, resp_either) %>%
+  summarize(acc_recall = mean(acc_recall)) %>% 
+  ggplot(aes(x = resp_either, y = acc_recall, color = fct_rev(cut_number(j_score, 3)), fill = fct_rev(cut_number(j_score, 3)))) + 
+  geom_line(aes(group = subj_num), alpha = 0.1) +
+  geom_smooth(method = "lm", alpha = 0.2) + 
+  scale_x_continuous(breaks = 1:2) +
+  scale_color_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
+  scale_fill_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
+  labs(x = "Joint associate recognition accuracy",
+       y = "Fact recall accuracy (generous)",
+       color = "Expertise tertile",
+       fill = "Expertise tertile") +
+  theme_bw()
+```
+
+---
+
+### _Combined_ recognition predicts _fact_ recall, slightly more so for experts
+
+Quick and dirty maximum-likelihood logistic regression
+
+Formula: `acc_recall ~ resp_either * j_score + (1 + resp_either | subj_num)`
+
+```{r}
+retrieval %>% 
+  filter(already_knew == "none") %>% 
+  mutate(acc_recall = as.numeric(acc_recall > 0),
+         across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
+         # so, like 20% of participants have no retrieval trials where they missed on both source and pic
+         # so this is run only using trials where people got _either_ source _or_ pic
+         # aka the difference between getting one and getting both
+         resp_either = resp_pic + resp_source - 1,
+         j_score = j_score - 0.7) %>% 
+  filter(resp_either > -1) %>% 
+  lme4::glmer(acc_recall ~ resp_either * j_score + (1 + resp_either | subj_num), data = ., family = "binomial") %>%
+  broom.mixed::tidy() %>%
+  filter(effect == "fixed") %>% 
+  select(term:statistic) %>% 
+  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
+  knitr::kable()
+```

### 2022-10-13 R/make_plots.R

@@ -1,0 +1,262 @@
+## setup ----
+
+require(tidyverse)
+require(magrittr)
+
+source(here::here("R", "get_cleaned_data.R"))
+
+this_theme <- theme_bw(base_size = 14,
+                       base_family = "Aileron") +
+  theme(legend.background = element_blank(),
+        plot.background = element_blank())
+
+## demographics ----
+
+plot_demos <- q_google_demos %>% 
+  mutate(gender = coalesce(gender, "not reported")) %>% 
+  left_join(q_google_demos %>%
+              count(gender) %>%
+              mutate(gender = coalesce(gender, "not reported"),
+                     gender_n = glue::glue("{gender} (n = {n})")) %>%
+              select(-n),
+            by = "gender") %>% 
+  ggplot(aes(x = age, fill = gender_n)) +
+  geom_histogram(position = "identity", alpha = 0.5, binwidth = 2) +
+  scale_y_continuous(breaks = scales::breaks_extended(6)) +
+  labs(fill = "gender") +
+  this_theme +
+  theme(legend.position = c(1, 1),
+        legend.justification = c(1, 1))
+
+## trivia expertise ----
+
+plot_expertise_hist <- j_exp %>% 
+  ggplot(aes(x = j_score)) +
+  geom_histogram(binwidth = .05, fill = "gray80") +
+  geom_vline(xintercept = 0.7, linetype = "dotted") +
+  annotate("text",
+           x = .67,
+           y = 20,
+           label = "Approx cutoff for Jeopardy callback",
+           hjust = 1,
+           family = "Aileron Light") +
+  labs(x = "Expertise score (fraction correct out of 50 questions)",
+       y = "count") +
+  this_theme
+
+plot_expertise_gender <- j_exp %>% 
+  mutate(subj_num = factor(subj_num)) %>% 
+  left_join(q_google_demos, by = "subj_num") %>% 
+  mutate(gender = if_else(gender != "male", "not male", gender, missing = "not male")) %>% 
+  ggplot(aes(x = gender, y = j_score)) +
+  geom_boxplot(fill = "gray80") +
+  geom_hline(yintercept = 0.7, linetype = "dotted") +
+  labs(y = "Expertise score") +
+  this_theme
+
+## encoding ----
+
+plot_encoding_interest <- encoding %>% 
+  group_by(subj_num, j_score) %>% 
[…]

### 2022-10-13 slides/data_checking.Rmd
teeny updates before mariam meeting today

@@
 
+## Novel fact recall
+
+```{r}
+retrieval %>% 
+  filter(already_knew == "none") %>% 
+  group_by(subj_num, j_score) %>% 
+  summarize(acc_recall = mean(acc_recall)) %>% 
+  left_join(q_google_demos, by = "subj_num") %>% 
+  filter(gender %in% c("male", "female")) %>% 
+  ggplot(aes(x = j_score, y = acc_recall, color = gender, fill = gender)) +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  labs(x = "Expertise score", y = "% correct recall for novel facts") +
+  theme_bw()
+```
+
 ## Photo recognition

### 2022-10-13 slides/results.Rmd
teeny updates before mariam meeting today

@@
 source(here::here("R", "get_cleaned_data.R"))
+
+count_streak <- function (acc_col, min_streak_length = 3) {
+  streak_count <- 0
+  current_streak <- 0
+  for (i in 1:length(acc_col)) {
+    if (acc_col[i] == 0) current_streak <- 0
+    if (acc_col[i] == 1) {
+      current_streak <- current_streak + acc_col[i]
+      if (current_streak == min_streak_length) {
+        # Only triggered once per streak because using == not >=
+        streak_count <- streak_count + 1
+      }
+    }
+  }
+  return (streak_count)
+}
 ```
@@
 
+### Trivia experts _don't_ show better photo memory
+
+```{r}
+retrieval %>%
+  filter(already_knew == "none") %>% 
+  mutate(across(c(resp_pic, resp_source, acc_recall),
+                ~if_else(. > 0, 1L, 0L))) %>% 
+  group_by(subj_num, j_score) %>% 
+  summarize(acc_pic = mean(resp_pic),
+            acc_source = mean(resp_source),
+            acc_fact = mean(acc_recall)) %>% 
+  pivot_longer(cols = starts_with("acc"),
+               names_to = "memory_type",
+               values_to = "acc",
+               names_prefix = "acc_") %>% 
+  ggplot(aes(x = j_score, y = acc, color = memory_type, fill = memory_type)) +
+  geom_hline(yintercept = 0.5, linetype = "dotted") +
+  geom_point() +
+  geom_smooth(method = "lm") +
+  facet_wrap(~ memory_type) +
+  guides(color = "none", fill = "none") +
+  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)",
+       title = "Memory as a function of trivia expertise",
+       subtitle = "Only trials with fully novel facts") +
+  theme_bw()
+```
+
+---
+
 ### _Photo_ recognition predicts _fact_ recall, slightly more so for experts
@@
   summarize(acc_recall = mean(acc_recall)) %>% 
-  ggplot(aes(x = resp_pic, y = acc_recall, color = fct_rev(cut_number(j_score, 3)), fill = fct_rev(cut_number(j_score, 3)))) + 
+  ggplot(aes(x = resp_pic, y = acc_recall, color = fct_rev(cut_number(j_score, 2)), fill = fct_rev(cut_number(j_score, 1)))) + 
   geom_line(aes(group = subj_num), alpha = 0.1) +
@@
        y = "Fact recall accuracy (generous)",
+       color = "Expertise median split",
+       fill = "Expertise median split") +
+  theme_bw()
+```
+???
+
+Main figure subplots: coefplot, a better version of this with median split and as close to trialwise data as possible, with Bayesian model fit ribbons on top
+
+---
+
+### _Source_ recognition predicts _fact_ recall for everyone
+
+```{r}
+retrieval %>% 
+  filter(already_knew == "none") %>% 
+  mutate(across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
+         acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
+  group_by(subj_num, j_score, resp_source) %>%
+  summarize(acc_recall = mean(acc_recall)) %>% 
+  ggplot(aes(x = resp_source, y = acc_recall, color = fct_rev(cut_number(j_score, 3)), fill = fct_rev(cut_number(j_score, 3)))) + 
+  geom_line(aes(group = subj_num), alpha = 0.1) +
+  geom_smooth(method = "lm", alpha = 0.2) + 
+  scale_x_continuous(breaks = 0:1) +
+  scale_color_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
+  scale_fill_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
+  labs(x = "Source recognition accuracy",
+       y = "Fact recall accuracy (generous)",
        color = "Expertise tertile",
@@
 ```
+
+???
+
+Same plot subfigures as the previous
+
+Also, see about running a model with pic/source as a covariate to explicitly test the difference in interactions
 
@@
 encoding %>% 
-  mutate(j_score = j_score - 0.7) %>% 
+  mutate(j_score = (j_score - 0.7) * 10) %>% 
   lme4::lmer(resp ~ j_score + already_knew + (1 | subj_num), data = .) %>% 
@@
   mutate(acc_recall = as.numeric(acc_recall > 0),
-         j_score = j_score - 0.7) %>% 
+         j_score = (j_score - 0.7) * 10) %>% 
   lme4::glmer(acc_recall ~ j_score + (1 | subj_num), data = ., family = "binomial") %>%
@@
          j_score = (j_score - 0.7) * 10,
-         interest = (interest / 100) - .5) %>% 
+         # scaled to units of 0.1 where 1 is the full scale
+         interest = (interest / 10) - 5) %>% 
   lme4::glmer(acc_recall ~ j_score + interest + (1 + interest | subj_num), data = ., family = "binomial") %>%
@@
 ]
-
----
-
-### Trivia experts _don't_ show better photo memory
-
-```{r}
-retrieval %>%
-  # filter(already_knew == "none") %>% 
-  mutate(across(c(resp_pic, resp_source),
-                ~if_else(. > 0, 1L, 0L))) %>% 
-  group_by(subj_num, j_score) %>% 
-  summarize(acc_pic = mean(resp_pic),
-            acc_source = mean(resp_source)) %>% 
-  pivot_longer(cols = starts_with("acc"),
-               names_to = "memory_type",
-               values_to = "acc",
-               names_prefix = "acc_") %>% 
-  ggplot(aes(x = j_score, y = acc, color = memory_type, fill = memory_type)) +
-  geom_point() +
-  geom_smooth(method = "lm") +
-  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)") +
-  theme_bw()
-```
 
@@
          across(c(resp_pic, resp_source), ~(. / 100)),
-         interest = (interest / 100) - 0.5,
-         j_score = j_score - 0.7) %>% 
+         interest = (interest / 10) - 5,
+         j_score = (j_score - 0.7) * 10) %>% 
   lme4::glmer(acc_recall ~ resp_pic * j_score + interest + (1 + resp_pic | subj_num), data = ., family = "binomial") %>%
@@
   knitr::kable()
-```
-
----
-
-### _Source_ recognition predicts _fact_ recall for everyone
-
-```{r}
-retrieval %>% 
-  filter(already_knew == "none") %>% 
-  mutate(across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
-         acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
-  group_by(subj_num, j_score, resp_source) %>%
-  summarize(acc_recall = mean(acc_recall)) %>% 
-  ggplot(aes(x = resp_source, y = acc_recall, color = fct_rev(cut_number(j_score, 3)), fill = fct_rev(cut_number(j_score, 3)))) + 
-  geom_line(aes(group = subj_num), alpha = 0.1) +
-  geom_smooth(method = "lm", alpha = 0.2) + 
-  scale_x_continuous(breaks = 0:1) +
-  scale_color_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
-  scale_fill_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
-  labs(x = "Source recognition accuracy",
-       y = "Fact recall accuracy (generous)",
-       color = "Expertise tertile",
-       fill = "Expertise tertile") +
-  theme_bw()
 ```
@@
          across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
-         j_score = j_score - 0.7) %>% 
+         j_score = (j_score - 0.7) * 10) %>% 
   lme4::glmer(acc_recall ~ resp_source * j_score + (1 + resp_source | subj_num), data = ., family = "binomial") %>%
@@
          resp_either = resp_pic + resp_source - 1,
-         j_score = j_score - 0.7) %>% 
+         j_score = (j_score - 0.7) * 10) %>% 
   filter(resp_either > -1) %>% 

### 2023-01-25 writing/ms.Rmd
prepare to clone repo on other computer

@@
 author: "Monica Thieu"
-date: "5/29/2020"
+date: "Updated `r Sys.Date()`"
 output: html_document
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+require(tidyverse)
+require(magrittr)
+load(here::here("ignore", "data", "plots_ms.rda"))
 ```
 
-# Intro
+# Figures and captions
+
+## Figure 3
+
+```{r}
+plot_demos
+```
+
+```{r}
+plot_expertise_hist
+```
+
+## Figure 4
+
+```{r}
+plot_fact_by_expertise
+```
+
+## Figure 5
+
+```{r}
+plot_coefs_fact_by_pic
+```
+
+```{r}
+plot_fixef_fact_by_pic
+```
+
+```{r}
+plot_pic_by_expertise
+```
+
+## Figure 6
+
+```{r}
+plot_coefs_fact_by_source
+```
+
+```{r}
+plot_fixef_fact_by_source
+```
+
+```{r}
+plot_source_by_expertise
+```
+
+<!--
+# OLD STUFF I FOUND IN HERE: Intro
 
@@
 - Thus, the current study
+-->

### 2023-01-25 R/make_models.R

@@ -1,0 +1,48 @@
+## setup ----
+
+require(magrittr)
+require(rlang)
+require(tidyverse)
+
+options(mc.cores = parallel::detectCores())
+
+## load data ----
+
+source(here::here("R", "get_cleaned_data.R"))
+
+## prep data further ----
+
+retrieval_modelsafe <- retrieval %>% 
+  filter(already_knew == "none") %>% 
+  mutate(acc_recall = as.numeric(acc_recall > 0),
+         # YES binary! Leaving the slider at the center counted as a miss.
+         # People were endpointing a lot. I think this is more stable
+         # Effect-coded now
+         across(c(resp_pic, resp_source), ~if_else(. > 0, 0.5, -0.5)),
+         # dummy variable for whether stimulus came from the second (later) encoding block
+         from_encoding_late = if_else(encoding_trial_num > 40, 0.5, -0.5),
+         # Scaled to units of .1
+         interest = (interest / 10) - 5,
+         # Scaled to units of .1
+         j_score = (j_score - 0.7) * 10)
+
+## fit models ----
+
+model_fact_by_pic <- rstanarm::stan_glmer(acc_recall ~ resp_pic * j_score + from_encoding_late + interest + (1 | subj_num),
+                     family = binomial(link = "logit"),
+                     data = retrieval_modelsafe,
+                     prior = rstanarm::cauchy(0, 2.5),
+                     prior_intercept = rstanarm::cauchy(0, 2.5))
+
+model_fact_by_source <- rstanarm::stan_glmer(acc_recall ~ resp_source * j_score + from_encoding_late + interest + (1 | subj_num),
+                                          family = binomial(link = "logit"),
+                                          data = retrieval_modelsafe,
+                                          prior = rstanarm::cauchy(0, 2.5),
+                                          prior_intercept = rstanarm::cauchy(0, 2.5))
+
+## save that shit out immediately ----
+
+save(model_fact_by_pic,
+     model_fact_by_source,
+     file = here::here("ignore", "data", "models.rda"))
+

### 2023-01-25 R/make_plots.R

@@ -4,12 +4,25 @@ require(tidyverse)
 require(magrittr)
 
 source(here::here("R", "get_cleaned_data.R"))
+# For the model outputs
+load(here::here("ignore", "data", "preplots.rda"))
 
-this_theme <- theme_bw(base_size = 14,
+# Aileron family for slides
+# Something else...? for manuscript?
+theme_slides <- theme_bw(base_size = 14,
                        base_family = "Aileron") +
   theme(legend.background = element_blank(),
         plot.background = element_blank())
 
+# Specify this separately because plot annotations take their own font arg
+font_ms <- "Helvetica Neue"
+theme_ms <- theme_bw(base_size = 14,
+                     base_family = font_ms) +
+  theme(legend.background = element_blank(),
+        plot.background = element_blank())
+
+this_font <- font_ms
+this_theme <- theme_ms
 ## demographics ----
 
 plot_demos <- q_google_demos %>% 
@@ -21,9 +34,10 @@ plot_demos <- q_google_demos %>%
               select(-n),
             by = "gender") %>% 
   ggplot(aes(x = age, fill = gender_n)) +
-  geom_histogram(position = "identity", alpha = 0.5, binwidth = 2) +
+  geom_histogram(position = "stack", alpha = 0.5, binwidth = 2) +
   scale_y_continuous(breaks = scales::breaks_extended(6)) +
-  labs(fill = "gender") +
+  labs(y = "# of participants",
+       fill = "gender") +
   this_theme +
   theme(legend.position = c(1, 1),
         legend.justification = c(1, 1))
@@ -33,15 +47,15 @@ plot_demos <- q_google_demos %>%
 plot_expertise_hist <- j_exp %>% 
   ggplot(aes(x = j_score)) +
   geom_histogram(binwidth = .05, fill = "gray80") +
-  geom_vline(xintercept = 0.7, linetype = "dotted") +
+  geom_vline(xintercept = median(j_exp$j_score), linetype = "dotted") +
   annotate("text",
-           x = .67,
+           x = median(j_exp$j_score) - 0.02,
            y = 20,
-           label = "Approx cutoff for Jeopardy callback",
+           label = "median score",
            hjust = 1,
-           family = "Aileron Light") +
-  labs(x = "Expertise score (fraction correct out of 50 questions)",
-       y = "count") +
+           family = this_font) +
[…]

### 2023-01-25 R/make_preplots.R

@@ -1,0 +1,120 @@
+## setup ----
+
+require(magrittr)
+require(rlang)
+require(tidyverse)
+
+## load data ----
+
+load(here::here("ignore", "data", "models.rda"))
+
+## functions ----
+
+posterior_preplot_params <- function (object) {
+  out <- object %>%
+    as.data.frame() %>%
+    as_tibble() %>%
+    mutate(iteration = 1:nrow(.)) %>%
+    # removes all random effects and sigma terms. should yield fixed effects only
+    select(-contains("["), -contains("sigma")) %>%
+    rename(intercept = "(Intercept)") %>%
+    pivot_longer(cols = -iteration, names_to = "term", values_to = "estimate")
+  
+  return (out)
+}
+
+posterior_preplot_bysubj <- function (object, newdata, pred_col = "y_pred", draws = 1000) {
+  out <- object %>%
+    rstanarm::posterior_epred(newdata = newdata,
+                              re.form = NULL,
+                              draws = draws)
+  
+  # Just the median of every predicted point for every subject
+  # Note that this doesn't select in a paired way for the "median iteration"
+  # returns a VECTOR which needs to get slapped onto newdata
+  out %<>%
+    apply(2, median) %>%
+    t() %>%
+    c()
+  
+  newdata %<>%
+    mutate(!!pred_col := out)
+  
+  return (newdata)
+}
+
+posterior_preplot_fixef <- function (object, newdata, pred_col = "y_pred", draws = 1000) {
+  
+  out <- object %>%
+    rstanarm::posterior_epred(newdata = newdata,
+                              re.form = NA,
+                              draws = draws)
+  
+  newdata %<>%
+    # Must expand AFTER predictions is already done to repeat for iterations
+    # need the "obs" column to make damn sure that the correct predicted points get pasted on the correct x values
+    mutate(obs = 1:nrow(.),
+           iteration = map(obs, ~1:draws)) %>%
+    unchop(iteration)
+  
+  out %<>%
+    as_tibble() %>%
+    mutate(iteration = 1:nrow(.)) %>%
+    pivot_longer(cols = -iteration, names_to = "obs", values_to = pred_col) %>%
+    mutate(obs = as.integer(obs)) %>%
+    right_join(newdata, by = c("obs", "iteration")) %>%
+    # the obs column obstructs any later pivoting, and is technically redundant if all the x cols are in there,
+    # so get outta here
+    select(-obs)
+  
+  return(out)
+}
+
[…]

### 2023-03-05 writing/ms.Rmd
start to add extra stat reports, bayes fact alone

@@
 require(magrittr)
+require(rlang)
+load(here::here("ignore", "data", "preplots.rda")) # For the model params
 load(here::here("ignore", "data", "plots_ms.rda"))
+
+signif_digits <- 3L
+```
+
+```{r setup-extra-stat-reports}
+summarize_report <- function (data, col, ..., stat_name = "", unit_name = "", digs = signif_digits) {
+  if (unit_name != "") unit_name %<>% paste0(" ", .)
+  glue_in = if_else(stat_name != "",
+                    "{stat_name} = {a}{unit_name}, 95% CI [{b}, {c}]",
+                    "{a}{unit_name}, 95% CI [{b}, {c}]")
+
+  col_chr = as_name(enexpr(col))
+  group_cols = enexprs(...)
+
+  data %<>%
+    select(iteration, !!!group_cols, starts_with(col_chr)) %>%
+    pivot_longer(cols = starts_with(col_chr),
+                 names_to = "metric_type",
+                 values_to = "value",
+                 names_prefix = glue::glue("{col_chr}_"))
+
+  if (!is.null(group_cols)) {
+    data %<>% group_by(!!!group_cols, metric_type)
+  } else {
+    data %<>% group_by(metric_type)
+  }
+  data %<>%
+    summarize(avg = mean(value, na.rm = T),
+              q025 = quantile(value, .025, na.rm = T),
+              q975 = quantile(value, .975, na.rm = T)) %>% 
+    mutate(across(c("avg", "q025", "q975"),
+                  \(x) formatC(signif(x, digits = digs), digits = digs, format = "fg", flag = "#", mode = "double")),
+           txt_apa = pmap_chr(list(avg, q025, q975),
+                              \(a, b, c) {glue::glue(glue_in)}
+           ),
+           across(c("avg", "q025", "q975"), as.numeric))
+
+  return (data)
+}
+
+coefs_fact_by_pic <- preplot_params_fact_by_pic %>%
+  summarize_report(col = estimate, term, stat_name = "beta")
+
+coefs_fact_by_source <- preplot_params_fact_by_source %>%
+  summarize_report(col = estimate, term, stat_name = "beta")
 ```
@@
 
+Interaction coefficient: `r coefs_fact_by_pic %>% filter(term == "resp_pic:j_score") %>% pull(txt_apa)`
+
 ```{r}
@@
 ```
+
+Interaction coefficient: `r coefs_fact_by_source %>% filter(term == "resp_source:j_score") %>% pull(txt_apa)`
 

### 2023-03-05 R/make_models.R

@@ -73,6 +73,11 @@ glmer_spec <- logistic_reg() %>%
 control_spec <- control_parsnip(verbosity = 2L) %>% 
   control_workflow()
 
+workflow_fact_alone <- workflow() %>% 
+  add_recipe(base_recipe) %>% 
+  add_model(glmer_spec,
+            formula = acc_recall ~ j_score + from_encoding_late + interest + (1 | subj_num))
+
 workflow_fact_by_pic <- workflow() %>% 
   add_recipe(base_recipe) %>% 
   add_model(glmer_spec,
@@ -85,6 +90,10 @@ workflow_fact_by_source <- workflow() %>%
 
 ## fit models ----
 
+model_fact_alone <- fit(workflow_fact_alone,
+                        data = retrieval_modelsafe,
+                        control = control_spec)
+
 model_fact_by_pic <- fit(workflow_fact_by_pic,
     data = retrieval_modelsafe,
     control = control_spec)
@@ -95,7 +104,8 @@ model_fact_by_source <- fit(workflow_fact_by_source,
 
 ## save that shit out immediately ----
 
-save(model_fact_by_pic,
+save(model_fact_alone,
+     model_fact_by_pic,
      model_fact_by_source,
      file = here::here("ignore", "data", "models.rda"))
 

### 2023-03-06 R/make_models.R
more stuff for cns poster

@@ -95,12 +95,12 @@ model_fact_alone <- fit(workflow_fact_alone,
                         control = control_spec)
 
 model_fact_by_pic <- fit(workflow_fact_by_pic,
-    data = retrieval_modelsafe,
-    control = control_spec)
+                         data = retrieval_modelsafe,
+                         control = control_spec)
 
 model_fact_by_source <- fit(workflow_fact_by_source,
-    data = retrieval_modelsafe,
-    control = control_spec)
+                            data = retrieval_modelsafe,
+                            control = control_spec)
 
 ## save that shit out immediately ----
 

### 2023-03-06 R/make_plots.R

@@ -7,6 +7,17 @@ source(here::here("R", "get_cleaned_data.R"))
 # For the model outputs
 load(here::here("ignore", "data", "preplots.rda"))
 
+# A function factory for getting integer y-axis values.
+# From https://joshuacook.netlify.app/post/integer-values-ggplot-axis/
+integer_breaks <- function(n = 5, ...) {
+  fxn <- function(x) {
+    breaks <- floor(pretty(x, n, ...))
+    names(breaks) <- attr(breaks, "labels")
+    breaks
+  }
+  return(fxn)
+}
+
 # Aileron family for slides
 # Something else...? for manuscript?
 theme_slides <- theme_bw(base_size = 14,
@@ -16,6 +27,11 @@ theme_slides <- theme_bw(base_size = 14,
 
 theme_slides_ppt <- theme_bw(base_size = 22,
                              base_family = "Helvetica Neue") +
+  theme(legend.background = element_blank(),
+        plot.background = element_blank())
+
+theme_poster <- theme_bw(base_size = 26,
+                         base_family = "Helvetica Neue") +
   theme(legend.background = element_blank(),
         plot.background = element_blank())
 
@@ -40,7 +56,7 @@ plot_demos <- q_google_demos %>%
             by = "gender") %>% 
   ggplot(aes(x = age, fill = gender_n)) +
   geom_histogram(position = "stack", alpha = 0.5, binwidth = 2) +
-  scale_y_continuous(breaks = scales::breaks_extended(6)) +
+  scale_y_continuous(breaks = integer_breaks()) +
   labs(y = "# of participants",
        fill = "gender") +
   this_theme +
@@ -402,6 +418,61 @@ ggsave(here::here("ignore", "figs", "plot_cns2023talk_fixef_fact_by_pic.png"),
        device = "png",
        width = 5.71,
        height = 6.85,
+       units = "in")
+
+## save plot objects for CNS poster (specific shapes) ----
+
+ggsave(here::here("ignore", "figs", "plot_cns2023poster_demos.png"),
+       plot = plot_demos + 
+         theme_poster + 
+         theme(legend.position = c(1, 1), 
+               legend.justification = c(1, 1),
+               legend.title = element_text(size = 20),
+               legend.text = element_text(size = 16)),
+       device = "png",
+       width = 7,
+       height = 5,
+       units = "in")
+
+# plot_fact_by_expertise but with a different constant color
[…]

### 2023-03-06 R/make_preplots.R

@@ -91,6 +91,8 @@ posterior_preplot_fixef <- function (object, newdata, pred_col = "y_pred", draws
 
 ## make the preplot objects ----
 
+preplot_params_fact_alone <- posterior_preplot_params(model_fact_alone)
+
 preplot_params_fact_by_pic <- posterior_preplot_params(model_fact_by_pic)
 
 preplot_params_fact_by_source <- posterior_preplot_params(model_fact_by_source)
@@ -137,7 +139,8 @@ preplot_fixef_fact_by_source <- posterior_preplot_fixef(object = model_fact_by_s
                                                         newdata = newdata_preplot_fixef,
                                                         pred_col = "acc_pred")
 
-save(preplot_params_fact_by_pic,
+save(preplot_params_fact_alone,
+     preplot_params_fact_by_pic,
      preplot_params_fact_by_source,
      preplot_by_subj_fact_by_pic,
      preplot_by_subj_fact_by_source,

### 2023-05-11 R/analyze/make_models.R
moving around and target-ifying scripts

@@ -1,0 +1,97 @@
+# Note: Run it with 4 cores if you can
+
+## prep data further ----
+
+prep_retrieval_data <- function (retrieval_data) {
+  out <- retrieval_data %>%
+    # Just drop those extra columns now
+    # The recipe validation is super annoying when there's a bunch of leftover cols
+    select(subj_num, 
+           acc_recall, 
+           resp_pic, resp_source, 
+           j_score, 
+           encoding_trial_num, 
+           interest, 
+           already_knew)
+  
+  return (out)
+}
+
+make_recipe <- function (retrieval_data_prepped) {
+  out <- recipe(retrieval_data_prepped) %>% 
+    step_filter(already_knew == "none") %>% 
+    update_role(acc_recall, new_role = "outcome") %>% 
+    update_role(c(resp_pic, resp_source, j_score, encoding_trial_num, interest, subj_num), new_role = "predictor") %>% 
+    # so I don't have to put already_knew into the preplot new data
+    update_role_requirements(role = "NA", bake = FALSE) %>% 
+    # update_role(subj_num, new_role = "ID") %>% 
+    # Sort of a roundabout way of discretizing and then re-numeric-izing these variables
+    # But it just seems better than changing the global contrasts option
+    # and using the dummy variables steps
+    # Have to use num2factor instead of cut because cut doesn't currently output ordered
+    step_num2factor(acc_recall,
+                    # num2factor expects factor levels to start at 1
+                    transform = \(x) ifelse(x > 0, 2, 1),
+                    levels = c("incorrect", "correct"),
+                    ordered = TRUE,
+                    # bc it's an outcome var, skip when running with predict
+                    skip = TRUE) %>% 
+    # so that leaving the slider as 0 gets binned in with incorrect
+    step_num2factor(c(resp_pic, resp_source),
+                    transform = \(x) ifelse(x > 0, 2, 1),
+                    levels = c("incorrect", "correct"),
+                    ordered = TRUE) %>% 
+    step_num2factor(encoding_trial_num,
+                    transform = \(x) ifelse(x > 40, 2, 1),
+                    levels = c("early", "late"),
+                    ordered = TRUE) %>% 
+    step_ordinalscore(c(resp_pic, resp_source, encoding_trial_num)) %>%
+    # to get it to -0.5 and +0.5
[…]

### 2023-05-11 R/analyze/make_plots_ms.R

@@ -1,0 +1,217 @@
+# A function factory for getting integer y-axis values.
+# From https://joshuacook.netlify.app/post/integer-values-ggplot-axis/
+integer_breaks <- function(n = 5, ...) {
+  fxn <- function(x) {
+    breaks <- floor(pretty(x, n, ...))
+    names(breaks) <- attr(breaks, "labels")
+    breaks
+  }
+  return(fxn)
+}
+
+make_plot_demos <- function (demo_data) {
+  demo_data %>% 
+    mutate(gender = coalesce(gender, "not reported")) %>% 
+    left_join(demo_data %>%
+                count(gender) %>%
+                mutate(gender = coalesce(gender, "not reported"),
+                       gender_n = glue::glue("{gender} (n = {n})")) %>%
+                select(-n),
+              by = "gender") %>% 
+    ggplot(aes(x = age, fill = gender_n)) +
+    geom_histogram(position = "stack", alpha = 0.5, binwidth = 2) +
+    scale_y_continuous(breaks = integer_breaks()) +
+    labs(y = "# of participants",
+         fill = "gender")
+}
+
+make_plot_expertise_hist <- function (expertise_score_data, annotation_font = "Helvetica Neue") {
+  median_score <- median(expertise_score_data$j_score)
+  
+  expertise_score_data %>% 
+    ggplot(aes(x = j_score)) +
+    geom_histogram(binwidth = .05, fill = "gray80") +
+    geom_vline(xintercept = median_score, linetype = "dotted") +
+    annotate("text",
+             x = median_score - 0.02,
+             y = 20,
+             label = "median score",
+             hjust = 1,
+             family = annotation_font) +
+    labs(x = "Expertise score (proportion correct out of 50 questions)",
+         y = "# of participants") 
+}
+
+make_plot_retrieval_by_expertise <- function (retrieval_data, resp_col, y_label) {
+  retrieval_data %>%
+    filter(already_knew == "none") %>% 
+    # pic and source memory should have been binarized before entering the function!
+    group_by(subj_num, j_score) %>% 
+    summarize(resp_mean = mean({{resp_col}})) %>% 
+    ggplot(aes(x = j_score, y = resp_mean)) +
+    geom_hline(yintercept = 0.5, linetype = "dotted") +
+    geom_point(alpha = 0.5) +
+    geom_smooth(method = "lm", color = "black") +
+    labs(x = "Trivia expertise", y = y_label)
+}
+
[…]

### 2023-05-11 R/analyze/make_preplots.R

@@ -1,0 +1,85 @@
+posterior_preplot_params <- function (object) {
+  out <- object %>%
+    extract_fit_engine() %>% 
+    as.data.frame() %>%
+    as_tibble() %>%
+    mutate(iteration = 1:nrow(.)) %>%
+    # removes all random effects and sigma terms. should yield fixed effects only
+    select(-contains("["), -contains("sigma")) %>%
+    rename(intercept = "(Intercept)") %>%
+    pivot_longer(cols = -iteration, names_to = "term", values_to = "estimate")
+  
+  return (out)
+}
+
+posterior_preplot_bysubj <- function (object, newdata, pred_col = "y_pred", draws = 1000) {
+  
+  preproc <- object %>% 
+    extract_recipe()
+  
+  newdata <- preproc %>% 
+    bake(new_data = newdata)
+  
+  out <- object %>%
+    extract_fit_engine() %>% 
+    rstanarm::posterior_epred(newdata = newdata,
+                              re.form = NULL,
+                              draws = draws)
+  
+  # Just the median of every predicted point for every subject
+  # Note that this doesn't select in a paired way for the "median iteration"
+  # returns a VECTOR which needs to get slapped onto newdata
+  out %<>%
+    apply(2, median) %>%
+    t() %>%
+    c()
+  
+  newdata %<>%
+    mutate(!!pred_col := out)
+  
+  return (newdata)
+}
+
+posterior_preplot_fixef <- function (object, newdata, pred_col = "y_pred", draws = 1000) {
+  
+  preproc <- object %>% 
+    extract_recipe()
+  
+  newdata <- preproc %>% 
+    bake(new_data = newdata)
+  
+  out <- object %>%
+    extract_fit_engine() %>% 
+    rstanarm::posterior_epred(newdata = newdata,
+                              re.form = NA,
+                              draws = draws)
+  
+  newdata %<>%
+    # Must expand AFTER predictions is already done to repeat for iterations
+    # need the "obs" column to make damn sure that the correct predicted points get pasted on the correct x values
+    mutate(obs = 1:nrow(.),
+           iteration = map(obs, ~1:draws)) %>%
+    unchop(iteration)
+  
+  out %<>%
+    as_tibble() %>%
+    mutate(iteration = 1:nrow(.)) %>%
+    pivot_longer(cols = -iteration, names_to = "obs", values_to = pred_col) %>%
+    mutate(obs = as.integer(obs)) %>%
[…]

### 2023-05-11 R/clean_demos_ids.R

@@ -1,13 +1,0 @@
-require(tidyverse)
-require(magrittr)
-source(here::here("R", "utils_read_gorilla.R"))
-
-raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
-  read_gorilla_data("questionnaire-4vcn")
-
-less_raw <- raw %>% 
-  select(subj_num = `Participant Private ID`, q_key = `Question Key`, resp = Response) %>%
-  filter(!endsWith(q_key, "QUESTIONNAIRE")) %>% 
-  pivot_wider(names_from = q_key, values_from = resp)
-
-write_csv(less_raw, file = here::here("ignore", "data", "demos_ids.csv"))

### 2023-05-11 R/clean_encoding.R

@@ -1,50 +1,0 @@
-require(tidyverse)
-require(magrittr)
-source(here::here("R", "utils_read_gorilla.R"))
-
-raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
-  read_gorilla_data("task-ujps|task-wckg")
-
-pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
-  select(-n_correct) %>%
-  pivot_wider(names_from = category_num, values_from = category, names_prefix = "category") %>%
-  mutate(categories = paste(category1, category2, sep = "_"))
-
-less_raw <- raw %>% 
-  select(subj_num = `Participant Private ID`,
-         group,
-         group_trial_num = trial_num,
-         trial_screen = `Screen Name`,
-         zone = `Zone Name`,
-         rt = `Reaction Time`,
-         resp = `Response`,
-         starts_with("encoding_sentence")) %>% 
-  filter((trial_screen == "fact" & zone == "slider") | trial_screen == "already_knew") %>%
-  nest(data = -c(subj_num, group, group_trial_num, trial_screen)) %>%
-  pivot_wider(names_from = trial_screen, values_from = data) %>% 
-  mutate(already_knew = map_chr(already_knew, ~.x$resp)) %>% 
-  unnest(fact) %>% 
-  mutate(# Should catch slider trials where the slider was never clicked
-         # bc I think timeout will still be true if submitResp was never clicked but the slider was moved
-         resp = if_else(zone == "scale" & rt >= 34900, NA_character_, resp),
-         resp = as.integer(resp)) %>%
-  nest(data = -c(subj_num, group, group_trial_num)) %>% 
-  # stuff to pull only the row of scale trials where the slider stopped moving
-  mutate(data = map(data, get_slider_rt)) %>%
-  unnest(data) %>% 
-  # this SHOULD keep one row per trial and also keep no responses
-  select(-zone) %>% 
-  nest(data = -subj_num) %>% 
-  left_join(pretest, by = "subj_num") %>% 
-  mutate(data = map2(data, categories,
-                     ~.x %>% select(group_trial_num,
-                                    group,
-                                    resp,
-                                    rt,
-                                    already_knew,
-                                    encoding_sentence = paste0("encoding_sentence.", .y)))) %>%
-  unnest(data) %>% 
-  mutate(category = if_else(group == "academic", category1, category2)) %>% 
[…]

### 2023-05-11 R/clean_expertise.R

@@ -1,60 +1,0 @@
-require(tidyverse)
-require(magrittr)
-source(here::here("R", "utils_read_gorilla.R"))
-
-## reading in and cleaning ----
-
-raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
-  read_gorilla_data("task-v9u2")
-
-less_raw <- raw %>% 
-  # Just this one P had a weird task lapse where 2.5 trials repeated
-  filter(!(`Participant Private ID` == 4488331 & `Event Index` %in% 74:86)) %>% 
-  select(subj_num = `Participant Private ID`,
-         trial_num = `Trial Number`,
-         trial_screen = `Screen Name`,
-         zone = `Zone Name`,
-         rt = `Reaction Time`,
-         resp = `Response`,
-         timeout = `Timed Out`,
-         question,
-         answer) %>%
-  filter(trial_screen %in% c("recall", "confidence")) %>%
-  mutate(trial_num = as.integer(trial_num),
-         timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout),
-         # Should catch slider trials where the slider was never clicked
-         # bc I think timeout will still be true if submitResp was never clicked but the slider was moved
-         resp = if_else(zone == "scale" & rt >= 14900, NA_character_, resp),
-         # Fix the typo for the older subjects so the question text doesn't appear repeated
-         question = str_replace(question, "1890", "1899"),
-         answer = if_else(answer == "SF Giants", "San Francisco Giants", answer)) %>%
-  nest(data = -c(subj_num, trial_num, trial_screen)) %>% 
-  # patch in a "response" row if fully timed out
-  mutate(data = map(data,
-                    function (x) {
-                      if (nrow(x) == 1) {
-                        if (x$zone == "timelimit") {
-                          x$zone <- "response"
-                        }
-                      }
-                      return (x)
-                    })) %>% 
-  unnest(data) %>% 
-  filter(!(zone %in% c("continueButton", "timelimit"))) %>%
-  # stuff to pull only the row of scale trials where the slider stopped moving
-  nest(data = -c(subj_num, trial_num, trial_screen)) %>%
-  pivot_wider(names_from = trial_screen, values_from = data) %>% 
-  mutate(confidence = map(confidence, ~.x %>% 
-                            mutate(resp = as.integer(resp)) %>% 
-                            get_slider_rt()),
-         confidence = map(confidence,
[…]

### 2023-05-11 R/clean_metamemory.R

@@ -1,31 +1,0 @@
-require(tidyverse)
-require(magrittr)
-source(here::here("R", "utils_read_gorilla.R"))
-
-raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
-  read_gorilla_data("task-wlkb")
-
-less_raw <- raw %>% 
-  select(subj_num = `Participant Private ID`,
-         trial_num = `Trial Number`,
-         trial_screen = `Screen Name`,
-         zone = `Zone Name`,
-         rt = `Reaction Time`,
-         resp = `Response`,
-         timeout = `Timed Out`,
-         question,
-         answer) %>% 
-  mutate(question = str_replace(question, "1890", "1899"),
-         answer = if_else(answer == "SF Giants", "San Francisco Giants", answer))
-
-mem_states <- less_raw %>%
-  filter(trial_screen == "recall") %>% 
-  select(-c(trial_screen, zone))
-
-write_csv(mem_states, file = here::here("ignore", "data", "task_jeopardy_meta_states.csv"))
-
-mem_descriptions <- less_raw %>%
-  filter(trial_screen == "describe" & zone == "response") %>% 
-  select(subj_num, trial_num, question, resp)
-
-write_csv(mem_descriptions, file = here::here("ignore", "data", "task_jeopardy_meta_descriptions.csv"))

### 2023-05-11 R/clean_pretest.R

@@ -1,16 +1,0 @@
-require(tidyverse)
-require(magrittr)
-source(here::here("R", "utils_read_gorilla.R"))
-
-raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
-  read_gorilla_data("task-4elo")
-
-less_raw <- raw %>% 
-  select(subj_num = "Participant Private ID",
-         category_num = "Zone Name",
-         category = "Response",
-         n_correct = "Reaction Time") %>% 
-  filter(startsWith(category_num, "category")) %>% 
-  mutate(category_num = as.integer(str_sub(category_num, start = -1L)))
-
-write_csv(less_raw, file = here::here("ignore", "data", "task_pretest.csv"))

### 2023-05-11 R/clean_q_google_demos.R

@@ -1,35 +1,0 @@
-## setup ----
-
-require(tidyverse)
-require(magrittr)
-
-googledrive::drive_download(googledrive::as_id("1yW13tK4dVr8MXtJTaZxV_3M8IaD5TqhbzD8QKPuEndM"),
-                            path = here::here("ignore", "data", "raw", "real", "demographics.csv"),
-                            type = "csv",
-                            overwrite = TRUE)
-
-## read n parse ----
-
-# Must do col transforming after dropping unwanted cols
-# col_types and cols_only don't seem to drop cols smoothly
-demos <- read_csv(here::here("ignore", "data", "raw", "real", "demographics.csv")) %>% 
-  select(study_name = "Study Name [***Do Not Edit***]",
-         timestamp = Timestamp,
-         demographics_id = "Participant ID [***Do Not Edit***]",
-         age = Age,
-         edu = "Years of Education",
-         gender = Gender,
-         ethnicity = Ethnicity,
-         race = "Race (check all that apply)") %>% 
-  mutate(timestamp = lubridate::parse_date_time(timestamp, "mdY HMS")) %>% 
-  filter(study_name == "JStudy", timestamp >= "2021-06-23") %>% 
-  mutate(gender = case_when(tolower(gender) %in% c("m", "male") ~ "male",
-                            tolower(gender) %in% c("f", "female") ~ "female",
-                            grepl("nonbinary|genderqueer", gender, ignore.case = T) ~ "genderqueer",
-                            grepl("male", gender, ignore.case = T) & !grepl("female", gender, ignore.case = T) ~ "male",
-                            grepl("female", gender, ignore.case = T)  ~ "female",
-                            grepl("man", gender, ignore.case = T) & !grepl("woman", gender, ignore.case = T) ~ "male",
-                            grepl("woman", gender, ignore.case = T)  ~ "female",
-                            TRUE ~ NA_character_))
-
-write_csv(demos, here::here("ignore", "data", "q_google_demos.csv"))

### 2023-05-11 R/clean_q_posttask.R

@@ -1,14 +1,0 @@
-require(tidyverse)
-require(magrittr)
-source(here::here("R", "utils_read_gorilla.R"))
-
-raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
-  read_gorilla_data("questionnaire-qdx5")
-
-less_raw <- raw %>% 
-  select(subj_num = `Participant Private ID`, q_key = `Question Key`, resp = Response) %>%
-  filter(!endsWith(q_key, "QUESTIONNAIRE")) %>% 
-  pivot_wider(names_from = q_key, values_from = resp) %>% 
-  rename_with(~str_replace(., "-", "_"), everything())
-
-write_csv(less_raw, file = here::here("ignore", "data", "q_posttask.csv"))

### 2023-05-11 R/clean_q_trivia_demos.R

@@ -1,15 +1,0 @@
-require(tidyverse)
-require(magrittr)
-source(here::here("R", "utils_read_gorilla.R"))
-
-raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
-  read_gorilla_data("questionnaire-d6y6")
-
-less_raw <- raw %>% 
-  select(subj_num = `Participant Private ID`, q_key = `Question Key`, resp = Response) %>%
-  filter(!endsWith(q_key, "QUESTIONNAIRE")) %>% 
-  pivot_wider(names_from = q_key, values_from = resp) %>% 
-  rename_with(~str_replace(., "-", "_"), everything()) %>% 
-  mutate(across(c(starts_with("trivia"), ends_with("quantised")), as.integer))
-
-write_csv(less_raw, file = here::here("ignore", "data", "q_trivia_demos.csv"))

### 2023-05-11 R/clean_retrieval_facts.R

@@ -1,71 +1,0 @@
-require(tidyverse)
-require(magrittr)
-source(here::here("R", "utils_read_gorilla.R"))
-
-## reading in and cleaning ----
-
-raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
-  read_gorilla_data("task-txhz")
-
-pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
-  select(-n_correct) %>%
-  pivot_wider(names_from = category_num, values_from = category, names_prefix = "category") %>%
-  mutate(categories = paste(category1, category2, sep = "_"))
-
-less_raw <- raw %>% 
-  select(subj_num = `Participant Private ID`,
-         group,
-         encoding_block,
-         group_trial_num = trial_num,
-         retrieval_trial_num = `Trial Number`,
-         trial_screen = `Screen Name`,
-         zone = `Zone Name`,
-         rt = `Reaction Time`,
-         resp = `Response`,
-         timeout = `Timed Out`,
-         starts_with("test_question"),
-         starts_with("test_answer")) %>%
-  filter(trial_screen == "recall") %>%
-  mutate(retrieval_trial_num = as.integer(retrieval_trial_num),
-         timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout)) %>%
-  nest(data = -c(subj_num, retrieval_trial_num)) %>% 
-  # patch in a "response" row if fully timed out
-  mutate(data = map(data,
-                    function (x) {
-                      if (nrow(x) == 1) {
-                        if (x$zone == "timelimit") {
-                          x$zone <- "response"
-                        }
-                      }
-                      return (x)
-                    })) %>% 
-  unnest(data) %>% 
-  filter(zone == "response") %>%
-  select(-c(trial_screen, zone)) %>% 
-  nest(data = -c(subj_num, retrieval_trial_num)) %>% 
-  mutate(data = map(data, get_typing_rts)) %>% 
-  unnest(data) %>% 
-  nest(data = -subj_num) %>% 
-  left_join(pretest, by = "subj_num") %>% 
-  mutate(data = map2(data, categories,
-                     ~.x %>% select(group,
-                                    group_trial_num,
-                                    retrieval_trial_num,
-                                    resp,
-                                    rt_start,
-                                    rt_end,
[…]

### 2023-05-11 R/clean_retrieval_pics.R

@@ -1,73 +1,0 @@
-require(tidyverse)
-require(magrittr)
-source(here::here("R", "utils_read_gorilla.R"))
-
-raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
-  read_gorilla_data("task-3n9k|task-cuj6")
-
-pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
-  select(-n_correct) %>%
-  pivot_wider(names_from = category_num, values_from = category, names_prefix = "category") %>%
-  mutate(categories = paste(category1, category2, sep = "_"))
-
-less_raw <- raw %>% 
-  select(subj_num = `Participant Private ID`,
-         group,
-         trial_num,
-         trial_screen = `Screen Name`,
-         zone = `Zone Name`,
-         rt = `Reaction Time`,
-         resp = `Response`,
-         timeout = `Timed Out`,
-         encoding_pic = `counterbalance-mqv3`,
-         # retrieval_pic_oldnew = `counterbalance-ekxi`,
-         retrieval_pic_2afc = `randomiser-snec`,
-         starts_with("pic_c"),
-         starts_with("pic_d")) %>% 
-  filter(trial_screen == "test") %>% 
-  mutate(across(c(trial_num, resp), as.integer),
-         timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout)) %>% 
-  nest(data = -c(subj_num, group, trial_num)) %>% 
-  # stuff to pull only the row of scale trials where the slider stopped moving
-  mutate(data = map(data, get_slider_rt)) %>%
-  unnest(data) %>% 
-  select(-c(trial_screen, zone)) %>% 
-  nest(data = -subj_num) %>% 
-  left_join(pretest, by = "subj_num") %>% 
-  mutate(data = map2(data, categories,
-                     ~.x %>% select(group,
-                                    trial_num,
-                                    contains("_pic"),
-                                    resp,
-                                    rt,
-                                    pic_c = paste0("pic_c.", .y),
-                                    pic_d = paste0("pic_d.", .y)))) %>%
-  unnest(data)
-
-d_2afc <- less_raw %>% 
-  filter(!is.na(retrieval_pic_2afc)) %>% 
[…]

### 2023-05-11 R/clean_retrieval_source.R

@@ -1,46 +1,0 @@
-require(tidyverse)
-require(magrittr)
-source(here::here("R", "utils_read_gorilla.R"))
-
-raw <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T) %>% 
-  read_gorilla_data("task-1152|task-iqq7|task-dyao")
-
-pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
-  select(-n_correct) %>%
-  pivot_wider(names_from = category_num, values_from = category, names_prefix = "category") %>%
-  mutate(categories = paste(category1, category2, sep = "_"))
-
-less_raw <- raw %>% 
-  select(subj_num = `Participant Private ID`,
-         group,
-         group_trial_num = trial_num,
-         trial_screen = `Screen Name`,
-         zone = `Zone Name`,
-         rt = `Reaction Time`,
-         resp = `Response`,
-         timeout = `Timed Out`,
-         starts_with("encoding_sentence")) %>% 
-  filter(trial_screen == "test") %>% 
-  mutate(across(c(group_trial_num, resp), as.integer),
-         timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout)) %>% 
-  nest(data = -c(subj_num, group, group_trial_num)) %>% 
-  # stuff to pull only the row of scale trials where the slider stopped moving
-  mutate(data = map(data, get_slider_rt)) %>%
-  unnest(data) %>% 
-  select(-c(trial_screen, zone)) %>% 
-  nest(data = -subj_num) %>% 
-  left_join(pretest, by = "subj_num") %>% 
-  mutate(data = map2(data, categories,
-                     ~.x %>% select(group,
-                                    group_trial_num,
-                                    resp,
-                                    rt,
-                                    encoding_sentence = paste0("encoding_sentence.", .y)))) %>%
-  unnest(data) %>% 
-  mutate(category = if_else(group == "academic", category1, category2),
-         encoding_block = if_else(group_trial_num <= 20, 0L, 1L),
-         resp = if_else(encoding_block == 1, resp - 50, -(resp - 50)),
-         resp_binary = if_else(resp > 0, 1L, 0L)) %>% 
-  select(-c(category1, category2, categories))
-
-write_csv(less_raw, file = here::here("ignore", "data", "task_retrieval_source.csv"))

### 2023-05-11 R/get_cleaned_data.R

@@ -4,10 +4,11 @@ require(magrittr)
 demos_ids <- read_csv(here::here("ignore", "data", "demos_ids.csv"))
 q_google_demos <- read_csv(here::here("ignore", "data", "q_google_demos.csv")) %>% 
   right_join(demos_ids, by = "demographics_id") %>% 
-  mutate(subj_num = factor(subj_num))
+  mutate(subj_num = factor(subj_num)) %>% 
+  # One subject seems to have filled it out twice but gave the same data both times (thank god)
+  distinct(subj_num, age, edu, gender, ethnicity, race)
 
-j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv")) %>% 
-  mutate(resp_conf = if_else(is.na(resp_recall), NA_real_, resp_conf))
+j_recall <- read_csv(here::here("ignore", "data", "task_jeopardy_recall.csv"))
 
 j_exp <- j_recall %>% 
   group_by(subj_num) %>% 
@@ -27,12 +28,7 @@ j_meta_desc <- read_csv(here::here("ignore", "data", "task_jeopardy_meta_descrip
 
 encoding <- read_csv(here::here("ignore", "data", "task_encoding.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
-  mutate(subj_num = fct_reorder(as.character(subj_num), j_score),
-         already_knew = fct_recode(already_knew,
-                                   none = "Did not know this before",
-                                   some = "Knew some of this before",
-                                   all = "Knew all of this before"),
-         already_knew = fct_relevel(already_knew, "all", after = Inf))
+  mutate(subj_num = fct_reorder(as.character(subj_num), j_score))
 
 r_facts <- read_csv(here::here("ignore", "data",  "task_retrieval_facts.csv")) %>% 
   left_join(j_exp, by = "subj_num") %>% 
@@ -49,24 +45,3 @@ q_trivia_demos  <- read_csv(here::here("ignore", "data", "q_trivia_demos.csv")) 
 
 q_posttask  <- read_csv(here::here("ignore", "data", "q_posttask.csv"))
 
-retrieval <- r_facts %>%
-  select(subj_num, j_score, group, group_trial_num, retrieval_block, ep_is_same, sem_is_same, retrieval_trial_num, category, acc_recall, rt_start_recall = rt_start, rt_end_recall = rt_end) %>% 
-  left_join(r_pics %>% 
[…]

### 2023-05-11 R/make_models.R

@@ -1,111 +1,0 @@
-## setup ----
-
-require(tidymodels)
-require(multilevelmod)
-require(magrittr)
-require(rlang)
-require(tidyverse)
-
-options(mc.cores = 4)
-
-## load data ----
-
-source(here::here("R", "get_cleaned_data.R"))
-
-## prep data further ----
-
-retrieval_modelsafe <- retrieval %>%
-  # Just drop those extra columns now
-  # The validation is super annoying when there's a bunch of leftover cols
-  select(subj_num, 
-         acc_recall, 
-         resp_pic, resp_source, 
-         j_score, 
-         encoding_trial_num, 
-         interest, 
-         already_knew)
-
-base_recipe <- recipe(retrieval_modelsafe) %>% 
-  step_filter(already_knew == "none") %>% 
-  update_role(acc_recall, new_role = "outcome") %>% 
-  update_role(c(resp_pic, resp_source, j_score, encoding_trial_num, interest, subj_num), new_role = "predictor") %>% 
-  # so I don't have to put already_knew into the preplot new data
-  update_role_requirements(role = "NA", bake = FALSE) %>% 
-  # update_role(subj_num, new_role = "ID") %>% 
-  # Sort of a roundabout way of discretizing and then re-numeric-izing these variables
-  # But it just seems better than changing the global contrasts option
-  # and using the dummy variables steps
-  # Have to use num2factor instead of cut because cut doesn't currently output ordered
-  step_num2factor(acc_recall,
-                  # num2factor expects factor levels to start at 1
-                  transform = \(x) ifelse(x > 0, 2, 1),
-                  levels = c("incorrect", "correct"),
-                  ordered = TRUE,
-                  # bc it's an outcome var, skip when running with predict
-                  skip = TRUE) %>% 
-  # so that leaving the slider as 0 gets binned in with incorrect
-  step_num2factor(c(resp_pic, resp_source),
-                  transform = \(x) ifelse(x > 0, 2, 1),
-                  levels = c("incorrect", "correct"),
-                  ordered = TRUE) %>% 
-  step_num2factor(encoding_trial_num,
-                  transform = \(x) ifelse(x > 40, 2, 1),
-                  levels = c("early", "late"),
-                  ordered = TRUE) %>% 
-  step_ordinalscore(c(resp_pic, resp_source, encoding_trial_num)) %>%
-  # to get it to -0.5 and +0.5
[…]

### 2023-05-11 R/make_preplots.R

@@ -1,150 +1,0 @@
-## setup ----
-
-require(rstanarm)
-require(tidymodels)
-require(multilevelmod)
-require(magrittr)
-require(rlang)
-require(tidyverse)
-
-## load data ----
-
-load(here::here("ignore", "data", "models.rda"))
-
-## functions ----
-
-posterior_preplot_params <- function (object) {
-  out <- object %>%
-    extract_fit_engine() %>% 
-    as.data.frame() %>%
-    as_tibble() %>%
-    mutate(iteration = 1:nrow(.)) %>%
-    # removes all random effects and sigma terms. should yield fixed effects only
-    select(-contains("["), -contains("sigma")) %>%
-    rename(intercept = "(Intercept)") %>%
-    pivot_longer(cols = -iteration, names_to = "term", values_to = "estimate")
-  
-  return (out)
-}
-
-posterior_preplot_bysubj <- function (object, newdata, pred_col = "y_pred", draws = 1000) {
-  
-  preproc <- object %>% 
-    extract_recipe()
-  
-  newdata <- preproc %>% 
-    bake(new_data = newdata)
-  
-  out <- object %>%
-    extract_fit_engine() %>% 
-    rstanarm::posterior_epred(newdata = newdata,
-                              re.form = NULL,
-                              draws = draws)
-  
-  # Just the median of every predicted point for every subject
-  # Note that this doesn't select in a paired way for the "median iteration"
-  # returns a VECTOR which needs to get slapped onto newdata
-  out %<>%
-    apply(2, median) %>%
-    t() %>%
-    c()
-  
-  newdata %<>%
-    mutate(!!pred_col := out)
-  
-  return (newdata)
-}
-
-posterior_preplot_fixef <- function (object, newdata, pred_col = "y_pred", draws = 1000) {
-  
-  preproc <- object %>% 
-    extract_recipe()
-  
-  newdata <- preproc %>% 
-    bake(new_data = newdata)
-  
-  out <- object %>%
-    extract_fit_engine() %>% 
-    rstanarm::posterior_epred(newdata = newdata,
-                              re.form = NA,
-                              draws = draws)
-  
-  newdata %<>%
-    # Must expand AFTER predictions is already done to repeat for iterations
-    # need the "obs" column to make damn sure that the correct predicted points get pasted on the correct x values
-    mutate(obs = 1:nrow(.),
[…]

### 2023-05-11 R/preproc/clean_demos_ids.R

@@ -1,0 +1,10 @@
+clean_demos_ids <- function (id_data) {
+  out <- id_data %>% 
+    select(subj_num = `Participant Private ID`, q_key = `Question Key`, resp = Response) %>%
+    filter(!endsWith(q_key, "QUESTIONNAIRE")) %>% 
+    pivot_wider(names_from = q_key, values_from = resp)
+  
+  return (out)
+}
+
+# write_csv(less_raw, file = here::here("ignore", "data", "demos_ids.csv"))

### 2023-05-11 R/preproc/clean_encoding.R

@@ -1,0 +1,52 @@
+clean_encoding <- function (encoding_data, pretest_data) {
+  out <- encoding_data %>% 
+    select(subj_num = `Participant Private ID`,
+           group,
+           group_trial_num = trial_num,
+           trial_screen = `Screen Name`,
+           zone = `Zone Name`,
+           rt = `Reaction Time`,
+           resp = `Response`,
+           starts_with("encoding_sentence")) %>% 
+    filter((trial_screen == "fact" & zone == "slider") | trial_screen == "already_knew") %>%
+    nest(data = -c(subj_num, group, group_trial_num, trial_screen)) %>%
+    pivot_wider(names_from = trial_screen, values_from = data) %>% 
+    mutate(already_knew = map_chr(already_knew, ~.x$resp)) %>% 
+    unnest(fact) %>% 
+    mutate(# Should catch slider trials where the slider was never clicked
+      # bc I think timeout will still be true if submitResp was never clicked but the slider was moved
+      resp = if_else(zone == "scale" & rt >= 34900, NA_character_, resp),
+      resp = as.integer(resp)) %>%
+    nest(data = -c(subj_num, group, group_trial_num)) %>% 
+    # stuff to pull only the row of scale trials where the slider stopped moving
+    mutate(data = map(data, get_slider_rt)) %>%
+    unnest(data) %>% 
+    # this SHOULD keep one row per trial and also keep no responses
+    select(-zone) %>% 
+    nest(data = -subj_num) %>% 
+    left_join(pretest_data, by = "subj_num") %>% 
+    mutate(data = map2(data, categories,
+                       ~.x %>% select(group_trial_num,
+                                      group,
+                                      resp,
+                                      rt,
+                                      already_knew,
+                                      encoding_sentence = paste0("encoding_sentence.", .y)))) %>%
+    unnest(data) %>% 
+    mutate(category = if_else(group == "academic", category1, category2)) %>% 
+    select(-c(category1, category2, categories)) %>% 
+    mutate(already_knew = fct_recode(already_knew,
+                                     none = "Did not know this before",
+                                     some = "Knew some of this before",
+                                     all = "Knew all of this before"),
+           already_knew = fct_relevel(already_knew, "all", after = Inf))
+  
+  return (out)
+}
+
+# pretest <- read_csv(here::here("ignore", "data", "task_pretest.csv")) %>%
+#   select(-n_correct) %>%
[…]

### 2023-05-11 R/preproc/clean_expertise.R

@@ -1,0 +1,55 @@
+clean_expertise <- function (expertise_data) {
+  out <- expertise_data %>% 
+    # Just this one P had a weird task lapse where 2.5 trials repeated
+    filter(!(`Participant Private ID` == 4488331 & `Event Index` %in% 74:86)) %>% 
+    select(subj_num = `Participant Private ID`,
+           trial_num = `Trial Number`,
+           trial_screen = `Screen Name`,
+           zone = `Zone Name`,
+           rt = `Reaction Time`,
+           resp = `Response`,
+           timeout = `Timed Out`,
+           question,
+           answer) %>%
+    filter(trial_screen %in% c("recall", "confidence")) %>%
+    mutate(trial_num = as.integer(trial_num),
+           timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout),
+           # Should catch slider trials where the slider was never clicked
+           # bc I think timeout will still be true if submitResp was never clicked but the slider was moved
+           resp = if_else(zone == "scale" & rt >= 14900, NA_character_, resp),
+           # Fix the typo for the older subjects so the question text doesn't appear repeated
+           question = str_replace(question, "1890", "1899"),
+           answer = if_else(answer == "SF Giants", "San Francisco Giants", answer)) %>%
+    nest(data = -c(subj_num, trial_num, trial_screen)) %>% 
+    # patch in a "response" row if fully timed out
+    mutate(data = map(data,
+                      function (x) {
+                        if (nrow(x) == 1) {
+                          if (x$zone == "timelimit") {
+                            x$zone <- "response"
+                          }
+                        }
+                        return (x)
+                      })) %>% 
+    unnest(data) %>% 
+    filter(!(zone %in% c("continueButton", "timelimit"))) %>%
+    # stuff to pull only the row of scale trials where the slider stopped moving
+    nest(data = -c(subj_num, trial_num, trial_screen)) %>%
+    pivot_wider(names_from = trial_screen, values_from = data) %>% 
+    mutate(confidence = map(confidence, ~.x %>% 
+                              mutate(resp = as.integer(resp)) %>% 
+                              get_slider_rt()),
+           confidence = map(confidence,
+                            ~.x %>%
+                              select(resp, rt, timeout) %>% 
+                              rename_with(~paste0(., "_conf"), everything())),
+           recall = map(recall, ~.x %>% 
+                          select(-zone) %>% 
[…]

### 2023-05-11 R/preproc/clean_metamemory.R

@@ -1,0 +1,38 @@
+clean_metamemory <- function (metamemory_data) {
+  out <- metamemory_data %>% 
+    select(subj_num = `Participant Private ID`,
+           trial_num = `Trial Number`,
+           trial_screen = `Screen Name`,
+           zone = `Zone Name`,
+           rt = `Reaction Time`,
+           resp = `Response`,
+           timeout = `Timed Out`,
+           question,
+           answer) %>% 
+    mutate(question = str_replace(question, "1890", "1899"),
+           answer = if_else(answer == "SF Giants", "San Francisco Giants", answer))
+  
+  return (out)
+}
+
+clean_metamemory_states <- function (metamemory_data) {
+  out <- metamemory_data %>%
+    clean_metamemory() %>% 
+    filter(trial_screen == "recall") %>% 
+    select(-c(trial_screen, zone))
+  
+  return (out)
+}
+
+# write_csv(mem_states, file = here::here("ignore", "data", "task_jeopardy_meta_states.csv"))
+
+clean_metamemory_descriptions <- function (metamemory_data) {
+  out <- metamemory_data %>%
+    clean_metamemory() %>% 
+    filter(trial_screen == "describe" & zone == "response") %>% 
+    select(subj_num, trial_num, question, resp)
+  
+  return (out)
+}
+
+# write_csv(mem_descriptions, file = here::here("ignore", "data", "task_jeopardy_meta_descriptions.csv"))

### 2023-05-11 R/preproc/clean_pretest.R

@@ -1,0 +1,23 @@
+clean_pretest <- function (pretest_data) {
+  out <- pretest_data %>% 
+    select(subj_num = "Participant Private ID",
+           category_num = "Zone Name",
+           category = "Response",
+           n_correct = "Reaction Time") %>% 
+    filter(startsWith(category_num, "category")) %>% 
+    mutate(category_num = as.integer(str_sub(category_num, start = -1L)))
+  
+  return (out)
+}
+
+# the encoding and retrieval cleaning functions expect a slightly reshaped version
+reshape_pretest <- function (pretest_data_clean) {
+  out <- pretest_data_clean %>%
+    select(-n_correct) %>%
+    pivot_wider(names_from = category_num, values_from = category, names_prefix = "category") %>%
+    mutate(categories = paste(category1, category2, sep = "_"))
+  
+  return (out)
+}
+
+# write_csv(less_raw, file = here::here("ignore", "data", "task_pretest.csv"))

### 2023-05-11 R/preproc/clean_q_google_demos.R

@@ -1,0 +1,31 @@
+clean_q_google_demos <- function (demo_data, id_data) {
+  # Must do col transforming after dropping unwanted cols
+  # col_types and cols_only don't seem to drop cols smoothly
+  out <- demo_data %>% 
+    select(study_name = "Study Name [***Do Not Edit***]",
+           timestamp = Timestamp,
+           demographics_id = "Participant ID [***Do Not Edit***]",
+           age = Age,
+           edu = "Years of Education",
+           gender = Gender,
+           ethnicity = Ethnicity,
+           race = "Race (check all that apply)") %>% 
+    mutate(timestamp = lubridate::parse_date_time(timestamp, "mdY HMS")) %>% 
+    filter(study_name == "JStudy", timestamp >= "2021-06-23") %>% 
+    mutate(gender = case_when(tolower(gender) %in% c("m", "male") ~ "male",
+                              tolower(gender) %in% c("f", "female") ~ "female",
+                              grepl("nonbinary|genderqueer", gender, ignore.case = T) ~ "genderqueer",
+                              grepl("male", gender, ignore.case = T) & !grepl("female", gender, ignore.case = T) ~ "male",
+                              grepl("female", gender, ignore.case = T)  ~ "female",
+                              grepl("man", gender, ignore.case = T) & !grepl("woman", gender, ignore.case = T) ~ "male",
+                              grepl("woman", gender, ignore.case = T)  ~ "female",
+                              TRUE ~ NA_character_)) %>% 
+    right_join(id_data, by = "demographics_id") %>% 
+    mutate(subj_num = factor(subj_num)) %>% 
+    # One subject seems to have filled it out twice but gave the same data both times (thank god)
+    distinct(subj_num, age, edu, gender, ethnicity, race)
+  
+  return (out)
+}
+
+# write_csv(demos, here::here("ignore", "data", "q_google_demos.csv"))

### 2023-05-11 R/preproc/clean_q_posttask.R

@@ -1,0 +1,11 @@
+clean_q_posttask <- function (posttask_data) {
+  out <- posttask_data %>% 
+    select(subj_num = `Participant Private ID`, q_key = `Question Key`, resp = Response) %>%
+    filter(!endsWith(q_key, "QUESTIONNAIRE")) %>% 
+    pivot_wider(names_from = q_key, values_from = resp) %>% 
+    rename_with(~str_replace(., "-", "_"), everything())
+  
+  return (out)
+}
+
+# write_csv(less_raw, file = here::here("ignore", "data", "q_posttask.csv"))

### 2023-05-11 R/preproc/clean_q_trivia_demos.R

@@ -1,0 +1,12 @@
+clean_q_trivia_demos <- function (trivia_demo_data) {
+  out <- trivia_demo_data %>% 
+    select(subj_num = `Participant Private ID`, q_key = `Question Key`, resp = Response) %>%
+    filter(!endsWith(q_key, "QUESTIONNAIRE")) %>% 
+    pivot_wider(names_from = q_key, values_from = resp) %>% 
+    rename_with(~str_replace(., "-", "_"), everything()) %>% 
+    mutate(across(c(starts_with("trivia"), ends_with("quantised")), as.integer))
+  
+  return (out)
+}
+
+# write_csv(less_raw, file = here::here("ignore", "data", "q_trivia_demos.csv"))

### 2023-05-11 R/preproc/clean_retrieval.R

@@ -1,0 +1,168 @@
+clean_retrieval_facts <- function (retrieval_data, pretest_data) {
+  out <- retrieval_data %>% 
+    select(subj_num = `Participant Private ID`,
+           group,
+           encoding_block,
+           group_trial_num = trial_num,
+           retrieval_trial_num = `Trial Number`,
+           trial_screen = `Screen Name`,
+           zone = `Zone Name`,
+           rt = `Reaction Time`,
+           resp = `Response`,
+           timeout = `Timed Out`,
+           starts_with("test_question"),
+           starts_with("test_answer")) %>%
+    filter(trial_screen == "recall") %>%
+    mutate(retrieval_trial_num = as.integer(retrieval_trial_num),
+           timeout = if_else(lead(zone, 1) == "timelimit", 1L, timeout)) %>%
+    nest(data = -c(subj_num, retrieval_trial_num)) %>% 
+    # patch in a "response" row if fully timed out
+    mutate(data = map(data,
+                      function (x) {
+                        if (nrow(x) == 1) {
+                          if (x$zone == "timelimit") {
+                            x$zone <- "response"
+                          }
+                        }
+                        return (x)
+                      })) %>% 
+    unnest(data) %>% 
+    filter(zone == "response") %>%
+    select(-c(trial_screen, zone)) %>% 
+    nest(data = -c(subj_num, retrieval_trial_num)) %>% 
+    mutate(data = map(data, get_typing_rts)) %>% 
+    unnest(data) %>% 
+    nest(data = -subj_num) %>% 
+    left_join(pretest_data, by = "subj_num") %>% 
+    mutate(data = map2(data, categories,
+                       ~.x %>% select(group,
+                                      group_trial_num,
+                                      retrieval_trial_num,
+                                      resp,
+                                      rt_start,
+                                      rt_end,
+                                      test_question = paste0("test_question.", .y),
+                                      test_answer = paste0("test_answer.", .y)))) %>%
+    unnest(data) %>% 
+    mutate(category = if_else(group == "academic", category1, category2)) %>% 
+    select(-c(category1, category2, categories)) %>%
+    mutate(encoding_is_late = if_else(group_trial_num <= 20, 0L, 1L)) %>% 
+    group_by(subj_num) %>% 
[…]

### 2023-05-11 R/preproc/score_expertise.R

@@ -1,0 +1,129 @@
+clean_expertise_questions <- function (question_data) {
+  out <- question_data %>% 
+    filter(use_question == 1) %>% 
+    select(question, answer, answer_short) %>% 
+    mutate(answer_short = coalesce(answer_short, answer))
+  
+  return (out)
+}
+
+score_expertise_firstpass <- function (expertise_data_unscored, question_data) {
+  out <- expertise_data_unscored %>% 
+    left_join(question_data) %>% 
+    mutate(acc_recall_grepl_strict = map2_lgl(resp_recall, answer,
+                                              function (a, b) {
+                                                # trim non alpha nums in response in case they make grepl yell
+                                                a <- str_remove_all(a, "[^a-zA-Z\\d\\s-]")
+                                                if (is.na(a) | nchar(a) == 0) return (FALSE)
+                                                out <- (grepl(a, b, ignore.case = T) | grepl(b, a, ignore.case = T))
+                                                
+                                                return (out)
+                                              }),
+           # Particular very common misspellings that get special treatment
+           acc_recall_grepl_strict = case_when(answer == "Spanish-American War" & grepl("spanish american", resp_recall, ignore.case = T) ~ TRUE,
+                                               answer == "Andrea Bocelli" & grepl("andrea boccelli", resp_recall, ignore.case = T) ~ TRUE,
+                                               answer == "distillation" & grepl("^distill|^destill", resp_recall, ignore.case = T) ~ TRUE,
+                                               answer == "uranium" & grepl("plutonium", resp_recall, ignore.case = T) ~ FALSE,
+                                               TRUE ~ acc_recall_grepl_strict),
+           acc_recall_grepl_fuzzy = map2_lgl(resp_recall, answer,
+                                             function (a, b) {
+                                               # so titles starting with The don't get disadvantaged
+                                               # by the cost dividing by whole string length
+                                               b <- str_remove(b, "^The ")
[…]

### 2023-05-11 R/preproc/score_retrieval_facts.R

@@ -1,0 +1,147 @@
+my_agrepl <- function (pattern, x, max.distance = 0.24, ignore.case = T) {
+  return (coalesce(c(adist(pattern, x, ignore.case = ignore.case)) / nchar(pattern) <= max.distance, FALSE))
+}
+
+score_retrieval_facts_firstpass <- function (retrieval_data_unscored) {
+  out <- retrieval_data_unscored %>% 
+    mutate(acc_recall_grepl_strict = map2_lgl(resp, test_answer,
+                                              function (a, b) {
+                                                # trim non alpha nums in response in case they make grepl yell
+                                                a <- str_remove_all(a, "[^a-zA-Z\\d\\s-]")
+                                                b <- str_remove_all(b, "[^a-zA-Z\\d\\s-]")
+                                                if (is.na(a) | nchar(a) == 0) return (FALSE)
+                                                out <- (grepl(a, b, ignore.case = T) | grepl(b, a, ignore.case = T))
+                                                return (out)
+                                              }),
+           # Particular very common misspellings or key short phrases that get special treatment
+           acc_recall_grepl_strict = case_when(
+             nchar(str_remove_all(resp, "[^a-zA-Z\\d\\s-]")) / nchar(test_answer) <= 0.25 ~ FALSE,
+             group_trial_num == 1 & category == "gems" & grepl("cleav", resp, ignore.case = T) ~ TRUE,
+             group_trial_num == 13 & category == "musi" & tolower(resp) == "hurdy gurdy" ~ TRUE,
+             group_trial_num == 37 & category == "cook" & grepl("orchid", resp, ignore.case = T) ~ TRUE,
+             group_trial_num == 38 & category == "cook" & grepl("hen-of-the-woods", resp, ignore.case = T) ~ TRUE,
+             group_trial_num == 16 & category == "dino" & tolower(resp) == "nose" ~ TRUE,
+             group_trial_num == 21 & category == "dino" & grepl("medullary", resp, ignore.case = T) ~ TRUE,
+             group_trial_num == 36 & category == "dino" & grepl("saw fish", resp, ignore.case = T) ~ TRUE,
+             TRUE ~ acc_recall_grepl_strict
+           ),
+           acc_recall_grepl_fuzzy = map2_lgl(resp, test_answer,
[…]

### 2023-05-11 R/preproc/utils_read_googledrive.R

@@ -1,0 +1,9 @@
+# Basically downloads it silently, returns destination path for targets to track file
+get_googledrive_csv <- function (drive_id, destination_path) {
+  googledrive::drive_download(googledrive::as_id(drive_id),
+                              path = destination_path,
+                              type = "csv",
+                              overwrite = TRUE)
+  
+  return (destination_path)
+}

### 2023-05-11 R/preproc/utils_read_gorilla.R

@@ -1,5 +1,4 @@
-require(tidyverse)
-require(magrittr)
+# No packages libraried because this now is only called by targets!
 
 get_typing_rts <- function (df) {
   out <- df %>% 
@@ -32,8 +31,9 @@ get_slider_rt <- function (df) {
   return (out)
 }
 
-read_gorilla_data <- function (paths, node_id) {
-  out <- paths[grepl(node_id, paths)] %>%
+# Always returns one mega-df
+read_gorilla_data <- function (paths) {
+  out <- paths %>%
     map(~read_lines(.)) %>%
     .[lengths(.) > 2] %>%
     map(~head(., n = -1)) %>%
@@ -42,4 +42,8 @@ read_gorilla_data <- function (paths, node_id) {
     map(~mutate(., across(any_of(c("randomise_blocks", "Timed Out")), as.integer))) %>%
     bind_rows()
   return (out)
+}
+
+filter_paths_grepl <- function (paths, pattern) {
+  paths[grepl(pattern, paths)]
 }

### 2023-05-11 R/score_expertise.R

@@ -1,121 +1,0 @@
-## setup ----
-
-require(tidyverse)
-require(magrittr)
-
-unscored <- read_csv(here::here("ignore", "data", "task_jeopardy_recall_unscored.csv"))
-
-if (FALSE) {
-  googledrive::drive_download(file = googledrive::as_id("1e7R4CSDjSA5trC820aiwUbe7szjn7DTfMiZPI4my8Rk"),
-                              path = here::here("stim_stuff", "jeopardy_spreadsheet.csv"),
-                              type = "csv",
-                              overwrite = TRUE)
-}
-
-questions <- read_csv(here::here("stim_stuff", "jeopardy_spreadsheet.csv")) %>% 
-  filter(use_question == 1) %>% 
-  select(question, answer, answer_short) %>% 
-  mutate(answer_short = coalesce(answer_short, answer))
-
-
-## grepl scoring first pass ----
-
-scored <- unscored %>% 
-  left_join(questions) %>% 
-  mutate(acc_recall_grepl_strict = map2_lgl(resp_recall, answer,
-                                            function (a, b) {
-                                              # trim non alpha nums in response in case they make grepl yell
-                                              a <- str_remove_all(a, "[^a-zA-Z\\d\\s-]")
-                                              if (is.na(a) | nchar(a) == 0) return (FALSE)
-                                              out <- (grepl(a, b, ignore.case = T) | grepl(b, a, ignore.case = T))
-                                              
-                                              return (out)
-                                            }),
-         # Particular very common misspellings that get special treatment
-         acc_recall_grepl_strict = case_when(answer == "Spanish-American War" & grepl("spanish american", resp_recall, ignore.case = T) ~ TRUE,
-                                             answer == "Andrea Bocelli" & grepl("andrea boccelli", resp_recall, ignore.case = T) ~ TRUE,
-                                             answer == "distillation" & grepl("^distill|^destill", resp_recall, ignore.case = T) ~ TRUE,
-                                             answer == "uranium" & grepl("plutonium", resp_recall, ignore.case = T) ~ FALSE,
-                                             TRUE ~ acc_recall_grepl_strict),
[…]

### 2023-05-11 R/score_retrieval_facts.R

@@ -1,144 +1,0 @@
-## setup ----
-
-require(tidyverse)
-require(magrittr)
-
-my_agrepl <- function (pattern, x, max.distance = 0.24, ignore.case = T) {
-  return (coalesce(c(adist(pattern, x, ignore.case = ignore.case)) / nchar(pattern) <= max.distance, FALSE))
-}
-
-unscored <- read_csv(here::here("ignore", "data", "task_retrieval_facts_unscored.csv"))
-
-## grepl scoring first pass----
-
-scored <- unscored %>% 
-  mutate(acc_recall_grepl_strict = map2_lgl(resp, test_answer,
-                                            function (a, b) {
-                                              # trim non alpha nums in response in case they make grepl yell
-                                              a <- str_remove_all(a, "[^a-zA-Z\\d\\s-]")
-                                              b <- str_remove_all(b, "[^a-zA-Z\\d\\s-]")
-                                              if (is.na(a) | nchar(a) == 0) return (FALSE)
-                                              out <- (grepl(a, b, ignore.case = T) | grepl(b, a, ignore.case = T))
-                                              return (out)
-                                            }),
-         # Particular very common misspellings or key short phrases that get special treatment
-         acc_recall_grepl_strict = case_when(
-           nchar(str_remove_all(resp, "[^a-zA-Z\\d\\s-]")) / nchar(test_answer) <= 0.25 ~ FALSE,
-           group_trial_num == 1 & category == "gems" & grepl("cleav", resp, ignore.case = T) ~ TRUE,
-           group_trial_num == 13 & category == "musi" & tolower(resp) == "hurdy gurdy" ~ TRUE,
-           group_trial_num == 37 & category == "cook" & grepl("orchid", resp, ignore.case = T) ~ TRUE,
-           group_trial_num == 38 & category == "cook" & grepl("hen-of-the-woods", resp, ignore.case = T) ~ TRUE,
-           group_trial_num == 16 & category == "dino" & tolower(resp) == "nose" ~ TRUE,
-           group_trial_num == 21 & category == "dino" & grepl("medullary", resp, ignore.case = T) ~ TRUE,
-           group_trial_num == 36 & category == "dino" & grepl("saw fish", resp, ignore.case = T) ~ TRUE,
-           TRUE ~ acc_recall_grepl_strict
[…]

### 2023-05-11 _targets.R
we use targets now yay!

@@ -1,0 +1,364 @@
+## setup ----
+# Created by use_targets().
+# Follow the comments below to fill in this target script.
+# Then follow the manual to check and run the pipeline:
+#   https://books.ropensci.org/targets/walkthrough.html#inspect-the-pipeline # nolint
+
+# Load packages required to define the pipeline:
+library(targets)
+library(tarchetypes) # Load other packages as needed. # nolint
+
+# Set target options:
+tar_option_set(
+  packages = c("tidymodels",
+               "multilevelmod",
+               "rstanarm",
+               "tidyverse",
+               "magrittr",
+               "rlang"), # packages that your targets need to run
+  format = "rds" # default storage format
+  # Set other options as needed.
+)
+
+# tar_make_clustermq() configuration (okay to leave alone):
+options(# clustermq.scheduler = "multicore",
+        # For the models, sigh
+        mc.cores = 4)
+
+# tar_make_future() configuration (okay to leave alone):
+# Install packages {{future}}, {{future.callr}}, and {{future.batchtools}} to allow use_targets() to configure tar_make_future() options.
+
+# Run the R scripts in the R/ folder with your custom functions:
+tar_source(c("R/preproc/",
+             "R/analyze/"))
+
+paths_raw_data <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T)
+# source("other_functions.R") # Source other scripts as needed. # nolint
+
+## targets for demographics and subject IDs ----
+target_demos <- list(
+  tar_target(name = demos_ids_raw,
+             command = filter_paths_grepl(paths_raw_data, "questionnaire-4vcn"),
+             format = "file"),
+  tar_target(name = demos_ids,
+             command = demos_ids_raw %>% 
+               read_gorilla_data() %>% 
+               clean_demos_ids()
+  ),
+  tar_target(name = q_google_demos_raw,
+             command = get_googledrive_csv(drive_id = "1yW13tK4dVr8MXtJTaZxV_3M8IaD5TqhbzD8QKPuEndM",
+                                           destination_path = here::here("ignore", "data", "raw", "real", "demographics.csv")),
+             format = "file"),
+  tar_target(name = q_google_demos,
+             command = q_google_demos_raw %>% 
+               read_csv() %>% 
+               clean_q_google_demos(id_data = demos_ids)
+  )
+)
+
+## targets for expertise pre-test and metamemory judgments ----
[…]

### 2023-05-11 writing/ms.Rmd
more stuff for cns poster
makes cowplot grid figures now

@@
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+require(targets)
 require(tidyverse)
 require(magrittr)
+require(cowplot)
 require(rlang)
-load(here::here("ignore", "data", "preplots.rda")) # For the model params
-load(here::here("ignore", "data", "plots_ms.rda"))
+# source(here::here("R", "get_cleaned_data.R"))
+# load(here::here("ignore", "data", "preplots.rda")) # For the model params
+# load(here::here("ignore", "data", "plots_ms.rda"))
 
+target_store <- here::here("ignore", "_targets")
 signif_digits <- 3L
+
+# Specify this separately because plot annotations take their own font arg
+font_ms <- "Helvetica Neue"
+theme_ms <- theme_bw(base_size = 14,
+                     base_family = font_ms) +
+  theme(legend.background = element_blank(),
+        plot.background = element_blank())
 ```
@@
 
-coefs_fact_by_pic <- preplot_params_fact_by_pic %>%
+coefs_fact_alone <- tar_read(preplot_params_fact_alone, store = target_store) %>%
   summarize_report(col = estimate, term, stat_name = "beta")
 
-coefs_fact_by_source <- preplot_params_fact_by_source %>%
+coefs_fact_by_pic <- tar_read(preplot_params_fact_by_pic, store = target_store) %>%
+  summarize_report(col = estimate, term, stat_name = "beta")
+
+coefs_fact_by_source <- tar_read(preplot_params_fact_by_source, store = target_store) %>%
   summarize_report(col = estimate, term, stat_name = "beta")
@@
 ```{r}
-plot_demos
+q_google_demos <- tar_read(q_google_demos, store = target_store)
+j_exp <- tar_read(expertise_summarized, store = target_store)
+plot_demos <- tar_read(plot_demos, store = target_store) +
+  theme_ms +
+  theme(legend.position = c(1, 1),
+          legend.justification = c(1, 1)) 
+plot_expertise_hist <- tar_read(plot_expertise_hist, store = target_store) +
+  theme_ms
 ```
 
-```{r}
-plot_expertise_hist
+```{r figure-3}
+plot_grid(plot_demos,
+          plot_expertise_hist,
+          labels = LETTERS[1:2], ncol = 1)
 ```
+
+**Figure 3.** Participant demographics.
+**(A)** `r nrow(q_google_demos)` total participants aged 18 and up enrolled in the study (M~age~ = `r mean(q_google_demos$age, na.rm = T) %>% signif(digits = 3)` yrs, SD~age~ = `r sd(q_google_demos$age, na.rm = T) %>% signif(digits = 3)`).
+Histogram bars are stacked by participant gender such that the total bar height reflects all participants in that age bin.
+**(B)** Participants ranged in pre-existing trivia expertise, as measured by their score out of 50 questions on a cued-recall general knowledge test.
+The median expertise score was `r median(j_exp$j_score) * 50`/50 questions correct.
 
@@
 ```{r}
-plot_fact_by_expertise
+plot_fact_by_expertise <- tar_read(plot_fact_by_expertise, store = target_store)
 ```
+
+```{r}
+plot_fact_by_expertise +
+  theme_ms
+```
+
+**Figure 4.** Memory for new facts as a function of trivia expertise.
+Each point represents one participant’s percent correct fact recall.
+Participants with higher trivia expertise showed greater recall accuracy for novel facts encoded during the museum encoding phase.
+Participants with higher trivia expertise were more likely to report already knowing "some" or "all" of the presented facts at encoding [REMINDER TO PUT THE ASSOCIATED NUMBERS IN THE MAIN TEXT], so this figure shows recall only for facts that were judged to be novel.
+All subsequent analyses were also restricted to trials reported as novel at encoding.
+A linear regression line with 95% CI is plotted with ggplot2’s `geom_smooth()` to illustrate that participants with greater expertise tended to show better fact memory.
+
+Expertise score coefficient (from fancy multilevel model, takes into account diff number of trials per subject): `r coefs_fact_alone %>% filter(term == "j_score") %>% pull(txt_apa)`
 
@@
 ```{r}
-plot_coefs_fact_by_pic
+plot_coefs_fact_by_pic <- tar_read(plot_coefs_fact_by_pic, store = target_store)
+plot_fixef_fact_by_pic <- tar_read(plot_fixef_fact_by_pic, store = target_store)
+plot_pic_by_expertise <- tar_read(plot_pic_by_expertise, store = target_store)
 ```
 
-```{r}
-plot_fixef_fact_by_pic
+```{r, fig.height = 4, fig.width = 12}
+plot_grid(plot_coefs_fact_by_pic + theme_ms,
+          plot_fixef_fact_by_pic + 
+            theme_ms +
+            theme(legend.position = 0:1,
+                  legend.justification = 0:1),
+          plot_pic_by_expertise + theme_ms,
+          nrow = 1,
+          labels = LETTERS[1:3])
+# Question from Chris at Alyssano CNS practice lab meeting March 10 2023: Were trivia experts more likely to report certain facts as novel? (like, ones that might be harder)
 ```
 
+**Figure 5.** Memory for associated images predicts memory for new facts in trivia experts.
+**(A)** Coefficient estimates for a Bayesian logistic regression predicting fact recall as a function of photo memory, trivia expertise, and other covariates.
+Values are shown for the median coefficient estimate along with the 80% (thick line) and 95% (thin line) posterior intervals.
+**(B)** Predicted across-participant fixed effects from the model.
+Each line represents the simple effect of photo memory on fact recall for participants in the upper or lower half of trivia expertise estimated on a particular iteration of the Bayesian regression (2 lines per iteration, 1 for each color/trivia expertise level).
+The spread and overlap of the color ribbons can thus be taken as a holistic representation of effect size of any differences in predicted fact recall.
+An interaction is visible in the coefficients **(A)** and predicted simple effects **(B)**, such that trialwise photo memory does not predict fact recall for participants in the lower half of trivia expertise, but successful photo memory predicts successful fact recall for participants in the upper half of trivia expertise.
+Raw data for individual participants are shown behind the fixed effects, with two points and one connecting line for each participant, reflecting their raw recall accuracy for facts presented with photos that were subsequently incorrectly vs.
+correctly identified.
+**(C)** Photo memory as a function of trivia expertise.
+Each point represents one participant’s percent correct photo choice.
+The chance line is shown at y = 0.5.
+A linear regression line with 95% CI is plotted with ggplot2’s `geom_smooth()` to illustrate that trivia expertise did not predict photo memory.
+
 Interaction coefficient: `r coefs_fact_by_pic %>% filter(term == "resp_pic:j_score") %>% pull(txt_apa)`
-
-```{r}
-plot_pic_by_expertise
-```
 
@@
 ```{r}
-plot_coefs_fact_by_source
+plot_coefs_fact_by_source <- tar_read(plot_coefs_fact_by_source, store = target_store)
+plot_fixef_fact_by_source <- tar_read(plot_fixef_fact_by_source, store = target_store)
+plot_source_by_expertise <- tar_read(plot_source_by_expertise, store = target_store)
 ```
 
-```{r}
-plot_fixef_fact_by_source
+```{r, fig.height = 4, fig.width = 12}
+plot_grid(plot_coefs_fact_by_source + theme_ms,
+          plot_fixef_fact_by_source + 
+            theme_ms +
+            theme(legend.position = 0:1,
+                  legend.justification = 0:1),
+          plot_source_by_expertise + theme_ms,
+          nrow = 1,
+          labels = LETTERS[1:3])
 ```
+
+**Figure 6.** Memory for encoding source (i.e., museum identity) predicts memory for new facts.
+**(A)** Coefficient estimates for a Bayesian logistic regression predicting fact recall as a function of museum memory, trivia expertise, and other covariates.
+Values are shown for the median coefficient estimate along with the 80% (thick line) and 95% (thin line) posterior intervals.
+**(B)** Predicted across-participant fixed effects from the model.
+Each line represents the simple effect of museum memory on fact recall for participants in the upper or lower half of trivia expertise estimated on a particular iteration of the Bayesian regression (2 lines per iteration, 1 for each color/trivia expertise level).
+The spread and overlap of the color ribbons can thus be taken as a holistic representation of effect size of any differences in predicted fact recall.
+Two main effects are visible in the coefficients **(A)** and predicted simple effects **(B)**, such that trialwise museum memory predicts fact recall for participants irrespective of trivia expertise, and participants in the upper half of trivia expertise have greater fact recall irrespective of museum memory.
+Raw data for individual participants are shown behind the fixed effects, with two points and one connecting line for each participant, reflecting their raw recall accuracy for facts associated with museums that were subsequently incorrectly vs.
+correctly identified as the encoding source.
+**(C)** Museum memory as a function of trivia expertise.
+Each point represents one participant’s percent correct museum choice.
+The chance line is shown at y = 0.5.
+A linear regression line with 95% CI is plotted with ggplot2’s `geom_smooth()` to illustrate that participants with greater expertise tended to show better museum memory.
 
@@
 
+## Figure 7
+
+This may come to supplant both figures 5 and 6 if we move forward with this version of the analysis.
+
 ```{r}
-plot_source_by_expertise
+plot_coefs_fact_by_both <- tar_read(plot_coefs_fact_by_both, store = target_store)
+plot_fixef_fact_by_both <- tar_read(plot_fixef_fact_by_both, store = target_store)
 ```
+
+```{r, fig.height = 4, fig.width = 12}
+plot_grid(plot_coefs_fact_by_both + theme_ms,
+          plot_fixef_fact_by_both + 
+            theme_ms +
+            theme(legend.position = 0:1,
+                  legend.justification = 0:1),
+          nrow = 1,
+          labels = LETTERS[1:2])
+```
+
+**Figure 7.** Memory for associated episodic details interacts to predict memory for new facts.
+**(A)** Coefficient estimates for a Bayesian logistic regression predicting fact recall.
+Values are shown for the median coefficient estimate along with the 80% (thick line) and 95% (thin line) posterior intervals.
+**(B)** Predicted across-participant fixed effects from the model.
+Each line represents the simple effect of museum memory on fact recall for participants in the upper or lower half of trivia expertise estimated on a particular iteration of the Bayesian regression (2 lines per iteration, 1 for each color/trivia expertise level).
+The spread and overlap of the color ribbons can thus be taken as a holistic representation of effect size of any differences in predicted fact recall.
+Raw data for individual participants are shown behind the fixed effects, with two points and one connecting line for each participant, reflecting their raw recall accuracy for facts presented with photos that were subsequently incorrectly vs.
+correctly identified.
+The left and right panels split up trials with museums that were subsequently incorrectly vs.
+correctly identified as the encoding source.
+Two main effects are visible in the coefficients **(A)** and predicted simple effects **(B)**, such that trialwise museum memory predicts fact recall for participants irrespective of trivia expertise, and participants in the upper half of trivia expertise have greater fact recall irrespective of museum memory.
+A two-way interaction between photo and museum memory is visible, such that fact recall is higher when participants correctly recognized _both_ the associated photo and encoding museum.
+Finally, a three-way interaction is visible, such that that two-way interaction effect of joint photo and museum memory predicting fact recall is stronger for participants higher in trivia expertise.
 

### 2023-05-18 _targets.R
preplots estimated in middle of encoding_trial_num

@@ -228,7 +228,7 @@ target_preplots <- list(
              command = expertise_summarized %>%
                mutate(subj_num = fct_reorder(as.character(subj_num), j_score)) %>% 
                expand(nesting(subj_num, j_score), 
-                      encoding_trial_num = 1, 
+                      encoding_trial_num = 40.5, 
                       nesting(resp_pic = c(-50, 50),
                               resp_source = c(-50, 50)), 
                       interest = seq(0, 100, 10),
@@ -246,7 +246,7 @@ target_preplots <- list(
   ),
   tar_target(name = newdata_preplot_fixef,
              command = crossing(j_score = c(0.5, 0.8),
-                                encoding_trial_num = 1,
+                                encoding_trial_num = 40.5,
                                 interest = 50,
                                 resp_pic = c(-50, 50),
                                 resp_source = c(-50, 50),

### 2023-05-18 R/analyze/make_plots_ms.R
move ms plots over

@@ -92,7 +92,7 @@ make_plot_coefs_fact_by_pic <- function (preplot_params) {
                              "Intercept" = "intercept",
                              "Interest at encoding" = "interest",
                              "Trivia expertise" = "j_score",
-                             "Photo from second museum?" = "from_encoding_late",
+                             "First vs. second museum?" = "from_encoding_late",
                              "Photo memory" = "resp_pic",
                              "Expertise x photo memory" = "resp_pic:j_score")) %>% 
     make_plot_coefs()
@@ -112,7 +112,7 @@ make_plot_coefs_fact_by_source <- function (preplot_params) {
                              "Intercept" = "intercept",
                              "Interest at encoding" = "interest",
                              "Trivia expertise" = "j_score",
-                             "Fact from second museum?" = "from_encoding_late",
+                             "First vs. second museum?" = "from_encoding_late",
                              "Museum memory" = "resp_source",
                              "Expertise x museum memory" = "resp_source:j_score")) %>% 
     make_plot_coefs()
@@ -136,7 +136,7 @@ make_plot_coefs_fact_by_both <- function (preplot_params) {
                              "Intercept" = "intercept",
                              "Interest at encoding" = "interest",
                              "Trivia expertise" = "j_score",
-                             "Fact from second museum?" = "from_encoding_late",
+                             "First vs. second museum?" = "from_encoding_late",
                              "Photo memory" = "resp_pic",
                              "Museum memory" = "resp_source",
                              "Expertise x photo memory" = "resp_pic:j_score",
@@ -186,32 +186,30 @@ make_plot_fixef_fact_by_both <- function (preplot_fixef, retrieval_data) {
   retrieval_summarized <- retrieval_data %>% 
     filter(already_knew == "none") %>% 
     mutate(acc_recall = as.numeric(acc_recall > 0),
-           resp_pic = if_else(resp_pic > 0, "correct", "incorrect"),
-           resp_source = if_else(resp_source > 0, "correct museum", "incorrect museum"),
-           j_score = if_else(j_score > 0.7, "upper half", "lower half")) %>% 
+           across(c(resp_pic, resp_source), \(x) if_else(x > 0, "correct", "incorrect")),
+           j_score = if_else(j_score > 0.7, "upper half of expertise", "lower half of expertise")) %>% 
[…]

### 2023-05-18 R/make_plots.R

@@ -7,16 +7,7 @@ source(here::here("R", "get_cleaned_data.R"))
 # For the model outputs
 load(here::here("ignore", "data", "preplots.rda"))
 
-# A function factory for getting integer y-axis values.
-# From https://joshuacook.netlify.app/post/integer-values-ggplot-axis/
-integer_breaks <- function(n = 5, ...) {
-  fxn <- function(x) {
-    breaks <- floor(pretty(x, n, ...))
-    names(breaks) <- attr(breaks, "labels")
-    breaks
-  }
-  return(fxn)
-}
+
 
 # Aileron family for slides
 # Something else...? for manuscript?
@@ -30,15 +21,9 @@ theme_slides_ppt <- theme_bw(base_size = 22,
   theme(legend.background = element_blank(),
         plot.background = element_blank())
 
+font_poster <- "ITC Korinna Regular"
 theme_poster <- theme_bw(base_size = 26,
-                         base_family = "Helvetica Neue") +
-  theme(legend.background = element_blank(),
-        plot.background = element_blank())
-
-# Specify this separately because plot annotations take their own font arg
-font_ms <- "Helvetica Neue"
-theme_ms <- theme_bw(base_size = 14,
-                     base_family = font_ms) +
+                         base_family = font_poster) +
   theme(legend.background = element_blank(),
         plot.background = element_blank())
 
@@ -46,38 +31,9 @@ this_font <- font_ms
 this_theme <- theme_ms
 ## demographics ----
 
-plot_demos <- q_google_demos %>% 
-  mutate(gender = coalesce(gender, "not reported")) %>% 
-  left_join(q_google_demos %>%
-              count(gender) %>%
-              mutate(gender = coalesce(gender, "not reported"),
-                     gender_n = glue::glue("{gender} (n = {n})")) %>%
-              select(-n),
-            by = "gender") %>% 
-  ggplot(aes(x = age, fill = gender_n)) +
-  geom_histogram(position = "stack", alpha = 0.5, binwidth = 2) +
-  scale_y_continuous(breaks = integer_breaks()) +
-  labs(y = "# of participants",
-       fill = "gender") +
-  this_theme +
-  theme(legend.position = c(1, 1),
-        legend.justification = c(1, 1))
+
 
 ## trivia expertise ----
-
-plot_expertise_hist <- j_exp %>% 
-  ggplot(aes(x = j_score)) +
-  geom_histogram(binwidth = .05, fill = "gray80") +
[…]

### 2023-05-18 R/analyze/make_models.R
leave opening for newdata to hit encoding_trial_num middle

@@ -41,9 +41,16 @@ make_recipe <- function (retrieval_data_prepped) {
                     transform = \(x) ifelse(x > 0, 2, 1),
                     levels = c("incorrect", "correct"),
                     ordered = TRUE) %>% 
+    # So that there is a value that will get treated as the true middle
+    # Should never appear for the purposes of modeling
+    # But we need to be able to get a hypothetical middle trial for preplots
+    # with the effect code at 0
     step_num2factor(encoding_trial_num,
-                    transform = \(x) ifelse(x > 40, 2, 1),
-                    levels = c("early", "late"),
+                    transform = \(x) case_when(x >= 41 ~ 3,
+                                               x > 40 & x < 41 ~ 2,
+                                               x <= 40 ~ 1,
+                                               TRUE ~ NA_real_),
+                    levels = c("early", "mid", "late"),
                     ordered = TRUE) %>% 
     step_ordinalscore(c(resp_pic, resp_source, encoding_trial_num)) %>%
     # to get it to -0.5 and +0.5

### 2023-05-18 writing/ms.Rmd
add loose stats for model fact by both

@@
 coefs_fact_by_source <- tar_read(preplot_params_fact_by_source, store = target_store) %>%
+  summarize_report(col = estimate, term, stat_name = "beta")
+
+coefs_fact_by_both <- tar_read(preplot_params_fact_by_both, store = target_store) %>%
   summarize_report(col = estimate, term, stat_name = "beta")
@@
 ```{r}
+preplot_fixef_fact_by_both <- tar_read(preplot_fixef_fact_by_both, store = target_store)
+
+preplot_fixef_fact_by_both %>% 
+  mutate(across(c(j_score, resp_pic, resp_source), \(x) if_else(x > 0, "high", "low")),
+         resp_pic = paste0("pic.", resp_pic),
+         resp_source = paste0("source.", resp_source)) %>% 
+  pivot_wider(names_from = c(resp_pic, resp_source),
+              values_from = acc_pred) %>% 
+  mutate(superdiff = (pic.high_source.high - pic.low_source.high) - (pic.high_source.low - pic.low_source.low)) %>% 
+  select(-starts_with("pic.")) %>% 
+  group_by(j_score) %>% 
+  summarize(avg = mean(superdiff, na.rm = T),
+            q025 = quantile(superdiff, .025, na.rm = T),
+            q500 = median(superdiff, na.rm = T),
+            q975 = quantile(superdiff, .975, na.rm = T))
+```
+
+```{r}
 plot_coefs_fact_by_both <- tar_read(plot_coefs_fact_by_both, store = target_store)

### 2023-07-30 R/preproc/clean_retrieval.R
stop grouping retrieval! it makes warnings later

@@ -162,7 +162,8 @@ bind_retrieval <- function (fact_data_scored, pic_data_clean, source_data_clean,
                                             TRUE ~ NA_character_),
            encoding_trial_num = if_else(group == "academic",
                                         group_trial_num * 2 - 1,
-                                        group_trial_num * 2))
+                                        group_trial_num * 2)) %>% 
+    ungroup()
   
   return (out)
 }

### 2023-07-30 R/analyze/make_models.R
add already knew model

@@ -65,7 +65,7 @@ make_retrieval_recipe <- function (retrieval_data_prepped) {
   return (out)
 }
 
-make_encoding_recipe <- function (retrieval_data_prepped) {
+make_interest_recipe <- function (retrieval_data_prepped) {
   out <- recipe(retrieval_data_prepped) %>% 
     step_filter(already_knew == "none") %>% 
     update_role(interest, new_role = "outcome") %>% 
@@ -88,9 +88,26 @@ make_encoding_recipe <- function (retrieval_data_prepped) {
     # to get it to -0.5 and +0.5
     # have to use step_range because ordinalscore requires int output
     step_range(encoding_trial_num, min = -0.5, max = 0.5) %>% 
-    # re-centering but NOT scaling because I want it to predict in single interest points
-    step_range(interest, min = -50, max = 50) %>% 
+    # re-centering but and scaling because it might behave better at smaller range
+    step_range(interest, min = -5, max = 5) %>% 
     # scaling these to range of 10 makes it so unit change is 10% of the full range
+    # the actual lowest j_score is .26 so this gets it to the same range where a score of 0 would range down to -7
+    step_range(j_score, min = -4.4, max = 3) %>%  # %>% 
+    step_rename(from_encoding_late = encoding_trial_num)
+  
+  return (out)
+}
+
+make_alreadyknew_recipe <- function (retrieval_data_prepped) {
+  out <- recipe(retrieval_data_prepped) %>% 
+    update_role(already_knew, new_role = "outcome") %>% 
+    update_role(c(j_score, subj_num), new_role = "predictor") %>% 
+    # so I don't have to put already_knew into the preplot new data
+    update_role_requirements(role = "NA", bake = FALSE) %>% 
+    # to specifically combine "all" into "some"
+    # bc step_other collapses by number, not specific levels
+    step_mutate(already_knew = fct_recode(already_knew, "some" = "all")) %>% 
+    # scaling to range of 10 makes it so unit change is 10% of the full range
     # the actual lowest j_score is .26 so this gets it to the same range where a score of 0 would range down to -7
     step_range(j_score, min = -4.4, max = 3) %>%  # %>% 
     step_rename(from_encoding_late = encoding_trial_num)
@@ -135,7 +152,7 @@ fit_encoding_model <- function (in_data, in_formula) {
[…]

### 2023-07-30 R/analyze/make_plots_ms.R
update theme_ms, some plot cleanup

@@ -9,6 +9,20 @@ integer_breaks <- function(n = 5, ...) {
   return(fxn)
 }
 
+## theme elements ----
+
+theme_ms <- function (base_size, base_family, ...) {
+  out <- theme_linedraw(base_size = base_size,
+                        base_family = base_family) +
+    theme(legend.background = element_blank(),
+          plot.background = element_blank(),
+          ...)
+  
+  return (out)
+}
+
+## functions ----
+
 make_plot_demos <- function (demo_data) {
   demo_data %>% 
     mutate(gender = coalesce(gender, "not reported")) %>% 
@@ -30,7 +44,7 @@ make_plot_expertise_hist <- function (expertise_score_data, annotation_font = "H
   
   expertise_score_data %>% 
     ggplot(aes(x = j_score)) +
-    geom_histogram(binwidth = .05, fill = "gray80") +
+    geom_histogram(alpha = 0.5, binwidth = .05, fill = "gray80") +
     geom_vline(xintercept = median_score, linetype = "dotted") +
     annotate("text",
              x = median_score - 0.02,
@@ -202,7 +216,7 @@ make_plot_fixef_fact_by_both <- function (preplot_fixef, retrieval_data) {
                   \(x) recode_factor(as.character(x),
                                      `-0.5` = "incorrect",
                                      `0.5` = "correct"))) %>% 
-    ggplot(aes(x = fct_rev(resp_pic), y = acc_pred, color = fct_rev(resp_source))) +
+    ggplot(aes(x = fct_rev(resp_pic), y = acc_pred, color = resp_source)) +
     geom_line(aes(group = interaction(subj_num, resp_source)),
               data = retrieval_summarized,
               alpha = 0.2) +
@@ -214,5 +228,5 @@ make_plot_fixef_fact_by_both <- function (preplot_fixef, retrieval_data) {
     guides(color = guide_legend(override.aes = list(alpha = 1, linewidth = 3))) +
     labs(x = "Forced-choice photo memory",
          y = "P(recall) for novel facts",
-         color = "Forced-choice museum memory")
+         color = "Forced-choice\nmuseum memory")
 }

### 2023-07-30 _targets.R

@@ -37,10 +37,9 @@ tar_source(c("R/preproc/",
 paths_raw_data <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T)
 
 # For the figure fonts
-library(showtext)
-# showtext_auto()
-# figure_font <- "Montserrat"
-# font_add_google(figure_font)
+font_ms <- "Helvetica Neue"
+fontsize_ms <- 10
+
 # source("other_functions.R") # Source other scripts as needed. # nolint
 
 ## targets for demographics and subject IDs ----
@@ -214,8 +213,12 @@ target_models <- list(
   ),
   tar_target(name = model_interest,
              command = fit_encoding_model(in_data = retrieval,
-                                           in_formula = interest ~ j_score + from_encoding_late + (1 | subj_num))
-             )
+                                          in_formula = interest ~ j_score + from_encoding_late + (1 | subj_num))
+  ),
+  tar_target(name = model_alreadyknew,
+             command = fit_alreadyknew_model(in_data = retrieval,
+                                          in_formula = already_knew ~ j_score + (1 | subj_num))
+  )
 )
 
 ## targets for post-model PRE-PLOT objects ----
@@ -231,6 +234,12 @@ target_preplots <- list(
   ),
   tar_target(name = preplot_params_source,
              command = posterior_preplot_params(model_source)
+  ),
+  tar_target(name = preplot_params_interest,
+             command = posterior_preplot_params(model_interest)
+  ),
+  tar_target(name = preplot_params_alreadyknew,
+             command = posterior_preplot_params(model_alreadyknew)
   ),
   # Importante: now that preprocessing is done with a recipe,
   # create the newdata ON THE SCALE OF THE ORIGINAL/REAL DATA
@@ -303,10 +312,13 @@ target_ms_figs <- list(
              command = {
                path <- here::here("ignore", "figs", "ms_fig3.png")
                figure <- plot_grid(plot_demos +
-                                     theme(legend.position = c(1, 1),
-                                           legend.justification = c(1, 1),
-                                           legend.background = element_blank()),
-                                   plot_expertise_hist,
+                                     theme_ms(base_size = fontsize_ms,
+                                              base_family = font_ms,
+                                              legend.position = c(1, 1),
+                                              legend.justification = c(1, 1)),
+                                   plot_expertise_hist +
+                                     theme_ms(base_size = fontsize_ms,
+                                              base_family = font_ms),
[…]

### 2023-07-30 writing/ms.Rmd
now outputs target-made figs and supplemental tables

--- 2023-03-05 writing/ms.Rmd
@@
 knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
+require(targets)
 require(tidyverse)
@@
 require(rlang)
-load(here::here("ignore", "data", "preplots.rda")) # For the model params
-load(here::here("ignore", "data", "plots_ms.rda"))
+# source(here::here("R", "get_cleaned_data.R"))
+# load(here::here("ignore", "data", "preplots.rda")) # For the model params
+# load(here::here("ignore", "data", "plots_ms.rda"))
 
+target_store <- here::here("ignore", "_targets")
 signif_digits <- 3L
@@
 ```{r setup-extra-stat-reports}
-summarize_report <- function (data, col, ..., stat_name = "", unit_name = "", digs = signif_digits) {
-  if (unit_name != "") unit_name %<>% paste0(" ", .)
-  glue_in = if_else(stat_name != "",
-                    "{stat_name} = {a}{unit_name}, 95% CI [{b}, {c}]",
-                    "{a}{unit_name}, 95% CI [{b}, {c}]")
-
-  col_chr = as_name(enexpr(col))
-  group_cols = enexprs(...)
-
-  data %<>%
-    select(iteration, !!!group_cols, starts_with(col_chr)) %>%
-    pivot_longer(cols = starts_with(col_chr),
-                 names_to = "metric_type",
-                 values_to = "value",
-                 names_prefix = glue::glue("{col_chr}_"))
-
-  if (!is.null(group_cols)) {
-    data %<>% group_by(!!!group_cols, metric_type)
-  } else {
-    data %<>% group_by(metric_type)
+summarize_kable <- function (data,
+                               col,
+                               digs = signif_digits,
+                               fn_list = list(mean = \(x) mean(x, na.rm = T),
+                                              sd = \(x) sd(x, na.rm = T))) {
+  data %>% 
+    summarize(across({{col}}, fn_list)) %>% 
+    mutate(across(where(is.numeric), \(x) signif(x, digits = digs))) %>% 
+    knitr::kable()
 }
-  data %<>%
-    summarize(avg = mean(value, na.rm = T),
-              q025 = quantile(value, .025, na.rm = T),
-              q975 = quantile(value, .975, na.rm = T)) %>% 
-    mutate(across(c("avg", "q025", "q975"),
-                  \(x) formatC(signif(x, digits = digs), digits = digs, format = "fg", flag = "#", mode = "double")),
-           txt_apa = pmap_chr(list(avg, q025, q975),
-                              \(a, b, c) {glue::glue(glue_in)}
-           ),
-           across(c("avg", "q025", "q975"), as.numeric))
-
-  return (data)
-}
-
-coefs_fact_by_pic <- preplot_params_fact_by_pic %>%
-  summarize_report(col = estimate, term, stat_name = "beta")
-
-coefs_fact_by_source <- preplot_params_fact_by_source %>%
-  summarize_report(col = estimate, term, stat_name = "beta")
 ```
@@
 ```{r}
-plot_demos
+q_google_demos <- tar_read(q_google_demos, store = target_store)
+j_exp <- tar_read(expertise_summarized, store = target_store)
+plot_demos <- tar_read(plot_demos, store = target_store) +
+  theme_ms +
+  theme(legend.position = c(1, 1),
+          legend.justification = c(1, 1)) 
+plot_expertise_hist <- tar_read(plot_expertise_hist, store = target_store) +
+  theme_ms
 ```
 
-```{r}
-plot_expertise_hist
+```{r figure-3}
+knitr::include_graphics(here::here("ignore", "figs", "ms_fig3.png"))
 ```
@@
 ```{r}
-plot_fact_by_expertise
+knitr::include_graphics(here::here("ignore", "figs", "ms_fig4.png"))
 ```
@@
 ```{r}
-plot_coefs_fact_by_pic
+knitr::include_graphics(here::here("ignore", "figs", "ms_fig5.png"))
+# Question from Chris at Alyssano CNS practice lab meeting March 10 2023: Were trivia experts more likely to report certain facts as novel? (like, ones that might be harder)
+```
+
+# Stats to copy and paste
+
+Or to inject if I can figure out a better way that preserves the Google-Docsery...
+
+## Demographics
+
+Number of participants: `r nrow(q_google_demos)`
+
+Participants breakdown by gender:
+
+```{r}
+q_google_demos %>% 
+  count(gender) %>% 
+  knitr::kable()
+```
+
+Participant summary by age:
+
+```{r}
+q_google_demos %>% 
+  summarize_kable(age)
+```
+
+## Task info
+
+Encoding trial duration:
+
+```{r}
+encoding <- tar_read(encoding, store = target_store)
+
+encoding %>%
+  # there is literally _one_ trial where the timing seems to have messed up and run over
+  filter(rt <= 35100) %>% 
+  mutate(rt = rt / 1000) %>% 
+  summarize_kable(rt)
+```
+
+Expertise score:
+
+```{r}
+j_exp %>% 
+  # to get it in units of questions
+  mutate(j_score = j_score * 50) %>% 
+  summarize_kable(j_score,
+                  fn_list = list(min = \(x) min(x, na.rm = T),
+                                 max = \(x) max(x, na.rm = T),
+                                 median = \(x) median(x, na.rm = T)))
+```
+
+Number of novel facts at encoding:
+
+```{r}
+encoding %>% 
+  filter(already_knew == "none") %>% 
+  count(subj_num) %>% 
+  summarize_kable(n,
+                  digs = 2L,
+                  fn_list = list(min = \(x) min(x, na.rm = T),
+                                 mean = \(x) mean(x, na.rm = T),
+                                 sd = \(x) sd(x, na.rm = T)))
+```
+
+## Major results
+
+### Encoding
+
+Beta median/CIs from the model with **interest** as the outcome variable.
+
+Note: For this model, effective N failed to reach 10% of the sampling iterations for several parameters, even after increasing the number of sampling iterations to 3000 iterations/chain.
+However, no other associated model reliability parameters (like Rhat) suggested concern.
+We thus report these model outcomes as is.
+We expect that some of the apparently low N~eff~ may arise from individual participants having different distributions of interst ratings across their facts.
+
+```{r}
+fn_list_model.coefs <- list(q025 = \(x) quantile(x, .025),
+                            q500 = \(x) median(x, na.rm = T),
+                            q975 = \(x) quantile(x, .975))
+
+tar_read(preplot_params_interest, store = target_store) %>%
+  group_by(term) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+Beta median/CIs from the model with **prior knowledge** as the outcome variable. Should be encoded with none as 0 and some/all as 1.
+
+```{r}
+tar_read(preplot_params_alreadyknew, store = target_store) %>%
+  group_by(term) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+### Retrieval
+
+#### Beta medians & CIs
+
+Beta median/CIs from the model with **photo memory** as the outcome variable
+
+```{r}
+tar_read(preplot_params_pic, store = target_store) %>%
+  group_by(term) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+Beta median/CIs from the model with **museum memory** as the outcome variable
+
+```{r}
+tar_read(preplot_params_source, store = target_store) %>%
+  group_by(term) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+Beta medians/CIs from the **omnibus model**
+
+```{r}
+preplot_params_fact_by_both <- tar_read(preplot_params_fact_by_both, store = target_store)
+
+preplot_params_fact_by_both %>%
+  group_by(term) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+#### Omnibus model simple effects
+
+"low" trivia expertise for the preplots is j_score = -2, while "high" trivia expertise is +1
+
+```{r}
+preplot_params_fact_by_both %>% 
+  filter(term %in% c("resp_pic:resp_source", "resp_pic:resp_source:j_score")) %>% 
+  mutate(term = str_replace_all(term, ":", ".")) %>% 
+  pivot_wider(names_from = term,
+              values_from = estimate) %>% 
+  mutate(low = resp_pic.resp_source - 2*resp_pic.resp_source.j_score,
+         high = resp_pic.resp_source + resp_pic.resp_source.j_score) %>% 
+  select(iteration, low, high) %>% 
+  pivot_longer(cols = c(low, high),
+               names_to = "j_score",
+               values_to = "estimate") %>% 
+  group_by(j_score) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
 ```
@@
 ```{r}
-plot_fixef_fact_by_pic
+preplot_fixef_fact_by_both %>% 
+  group_by(j_score, resp_pic, resp_source) %>% 
+  summarize_kable(acc_pred,
+                  fn_list = list(median = median))
 ```
-
-Interaction coefficient: `r coefs_fact_by_pic %>% filter(term == "resp_pic:j_score") %>% pull(txt_apa)`
-
-```{r}
-plot_pic_by_expertise
-```
-
-## Figure 6
-
-```{r}
-plot_coefs_fact_by_source
-```
-
-```{r}
-plot_fixef_fact_by_source
-```
-
-Interaction coefficient: `r coefs_fact_by_source %>% filter(term == "resp_source:j_score") %>% pull(txt_apa)`
-
-```{r}
-plot_source_by_expertise
-```
-
-<!--
-# OLD STUFF I FOUND IN HERE: Intro
-
-Derpy abstract for myself:
-
-Individual behavioral differences in human memory pay testament to the complexity of our memory systems.
-Studying people performing at extremes of the memory spectrum can help us learn more about memory systems as they might function in the typical individual.
-However, memory, especially superior memory, is not a single construct.
-People may exhibit markedly strong memory in a variety of ways, each of which might rely on a different feature of the memory system.
-Nearly all research on people with superior memory has focused on superior memorizers, or individuals with the ability, through some combination of untrained and trained strategy, to quickly encode large amounts of information, typically otherwise meaningless, and retrieve it with high accuracy.
-
-Not all feats of impressive memory involve encoding large bodies of information at once, whether incidental or intentional.
-Other feats of memory are (or appear) more retrieval-based.
-Trivia games are one popular example, where competitors attempt to retrieve the most general knowledge, often as quickly as possible.
-Trivia experts are able to rapidly retrieve a broad range of facts, often having first encoded these facts years in the past.
-Notably, they often do this without apparent use of any memorization strategy [CITE].
-Given two people with approximately equivalent life experience, and exposure to general knowledge through schooling, what leads one person to be more successful in retaining and/or retrieving facts in a cued recall situation?
-
-Basic outline:
-
-- Episodic and semantic memory: separate? intertwined?
-    - MTL amnesics perform worse than controls on semantic fluency tasks (name exemplars of X category) that can be solved with an autobiographical episodic strategy [e.g.
-@Greenberg:2009fq; @Sheldon:2012ju]
-    - To the degree that a task is not "process-pure," we are likely to observe interdependencies between semantic and episodic memory if both might be individually contributing to task performance.
-But what about semantic memory tasks that do not have obvious episodic strategies, typically those that are speeded enough to preclude episodic elaboration?
-        - Participants making famous/nonfamous judgments of names, and reading names out loud, are faster to judge/read famous names with greater autobiographical significance, such that those names are more likely to be associated with autobiographical memories [@Westmacott:2003ee]
-        - Participants make lexical decisions about studied words faster for words they will later "remember" vs "know" [@Sheldon:2010cd].
-The authors suggest this provides evidence for ecphory or some other fast episodic retrieval component
-        - Ecphoric signals may be detected _early_ during old/new recognition trials [@Waldhauser:2016fx]
-        - Can this putative ecphory also support complex semantic retrieval, like answering general knowledge questions?
-- What can studying trivia experts tell us about overlap between episodic and semantic memory?
-    - individual differences in ecphoric strength at retrieval could contribute to 
-    - detect differing contributions of encoding- and retrieval-stage processes to overall retrieval success
-    - 
-- What can studying trivia experts tell us that studying other special populations doesn't?
-    - Relative to **amnesic patients:** patient work allows us to make critical claims about necessary and sufficient contributions of different structures/systems to memory tasks.
-However, these conclusions might not apply at the other end of the spectrum.
-Said otherwise, the contribution of "pure" episodic vs semantic components to task performance might not vary linearly with episodic and semantic memory ability all the way along the spectrum from impaired to exceptional.
-    - Relative to folks with **highly superior autobiographical memory:** Most people with HSAM who have been documented in case and group studies fail to show superior memory for historical events that happened before they were born.
-General knowledge expertise seems epiphenomenal to superior memory for current events as a subset of autobiographical memory [@McGaugh:2014jh]
-    - Relative to **memory champions:** modern memory champions deploy deliberate mnemonic strategies to encode huge amounts of information in a single sitting.
-General knowledge generally is acquired bit by bit and then tested at once, as opposed to having to encode at once and retrieve at once.
-Memory champions SEEM (cite?
-hard to find when people test this stuff) not to show above average general knowledge
-
-- What research has been done on superior memory?
-    - Superior memorizers
-    - (MAYBE SCRATCH) savants?
-    - Highly superior autobiographical memory
-- What can studying trivia experts tell us that studying other superior memory groups doesn't?
-    - Trivia expertise might be more likely to derive from innate memory differences than superior memorization, which tends to rely on becoming facile with a strategy
-    - Trivia facts, as must anything else, must be encoded through episodic mechanisms, but once encoded, are considered squarely within the domain of semantic memory.
-Studying trivia memory can tell us a lot about the putative boundary between episodic and semantic memory
-    - [@Brandt:2017cd]
-- What research has been done on general knowledge capacity as its own memory construct?
-- Thus, the current study
--->

### 2023-07-30 writing/supplement.Rmd
remove figs actually, rename file

--- 2023-07-30 writing/ms.Rmd
@@
 ---
-title: "J-Study manuscript"
-author: "Monica Thieu"
+title: "J-Study supplement"
+author: "Monica Thieu, Lauren Wilkins, & Mariam Aly"
 date: "Updated `r Sys.Date()`"
@@
 require(rlang)
-# source(here::here("R", "get_cleaned_data.R"))
-# load(here::here("ignore", "data", "preplots.rda")) # For the model params
-# load(here::here("ignore", "data", "plots_ms.rda"))
 
@@
 signif_digits <- 3L
-```
 
-```{r setup-extra-stat-reports}
 summarize_kable <- function (data,
@@
 
-# Figures and captions
-
-## Figure 3
-
-```{r}
-q_google_demos <- tar_read(q_google_demos, store = target_store)
-j_exp <- tar_read(expertise_summarized, store = target_store)
-plot_demos <- tar_read(plot_demos, store = target_store) +
-  theme_ms +
-  theme(legend.position = c(1, 1),
-          legend.justification = c(1, 1)) 
-plot_expertise_hist <- tar_read(plot_expertise_hist, store = target_store) +
-  theme_ms
-```
-
-```{r figure-3}
-knitr::include_graphics(here::here("ignore", "figs", "ms_fig3.png"))
-```
-
-## Figure 4
-
-```{r}
-knitr::include_graphics(here::here("ignore", "figs", "ms_fig4.png"))
-```
-
-## Figure 5
-
-```{r}
-knitr::include_graphics(here::here("ignore", "figs", "ms_fig5.png"))
-# Question from Chris at Alyssano CNS practice lab meeting March 10 2023: Were trivia experts more likely to report certain facts as novel? (like, ones that might be harder)
-```
-
 # Stats to copy and paste
@@
 ## Demographics
+
+```{r}
+q_google_demos <- tar_read(q_google_demos, store = target_store)
+```
 
@@
 ```{r}
+j_exp <- tar_read(expertise_summarized, store = target_store)
+
 j_exp %>% 
@@
 ```{r}
-preplot_fixef_fact_by_both %>% 
+tar_read(preplot_fixef_fact_by_both, store = target_store) %>% 
   group_by(j_score, resp_pic, resp_source) %>% 

### 2023-08-01 R/prep_task/parse_master_spreadsheet.R
rename file, make targets compatible

@@ -1,33 +1,11 @@
-## setup ----
-
-require(tidyverse)
-require(googledrive)
-require(magrittr)
-
-# Should download master spreadsheet to local copy for R manipulation
-# Trust me, the ID is correct
-# Checked it using drive_get("~/jstudy/master_spreadsheet")
-# But that takes a little bit to run so I hard coded it here
-
 ## parse master spreadsheet ----
 
-refresh_master_spreadsheet_raw <- function () {
-  drive_download(file = as_id("1degtvNziMvUM3V7wBX6VPkYyuUsEKOezWb8VZ933Irw"),
-                 path = here::here("stim_stuff", "master_spreadsheet.csv"),
-                 type = "csv",
-                 overwrite = TRUE)
-  return (read_csv(here::here("stim_stuff", "master_spreadsheet.csv")))
-}
-
-parse_master_spreadsheet <- function () {
+parse_master_spreadsheet <- function (master_spreadsheet_path, duration_data) {
   
-  master_spreadsheet_raw <- read_csv(here::here("stim_stuff", "master_spreadsheet.csv"))
-  
-  durations <- read_csv(here::here("ignore", "narration", "durations_parsed.csv"))
-  
-  out <- master_spreadsheet_raw %>% 
+  out <- master_spreadsheet_path %>%
+    read_csv() %>% 
     select(-ends_with("pretest")) %>% 
-    left_join(durations, by = "trial_num") %>% 
+    left_join(duration_data, by = "trial_num") %>% 
     pivot_longer(cols = -c(trial_num:display),
                  names_to = c("category", ".value"),
                  names_sep = 5L) %>% 
@@ -86,6 +64,6 @@ parse_master_spreadsheet <- function () {
                                 test_answer),
                 names_glue = "{.value}.{category_label_academic}_{category_label_nonacademic}")
   
-  write_csv(out, here::here("stim_stuff", "master_spreadsheet_parsed.csv"))
+  # write_csv(out, here::here("stim_stuff", "master_spreadsheet_parsed.csv"))
   return (out)
 }

### 2023-08-01 R/prep_task/make_spreadsheet_encoding.R
targets compatible stimlists yay

@@ -1,46 +1,47 @@
-## setup ----
-
-require(tidyverse)
-require(magrittr)
-
-master_spreadsheet <- read_csv(here::here("stim_stuff", "master_spreadsheet_parsed.csv"))
-
 ## format spreadsheet ----
 
-encoding <- master_spreadsheet %>% 
-  # NOT INCLUDING RANDOMISE_BLOCKS RIGHT NOW
-  # retrieval facts requires knowing which blocks appeared in which order
-  # using randomise_blocks appears not to allow easy feeding of block order
-  # into the next task
-  # so right now, encoding order is fixed for everybody
-  # bind on the start/finish display rows LATER
-  # when encoding is split into 2 before writing into 1st/2nd half CSVs
-  select(encoding_trial_num,
-         group,
-         trial_num,
-         starts_with("encoding_sentence"),
-         starts_with("mp3"),
-         starts_with("pic_a"),
-         starts_with("pic_b"),
-         starts_with("mp3"),
-         starts_with("wait_duration")) %>% 
-  arrange(encoding_trial_num)
-
-
-## write out ----
-
-encoding %>% 
-  slice(1:40) %>% 
-  mutate(display = "memorise_firsthalf") %>% 
-  bind_rows(tibble(display = "instructions_firsthalf"),
-            .,
-            tibble(display = "finish_firsthalf")) %>% 
-  write_csv(here::here("stim_stuff", "stimlist_encoding_firsthalf.csv"), na = "")
-
-encoding %>% 
-  slice(41:80) %>% 
-  mutate(display = "memorise_secondhalf") %>% 
-  bind_rows(tibble(display = "instructions_secondhalf"),
-            .,
-            tibble(display = "finish_secondhalf")) %>% 
-  write_csv(here::here("stim_stuff", "stimlist_encoding_secondhalf.csv"), na = "")
+make_spreadsheet_encoding <- function (master_spreadsheet_data, stimlist_folder) {
+  encoding <- master_spreadsheet_data %>% 
+    # NOT INCLUDING RANDOMISE_BLOCKS RIGHT NOW
+    # retrieval facts requires knowing which blocks appeared in which order
+    # using randomise_blocks appears not to allow easy feeding of block order
+    # into the next task
+    # so right now, encoding order is fixed for everybody
+    # bind on the start/finish display rows LATER
+    # when encoding is split into 2 before writing into 1st/2nd half CSVs
+    select(encoding_trial_num,
[…]

### 2023-08-01 R/prep_task/make_spreadsheet_pretest.R

@@ -1,87 +1,85 @@
-## setup ----
-
-require(tidyverse)
-require(magrittr)
-
-master_spreadsheet_raw <- read_csv(here::here("stim_stuff", "master_spreadsheet.csv"))
-
 ## format spreadsheet ----
 
-pretest <- master_spreadsheet_raw %>%
-  select(trial_num, ends_with("pic_a"), ends_with("pic_b"), ends_with("pretest")) %>%
-  pivot_longer(cols = -trial_num,
-               names_to = c("category", ".value"),
-               names_sep = 5L) %>%
-  filter(pretest) %>%
-  select(-pretest) %>% 
-  arrange(category, trial_num) %>% 
-  mutate(category = str_sub(category, end = -2L),
-         # manually label all the object names depicted in each pic
-         # because the test answer is not always the name of the object depicted
-         object_name = case_when(
-           category == "arms" & trial_num == 15 ~ "wonna",
-           category == "arms" & trial_num == 19 ~ "bagh nakh",
-           category == "arms" & trial_num == 25 ~ "shamshir",
-           category == "arms" & trial_num == 32 ~ "hauberk",
-           category == "arms" & trial_num == 36 ~ "besagew",
-           category == "cars" & trial_num == 12 ~ "flywheel",
-           category == "cars" & trial_num == 13 ~ "torque converter",
-           category == "cars" & trial_num == 16 ~ "catalytic converter",
-           category == "cars" & trial_num == 23 ~ "differential",
-           category == "cars" & trial_num == 33 ~ "drum brake",
-           category == "cook" & trial_num == 2 ~ "blewit",
-           category == "cook" & trial_num == 3 ~ "ramp",
-           category == "cook" & trial_num == 10 ~ "escabeche",
-           category == "cook" & trial_num == 11 ~ "galantine",
-           category == "cook" & trial_num == 13 ~ "involtino",
-           category == "dino" & trial_num == 15 ~ "Megalosaurus",
-           category == "dino" & trial_num == 23 ~ "Cetiosaurus",
-           category == "dino" & trial_num == 25 ~ "Citipati",
-           category == "dino" & trial_num == 33 ~ "Aepyornis",
-           category == "dino" & trial_num == 35 ~ "Shonisaurus",
-           category == "gems" & trial_num == 11 ~ "pegmatite",
-           category == "gems" & trial_num == 13 ~ "botryoidal crystal",
[…]

### 2023-08-01 R/prep_task/make_spreadsheet_retrieval_facts.R

@@ -1,100 +1,100 @@
-## setup ----
-
-require(tidyverse)
-require(magrittr)
-
-master_spreadsheet <- read_csv(here::here("stim_stuff", "master_spreadsheet_parsed.csv"))
-
 ## format spreadsheet ----
 
-retrieval_facts_order <- list(
-  # 1-4: same episodic same semantic
-  tibble(randomise_blocks = 1L,
-         block_trial_num = 1:5,
-         group = rep("academic", 5),
-         encoding_block = rep("early", 5)),
-  tibble(randomise_blocks = 2L,
-         block_trial_num = 1:5,
-         group = rep("nonacademic", 5),
-         encoding_block = rep("early", 5)),
-  tibble(randomise_blocks = 3L,
-         block_trial_num = 1:5,
-         group = rep("academic", 5),
-         encoding_block = rep("late", 5)),
-  tibble(randomise_blocks = 4L,
-         block_trial_num = 1:5,
-         group = rep("nonacademic", 5),
-         encoding_block = rep("late", 5)),
-  # 5-8: same episodic different semantic
-  tibble(randomise_blocks = rep(5:6, each = 5),
-         block_trial_num = rep(1:5, 2),
-         group = rep(c("academic", "nonacademic"), 5),
-         encoding_block = rep("early", 10)),
-  tibble(randomise_blocks = rep(7:8, each = 5),
-         block_trial_num = rep(1:5, 2),
-         group = rep(c("academic", "nonacademic"), 5),
-         encoding_block = rep("late", 10)),
-  # 9-12: different episodic same semantic
-  tibble(randomise_blocks = rep(9:10, each = 5),
-         block_trial_num = rep(1:5, 2),
-         group = rep("academic", 10),
-         encoding_block = rep(c("early", "late"), 5)),
-  tibble(randomise_blocks = rep(11:12, each = 5),
-         block_trial_num = rep(1:5, 2),
-         group = rep("nonacademic", 10),
-         encoding_block = rep(c("early", "late"), 5)),
-  # 12-16: different episodic different semantic
-  tibble(randomise_blocks = rep(13:14, each = 5),
-         block_trial_num = rep(1:5, 2),
-         group = rep(c("academic", "nonacademic"), 5),
-         encoding_block = rep(c("early", "late"), 5)),
-  tibble(randomise_blocks = rep(15:16, each = 5),
-         block_trial_num = rep(1:5, 2),
[…]

### 2023-08-01 R/prep_task/make_spreadsheet_retrieval_pics.R

@@ -1,29 +1,27 @@
-## setup ----
-
-require(tidyverse)
-require(magrittr)
-
-master_spreadsheet <- read_csv(here::here("stim_stuff", "master_spreadsheet_parsed.csv"))
-
 ## format spreadsheet ----
 
-retrieval_pics <- master_spreadsheet %>%
-  select(trial_num,
-         group,
-         starts_with("pic_c"),
-         starts_with("pic_d")) %>% 
-  mutate(randomise_trials = 1L,
-         display = "test") %>% 
-  select(trial_num,
-         display,
-         randomise_trials,
-         everything()) %>% 
-  bind_rows(tibble(display = "instructions"),
-            .,
-            tibble(display = "finish"))
-
-
-## write out ----
-
-write_csv(retrieval_pics,
-          here::here("stim_stuff", "stimlist_retrieval_pics.csv"), na = "")
+make_spreadsheet_retrieval_pics <- function (master_spreadsheet_data, stimlist_folder) {
+  
+  retrieval_pics <- master_spreadsheet_data %>%
+    select(trial_num,
+           group,
+           starts_with("pic_c"),
+           starts_with("pic_d")) %>% 
+    mutate(randomise_trials = 1L,
+           display = "test") %>% 
+    select(trial_num,
+           display,
+           randomise_trials,
+           everything()) %>% 
+    bind_rows(tibble(display = "instructions"),
+              .,
+              tibble(display = "finish"))
+  
+  # write out
+  out_path <- here::here(stimlist_folder, "stimlist_retrieval_pics.csv")
+  write_csv(retrieval_pics,
+            out_path, na = "")
+  
+  # returns path to file bc targets-compatible
+  return (out_path)
+}

### 2023-08-01 R/prep_task/make_spreadsheet_retrieval_source.R

@@ -1,28 +1,27 @@
-## setup ----
-
-require(tidyverse)
-require(magrittr)
-
-master_spreadsheet <- read_csv(here::here("stim_stuff", "master_spreadsheet_parsed.csv"))
-
 ## format spreadsheet ----
 
-retrieval_source <- master_spreadsheet %>% 
-  select(encoding_trial_num,
-         group,
-         trial_num,
-         starts_with("encoding_sentence")) %>% 
-  arrange(encoding_trial_num) %>% 
-  mutate(encoding_block = if_else(encoding_trial_num <= 40, "early", "late"),
-         display = "test",
-         # DO randomise trials completely for the source test
-         randomise_trials = 1) %>% 
-  select(randomise_trials, display, encoding_block, group, trial_num, everything()) %>% 
-  bind_rows(tibble(display = "instructions"),
-            .,
-            tibble(display = "finish"))
-
-## write out ----
-
-write_csv(retrieval_source,
-          here::here("stim_stuff", "stimlist_retrieval_source.csv"), na = "")
+make_spreadsheet_retrieval_source <- function (master_spreadsheet_data, stimlist_folder) {
+  
+  retrieval_source <- master_spreadsheet_data %>% 
+    select(encoding_trial_num,
+           group,
+           trial_num,
+           starts_with("encoding_sentence")) %>% 
+    arrange(encoding_trial_num) %>% 
+    mutate(encoding_block = if_else(encoding_trial_num <= 40, "early", "late"),
+           display = "test",
+           # DO randomise trials completely for the source test
+           randomise_trials = 1) %>% 
+    select(randomise_trials, display, encoding_block, group, trial_num, everything()) %>% 
+    bind_rows(tibble(display = "instructions"),
+              .,
+              tibble(display = "finish"))
+  
+  # write out
+  out_path <- here::here(stimlist_folder, "stimlist_retrieval_source.csv")
+  write_csv(retrieval_source,
+            out_path, na = "")
+  
+  # returns path to file bc targets-compatible
+  return (out_path)
+}

### 2023-08-01 R/prep_task/parse_narr_durations.R

@@ -1,23 +1,25 @@
-require(tidyverse)
-require(magrittr)
-
-durations <- read_delim(here::here("ignore", "narration", "durations.txt"),
-                        delim = "=", col_names = c("key", "value")) %>%
-  mutate(across(everything(), str_trim, side = "both"),
-         id = rep(1:(n()/2), each = 2)) %>%
-  pivot_wider(names_from = key, values_from = value) %>%
-  rename(mp3_duration = kMDItemDurationSeconds,
-         mp3 = kMDItemFSName) %>%
-  mutate(mp3_duration = as.numeric(mp3_duration),
-         wait_duration = pmin(25, mp3_duration),
-         category = str_sub(mp3, end = 4L),
-         trial_num = as.integer(str_sub(mp3, start = 5L, end = -6L)),
-         counterbalance = str_sub(mp3, start = -5L, end = -5L)) %>%
-  select(-id, -mp3_duration) %>%
-  # Get it wide by category and counterbalance to fit the master_spreadsheet format
-  pivot_wider(id_cols = trial_num, names_from = c(category, counterbalance),
-              values_from = c(mp3, ends_with("duration")),
-              names_glue = "{category}_{.value}_{counterbalance}") %>% 
-  arrange(trial_num)
-
-write_csv(durations, file = here::here("ignore", "narration", "durations_parsed.csv"))
+parse_narr_durations <- function (durations_raw_path) {
+  out <- read_delim(durations_raw_path,
+                    delim = "=",
+                    col_names = c("key", "value")) %>%
+    mutate(across(everything(), \(x) str_trim(x, side = "both")),
+           id = rep(1:(n()/2), each = 2)) %>%
+    pivot_wider(names_from = key, values_from = value) %>%
+    rename(mp3_duration = kMDItemDurationSeconds,
+           mp3 = kMDItemFSName) %>%
+    mutate(mp3_duration = as.numeric(mp3_duration),
+           wait_duration = pmin(25, mp3_duration),
+           # because after updating some pkgs it's reading in ghost quotation marks?
+           mp3 = str_sub(mp3, start = 2L, end = -2L),
+           category = str_sub(mp3, end = 4L),
+           trial_num = as.integer(str_sub(mp3, start = 5L, end = -6L)),
+           counterbalance = str_sub(mp3, start = -5L, end = -5L)) %>%
+    select(-id, -mp3_duration) %>%
+    # Get it wide by category and counterbalance to fit the master_spreadsheet format
[…]

### 2023-08-01 _targets.R

@@ -31,7 +31,8 @@ options(# clustermq.scheduler = "multicore",
 # Install packages {{future}}, {{future.callr}}, and {{future.batchtools}} to allow use_targets() to configure tar_make_future() options.
 
 # Run the R scripts in the R/ folder with your custom functions:
-tar_source(c("R/preproc/",
+tar_source(c("R/prep_task/",
+             "R/preproc/",
              "R/analyze/"))
 
 paths_raw_data <- list.files(here::here("ignore", "data", "raw", "real"), recursive = T, full.names = T)
@@ -41,6 +42,70 @@ font_ms <- "Helvetica Neue"
 fontsize_ms <- 10
 
 # source("other_functions.R") # Source other scripts as needed. # nolint
+
+## targets for RAW DATA from GOOGLE DRIVE (only works for authors) ----
+
+target_gdrive <- list(
+  tar_target(name = master_spreadsheet_raw,
+             command = get_googledrive_csv(drive_id = "1degtvNziMvUM3V7wBX6VPkYyuUsEKOezWb8VZ933Irw",
+                                   destination_path = here::here("stimlists", "master_spreadsheet.csv")),
+             format = "file"),
+  tar_target(name = q_google_demos_raw,
+             command = get_googledrive_csv(drive_id = "1yW13tK4dVr8MXtJTaZxV_3M8IaD5TqhbzD8QKPuEndM",
+                                           destination_path = here::here("ignore", "data", "raw", "real", "demographics.csv")),
+             format = "file"),
+  tar_target(name = expertise_questions_raw,
+             command = get_googledrive_csv(drive_id = "1e7R4CSDjSA5trC820aiwUbe7szjn7DTfMiZPI4my8Rk",
+                                           destination_path = here::here("stimlists", "jeopardy_spreadsheet.csv")),
+             format = "file")
+)
+
+## targets for COPIES OF RAW DATA (works for everyone else) ----
+
+target_from.gdrive <- list(
+  tar_target(name = master_spreadsheet_raw,
+             command = here::here("stimlists", "master_spreadsheet.csv"),
+             format = "file"),
+  tar_target(narration_durations_raw,
+             command = here::here("ignore", "narration", "durations.txt"),
+             format = "file"),
+  tar_target(name = q_google_demos_raw,
+             command = here::here("ignore", "data", "raw", "real", "demographics.csv"),
+             format = "file"),
+  tar_target(name = expertise_questions_raw,
[…]

### 2023-08-01 R/analyze/make_models.R
interest model back to 100 pt range

@@ -89,7 +89,7 @@ make_interest_recipe <- function (retrieval_data_prepped) {
     # have to use step_range because ordinalscore requires int output
     step_range(encoding_trial_num, min = -0.5, max = 0.5) %>% 
     # re-centering but and scaling because it might behave better at smaller range
-    step_range(interest, min = -5, max = 5) %>% 
+    step_range(interest, min = -50, max = 50) %>% 
     # scaling these to range of 10 makes it so unit change is 10% of the full range
     # the actual lowest j_score is .26 so this gets it to the same range where a score of 0 would range down to -7
     step_range(j_score, min = -4.4, max = 3) %>%  # %>% 

### 2023-08-01 writing/supplement.Rmd
update supplement with mariam edits and anonymous

@@
 ---
-title: "J-Study supplement"
-author: "Monica Thieu, Lauren Wilkins, & Mariam Aly"
+title: "Supplementary material"
+subtitle: "Main paper: Episodic memory bolsters acquisition of new semantic knowledge in trivia experts"
+author: "MT, LW, & MA"
 date: "Updated `r Sys.Date()`"
-output: html_document
+output:
+  pdf_document:
+    toc: true
+  html_document: default
 ---
@@
 }
+
+fn_list_model.coefs <- list(ci_95_lower = \(x) quantile(x, .025),
+                            median = \(x) median(x, na.rm = T),
+                            ci_95_upper = \(x) quantile(x, .975))
 ```
-
-# Stats to copy and paste
-
-Or to inject if I can figure out a better way that preserves the Google-Docsery...
 
@@
 
-```{r}
+```{r include=FALSE}
 q_google_demos <- tar_read(q_google_demos, store = target_store)
+j_exp <- tar_read(expertise_summarized, store = target_store)
+
+nrow(q_google_demos)
 ```
 
-Number of participants: `r nrow(q_google_demos)`
+### Figure 1: Trivia expertise as a function gender
 
-Participants breakdown by gender:
-
-```{r}
+```{r, include=FALSE}
+# These stats are in the paper!
 q_google_demos %>% 
@@
 
-Participant summary by age:
+```{r}
+q_google_demos %>% 
+  left_join(j_exp %>% mutate(subj_num = factor(subj_num))) %>% 
+  mutate(gender = coalesce(gender, "Not reported")) %>% 
+  ggplot(aes(x = j_score, fill = gender)) +
+  geom_histogram(position = "identity", alpha = 0.5) +
+  labs(x = "Trivia expertise score") +
+  theme_bw()
+```
+
+Men in our sample tended to score higher than women and genderqueer participants.
+LearnedLeague, the website from which we recruited, has more men than women participants, so we do not interpret these results any further.
+
+### Table 2: Participant breakdown by race
 
 ```{r}
+# These stats are in the paper!
+q_google_demos %>% 
+  # Anonymizing this one friend
+  mutate(race = if_else(race == "Asian, I want to be clear that I am Indian and not East Asian", "Asian", race)) %>% 
+  count(race) %>% 
+  arrange(desc(n)) %>% 
+  knitr::kable()
+```
+
+The vast majority of participants reported their race as White, with the largest minority of participants reporting their race as Asian/Pacific Islander.
+While LearnedLeague does not collect race information on members, we expect that this distribution is representative of website membership.
+We do not use race in any subsequent analyses because of the low race diversity in the sample.
+
+```{r, include=FALSE}
+# These stats are in the paper!
 q_google_demos %>% 
@@
 
-## Task info
+## Expertise pre-test
 
-Encoding trial duration:
+After completing the general knowledge pre-test, we asked participants to rate their meta-memory for each question.
+Ratings were based on Pereverseff and Bodner (2020)'s ratings.
+Participants were instructed as follows:
 
-```{r}
+- "Learning memory": When the answer came to mind, you also remembered a specific prior experience of learning this fact (e.g., how, when, and/or where you learned it).
+It does not have to be a memory of the first time you learned it.
+- "Related memory": When the answer came to mind, you also remembered a specific related personal memory, but the memory was not about learning this fact.
+- "Just know": When the answer came to mind, a specific personal memory did not come to mind. Instead, the answer just seems to be part of your general knowledge.
+- "Guess": You do not experience a specific personal memory or a general feeling of knowing the answer. It is an educated guess that you may have arrived at with some reasoning.
+- "Don't know": You have no idea what the answer could be, and you cannot even make a guess. You do not experience a specific personal memory or a general feeling of knowing the answer.
+
+After participants gave their metamemory ratings, we randomly selected one general knowledge fact endorsed by the participant for each of the five potential labels,
+and asked them to describe their metamemory state for that fact in words.
+We did not analyze any of the metamemory ratings because our validity checks indicated that participants did not use the ratings as instructed.
+Specifically, when we inspected participants’ descriptions, we found enough responses indicating “just know”-style metamemory for memories that participants had tagged with the “remember” responses (“learning memory” and “related memory”) that we considered the data to be unusable based on participants failing to follow task instructions.
+
+## Encoding task
+
+```{r include=FALSE}
+# These stats are in the paper!
 encoding <- tar_read(encoding, store = target_store)
@@
 
-Expertise score:
-
-```{r}
-j_exp <- tar_read(expertise_summarized, store = target_store)
-
+```{r include=FALSE}
+# These stats are in the paper!
 j_exp %>% 
@@
 
-Number of novel facts at encoding:
-
-```{r}
+```{r include=FALSE}
+# These stats are in the paper!
 encoding %>% 
@@
 
-## Major results
-
-### Encoding
-
-Beta median/CIs from the model with **interest** as the outcome variable.
-
-Note: For this model, effective N failed to reach 10% of the sampling iterations for several parameters, even after increasing the number of sampling iterations to 3000 iterations/chain.
-However, no other associated model reliability parameters (like Rhat) suggested concern.
-We thus report these model outcomes as is.
-We expect that some of the apparently low N~eff~ may arise from individual participants having different distributions of interst ratings across their facts.
-
-```{r}
-fn_list_model.coefs <- list(q025 = \(x) quantile(x, .025),
-                            q500 = \(x) median(x, na.rm = T),
-                            q975 = \(x) quantile(x, .975))
-
-tar_read(preplot_params_interest, store = target_store) %>%
-  group_by(term) %>% 
-  summarize_kable(estimate,
-                  fn_list = fn_list_model.coefs)
-```
-
-Beta median/CIs from the model with **prior knowledge** as the outcome variable. Should be encoded with none as 0 and some/all as 1.
+### Table 3: Model coefficients for encoding familiarity as a function of trivia expertise
 
@@
 
-### Retrieval
+This model was run as a Bayesian multilevel logistic regression (with the same model setting as the main model reported in the main text) predicting fact familiarity for each fact (unfamiliar = 0, familiar = 1) as a function of trivia expertise, with a random intercept for each participant.
+Participants rated their familiarity as "none", "some", or "all" for each encoding fact.
+For this analysis, we binned "some" and "all" together to compare the totally unfamiliar facts against facts for which participants reported _at least_ some familiarity.
 
-#### Beta medians & CIs
-
-Beta median/CIs from the model with **photo memory** as the outcome variable
+### Table 4: Model coefficients for encoding interest as a function of trivia expertise
 
 ```{r}
-tar_read(preplot_params_pic, store = target_store) %>%
+tar_read(preplot_params_interest, store = target_store) %>%
   group_by(term) %>% 
@@
 
-Beta median/CIs from the model with **museum memory** as the outcome variable
+This model was run as a Bayesian multilevel _linear_ regression (with the same model settings as the main model reported in the main text) predicting interest at encoding (on a 0-100 point scale, centered at 50 pts) as a function of trivia expertise, with a random intercept for each participant.
+We also included a covariate for first vs.
+second museum, coded the same way as it was for the model in the main text.
 
-```{r}
-tar_read(preplot_params_source, store = target_store) %>%
-  group_by(term) %>% 
-  summarize_kable(estimate,
-                  fn_list = fn_list_model.coefs)
-```
+For this model, effective N failed to reach 10% of the sampling iterations for several parameters, even after increasing the number of sampling iterations to 3000 iterations/chain.
+However, no other associated model reliability parameters (like Rhat) suggested concern.
+We thus report these model outcomes as is.
+We expect that some of the apparently low N~eff~ may arise from individual participants having different distributions of interest ratings across their facts.
 
-Beta medians/CIs from the **omnibus model**
+## Retrieval tasks
 
-```{r}
+```{r include=FALSE}
+# These stats are in the paper!
 preplot_params_fact_by_both <- tar_read(preplot_params_fact_by_both, store = target_store)
@@
 
-#### Omnibus model simple effects
-
-"low" trivia expertise for the preplots is j_score = -2, while "high" trivia expertise is +1
-
-```{r}
+```{r include=FALSE}
+# These stats are in the paper!
+# "low" trivia expertise for the preplots is j_score = -2
+# while "high" trivia expertise is +1
 preplot_params_fact_by_both %>% 
@@
 
-```{r}
+```{r include=FALSE}
+# These stats are in the paper!
 tar_read(preplot_fixef_fact_by_both, store = target_store) %>% 
@@
 ```
+
+### Table 5: Model coefficients for photo memory as a function of trivia expertise
+
+```{r}
+tar_read(preplot_params_pic, store = target_store) %>%
+  group_by(term) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+This model was run as a Bayesian multilevel logistic regression (with the same model settings as the main model reported in the main text) predicting binary photo recognition memory as a function of trivia expertise, with a random intercept for each participant.
+We also included covariates for interest at encoding and first vs.
+second museum, coded the same way as they were for the model in the main text.
+
+### Table 6: Model coefficients for museum memory as a function of trivia expertise
+
+```{r}
+tar_read(preplot_params_source, store = target_store) %>%
+  group_by(term) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+This model was run as a Bayesian multilevel logistic regression (with the same model settings as the main model reported in the main text) predicting binary museum recognition memory as a function of trivia expertise, with a random intercept for each participant.
+We also included covariates for interest at encoding and first vs.
+second museum, coded the same way as they were for the model in the main text.

### 2024-01-27 writing/supplement.Rmd
updates per pbr reviewers

@@
 require(tidyverse)
+require(cowplot)
 require(magrittr)
 require(rlang)
+source(here::here("R", "analyze", "make_plots_ms.R")) # for recode_params_pretty
 
@@
   data %>% 
-    summarize(across({{col}}, fn_list)) %>% 
+    summarize(across({{col}}, fn_list, .names = "{.fn}")) %>% 
     mutate(across(where(is.numeric), \(x) signif(x, digits = digs))) %>% 
@@
 
-fn_list_model.coefs <- list(ci_95_lower = \(x) quantile(x, .025),
-                            median = \(x) median(x, na.rm = T),
-                            ci_95_upper = \(x) quantile(x, .975))
+fn_list_model.coefs <- list(`95% CI lower bound` = \(x) quantile(x, .025),
+                            Median = \(x) median(x, na.rm = T),
+                            `95% CI upper bound` = \(x) quantile(x, .975))
+
+# Numerical stats mentioned in the main text are also tabulated in this document
+# They are in the chunks tagged with include=FALSE so that they don't appear in the supplement
+# Those chunks are only intended to be run interactively, and then (sigh)
+# the outputs are to be copied and pasted into the main text... it was the easiest overall
 ```
@@
 ```{r include=FALSE}
+# Numbers for the main text
 q_google_demos <- tar_read(q_google_demos, store = target_store)
@@
 
-### Figure 1: Trivia expertise as a function gender
+### Figure 1: Participant demographics
+
+```{r}
+knitr::include_graphics(here::here("ignore", "figs", "ms_fig3.png"))
+```
+
+Participant demographics.
+**(A)** 132 total participants aged 18 and up enrolled in the study (M~age~ = `r signif(mean(q_google_demos$age, na.rm = TRUE), digits = 3)` yrs, SD~age~ = `r signif(sd(q_google_demos$age, na.rm = TRUE), digits = 3)` yrs).
+Histogram bars are stacked by participant gender such that the total bar height reflects all participants in that age bin.
+**(B)** Participants ranged in pre-existing trivia expertise, as measured by their score out of 50 questions on a cued-recall general knowledge test.
+The median expertise score was 36/50 questions correct.
+
+### Figure 2: Trivia expertise as a function of gender
 
@@
 
-### Table 2: Participant breakdown by race
+### Table 1: Participant breakdown by race
 
@@
 
-```{r, include=FALSE}
+```{r age-mean-sd, include=FALSE}
 # These stats are in the paper!
@@
 ```
+
+```{r plot-jscore-by-age, include=FALSE}
+# TBD whether this should be rendered as a supplemental figure
+q_google_demos %>% 
+  inner_join(j_exp %>% 
+               mutate(subj_num = factor(subj_num)), 
+             by = "subj_num") %>% 
+  lm(scale(j_score) ~ scale(age), data = .) %>% 
+  summary()
+
+q_google_demos %>% 
+  inner_join(j_exp %>% 
+               mutate(subj_num = factor(subj_num)), 
+             by = "subj_num") %>% 
+  ggplot(aes(x = age, y = j_score)) + 
+  geom_point() + 
+  geom_smooth(method = "lm")
+```
+
+\newpage
 
@@
 
+\newpage
+
 ## Encoding task
@@
 ```{r include=FALSE}
-# These stats are in the paper!
+# These stats are in response to PB&R Reviewer 2's question about the encoding categories
 encoding <- tar_read(encoding, store = target_store)
 
+encoding_categories <- encoding %>% 
+  distinct(subj_num, j_score, group, category) %>% 
+  mutate(category = fct_relevel(category,
+                                "arms", "gems", "musi"),
+         category = fct_recode(category,
+                               "Arms and armor" = "arms",
+                               "Gemstone geology" = "gems",
+                               "Historical musical instruments" = "musi",
+                               "Prehistoric animals" = "dino",
+                               "How cars work" = "cars",
+                               "Cooking tools and techniques" = "cook"))
+
+encoding_categories %>% 
+  count(group, category) %>% 
+  group_by(group) %>% 
+  mutate(prob = n/sum(n))
+```
+
+```{r include=FALSE}
+# These stats are in the paper!
 encoding %>%
@@
 
-### Table 3: Model coefficients for encoding familiarity as a function of trivia expertise
+### Table 2: Model coefficients for encoding familiarity as a function of trivia expertise
 
@@
 tar_read(preplot_params_alreadyknew, store = target_store) %>%
+  mutate(term = recode_params_pretty(term)) %>% 
   group_by(term) %>% 
@@
 
-### Table 4: Model coefficients for encoding interest as a function of trivia expertise
+### Table 3: Model coefficients for encoding interest as a function of trivia expertise
 
@@
 tar_read(preplot_params_interest, store = target_store) %>%
+  mutate(term = recode_params_pretty(term),
+         term = fct_relevel(term, "Intercept")) %>% 
   group_by(term) %>% 
@@
 
+\newpage
+
 ## Retrieval tasks
 
-```{r include=FALSE}
+```{r load-retrieval}
+retrieval <- tar_read(retrieval, store = target_store) %>% 
+  left_join(q_google_demos, by = "subj_num")
+```
+
+### Figure 3: Recall as a function of semantic category
+
+```{r plot-recall-by-category}
+knitr::include_graphics(here::here("ignore", "figs", "ms_fig_supp_encoding_categories.png"))
+```
+
+**(A)** Median trivia expertise of participants assigned to each category is roughly evenly distributed around the whole-sample median trivia expertise (marked on the graph with a reference line).
+The number of participants assigned to each category is also visible (number of dots for each category).
+Across participants, the three “academic” categories were assigned roughly evenly, while among the three “non-academic” categories, prehistoric animal facts were presented to about 50% of participants.
+**(B)** Each dot represents one participant’s recall accuracy for novel facts, with each participant having one dot per color for their “academic” and “nonacademic” categories.
+Within the “academic” topics, recall performance was not significantly different across categories.
+Within the “non-academic” topics, performance in the car parts/functions category tended to be superior to that in the prehistoric animals and cooking tools/techniques categories (see following two Tables).
+
+\newpage
+
+### Table 4: Model coefficients for recall as a function of (academic) category and expertise 
+```{r}
+# These stats are in response to PB&R reviewers
+tar_read(preplot_params_fact_academic, store = target_store) %>%
+  mutate(term = recode_params_pretty(term),
+         term = fct_relevel(term, "Intercept"),
+         term = fct_recode(term,
+                           "Arms vs. gems" = "category_arms",
+                           "Musical instruments vs. gems" = "category_musi")) %>% 
+  group_by(term) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+"Academic" fact categories all showed similar recall performance.
+This model was run as a Bayesian multilevel logistic regression (with the same model settings as the main model reported in the main text) predicting novel "academic" fact recall (half of trials) as a function of fact category and trivia expertise, with a random intercept for each participant.
+Gemstone geology was coded as the baseline category, so coefficients reflect differences between gems vs.
+arms & armor, and gems vs.
+historical musical instruments.
+We also included covariates for interest at encoding and first vs.
+second museum, coded the same way as they were for the model in the main text.
+
+### Table 5: Model coefficients for recall as a function of (nonacademic) category and expertise
+
+```{r}
+# These stats are in response to PB&R reviewers
+tar_read(preplot_params_fact_nonacademic, store = target_store) %>%
+  mutate(term = recode_params_pretty(term),
+         term = fct_relevel(term, "Intercept"),
+         term = fct_recode(term,
+                           "Cooking vs. cars" = "category_cook",
+                           "Prehistoric animals vs. cars" = "category_dino")) %>% 
+  group_by(term) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+Of "nonacademic" fact categories, recall performance was higher for car facts, but independently of trivia expertise.
+This model was run as a Bayesian multilevel logistic regression (with the same model settings as the main model reported in the main text) predicting novel "nonacademic" fact recall (half of trials) as a function of fact category and trivia expertise, with a random intercept for each participant.
+Car parts/function was coded as the baseline category, so coefficients reflect differences between cars vs.
+cooking techniques, and cars vs.
+prehistoric animals.
+We also included covariates for interest at encoding and first vs.
+second museum, coded the same way as they were for the model in the main text.
+
+```{r recall-rt-start-by-age, include=FALSE}
+# These stats are in response to PB&R reviewers
+retrieval %>% 
+  lme4::lmer(rt_start_recall ~ scale(age, scale=F) + (1 | subj_num), data = .) %>% 
+  summary()
+```
+
+```{r recall-rt-end-by-age, include=FALSE}
+# These stats are in response to PB&R reviewers
+retrieval %>% 
+  lme4::lmer(rt_end_recall ~ scale(age, scale=F) + (1 | subj_num), data = .) %>% 
+  summary()
+```
+
+```{r recall-rt-timeout-by-age, include=FALSE}
+# These stats are in response to PB&R reviewers
+retrieval %>% 
+  filter(rt_end_recall >= 15000) %>% 
+  count(subj_num, age) %>% 
+  lm(n ~ scale(age, scale=F), data = .) %>% 
+  summary()
+```
+
+```{r encoding-retrieval-gap, include=FALSE}
+retrieval %>% 
+  select(subj_num, encoding_trial_num, retrieval_trial_num) %>% 
+  # estimated encoding trial length: 27 s (counting already knew and fixation)
+  mutate(encoding_trial_time = (encoding_trial_num - 1) * 27, 
+         # estimated retrieval trial length: 8 s, plus 5 min wait plus encoding offset
+         retrieval_trial_time = (retrieval_trial_num - 1) * 8 + 300 + max(encoding_trial_time), 
+         delay = retrieval_trial_time - encoding_trial_time) %>% 
+  summarize(mean_delay_min = mean(delay/60), sd_delay_min = sd(delay/60)) %>% 
+  mutate(across(where(is.numeric), \(x) signif(x, digits = 3)))
+```
+
+```{r preplot-params-fact-by-both-coefs, include=FALSE}
 # These stats are in the paper!
@@
 
-```{r include=FALSE}
+```{r preplot-params-fact-by-both-simple-fx, include=FALSE}
 # These stats are in the paper!
@@
 
-### Table 5: Model coefficients for photo memory as a function of trivia expertise
+```{r recall-rt-jscore, include=FALSE}
+# These stats are in the response to PB&R reviewers
+retrieval %>% 
+  # filter(acc_recall > 0) %>% 
+  mutate(across(starts_with("resp"), \(x) as.integer(x > 0)),
+         j_score = (j_score - 0.7) * 10) %>% 
+  lme4::glmer(rt_start_recall ~ j_score + (1 | subj_num), data = .) %>% 
+  broom.mixed::tidy()
+```
+
+```{r resp-pic-recall-rt, include=FALSE}
+# These stats are in the response to PB&R reviewers
+retrieval %>% 
+  filter(acc_recall > 0) %>% 
+  mutate(across(starts_with("resp"), \(x) as.integer(x > 0)),
+         j_score = (j_score - 0.7) * 10) %>% 
+  lme4::glmer(resp_pic ~ scale(rt_start_recall) * j_score + (1 | subj_num),
+              data = ., family = binomial) %>% 
+  broom.mixed::tidy()
+```
+
+```{r preplot-params-resp-pic-recall-rt-coefs, include=FALSE}
+# These stats are in the paper! After request by PB&R reviewers
+preplot_params_pic_rt.recall <- tar_read(preplot_params_pic_rt.recall, store = target_store)
+
+preplot_params_pic_rt.recall %>%
+  group_by(term) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+```{r preplot-params-resp-pic-recall-rt-simple-fx, include=FALSE}
+# These stats are in the paper! After request by PB&R reviewers
+# "low" trivia expertise for the preplots is j_score = -2
+# while "high" trivia expertise is +1
+preplot_params_pic_rt.recall %>% 
+  filter(term %in% c("rt_start_recall", "rt_start_recall:j_score")) %>% 
+  mutate(term = str_replace_all(term, ":", ".")) %>% 
+  pivot_wider(names_from = term,
+              values_from = estimate) %>% 
+  mutate(low = rt_start_recall - 2*rt_start_recall.j_score,
+         high = rt_start_recall + rt_start_recall.j_score) %>% 
+  select(iteration, low, high) %>% 
+  pivot_longer(cols = c(low, high),
+               names_to = "j_score",
+               values_to = "estimate") %>% 
+  group_by(j_score) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+```{r preplot-params-resp-source-recall-rt-coefs, include=FALSE}
+# These stats are in the paper! After request by PB&R reviewers
+preplot_params_source_rt.recall <- tar_read(preplot_params_source_rt.recall, store = target_store)
+
+preplot_params_source_rt.recall %>%
+  group_by(term) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+```{r preplot-params-resp-source-recall-rt-simple-fx, include=FALSE}
+# These stats are in the paper! After request by PB&R reviewers
+# "low" trivia expertise for the preplots is j_score = -2
+# while "high" trivia expertise is +1
+preplot_params_source_rt.recall %>% 
+  filter(term %in% c("rt_start_recall", "rt_start_recall:j_score")) %>% 
+  mutate(term = str_replace_all(term, ":", ".")) %>% 
+  pivot_wider(names_from = term,
+              values_from = estimate) %>% 
+  mutate(low = rt_start_recall - 2*rt_start_recall.j_score,
+         high = rt_start_recall + rt_start_recall.j_score) %>% 
+  select(iteration, low, high) %>% 
+  pivot_longer(cols = c(low, high),
+               names_to = "j_score",
+               values_to = "estimate") %>% 
+  group_by(j_score) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```
+
+```{r subset-correct-recall-details, include=FALSE}
+# These stats are also in the response to PB&R reviewers
+retrieval %>% 
+  filter(acc_recall > 0) %>% 
+  mutate(across(starts_with("resp"), \(x) as.integer(x > 0)),
+         no_details = as.integer(resp_source == 0 & resp_pic == 0),
+         j_score = (j_score - 0.7) * 10) %>% 
+  lme4::glmer(no_details ~ j_score + (1 | subj_num),
+              data = .,
+              family = binomial) %>% 
+  summary()
+```
+
+### Table 6: Model coefficients for photo memory as a function of trivia expertise
 
@@
 tar_read(preplot_params_pic, store = target_store) %>%
+  mutate(term = recode_params_pretty(term)) %>% 
   group_by(term) %>% 
@@
 
-### Table 6: Model coefficients for museum memory as a function of trivia expertise
+### Table 7: Model coefficients for museum memory as a function of trivia expertise
 
@@
 tar_read(preplot_params_source, store = target_store) %>%
+  mutate(term = recode_params_pretty(term)) %>% 
   group_by(term) %>% 
@@
 second museum, coded the same way as they were for the model in the main text.
+
+### Table 8: Model coefficients for fact recall as a function of expertise, for _familiar_ facts
+
+```{r}
+# Values from this table are also reported in the response to PB&R reviewers
+preplot_params_fact_by_both_known.facts <- tar_read(preplot_params_fact_by_both_known.facts, store = target_store)
+
+preplot_params_fact_by_both_known.facts %>% 
+  mutate(term = recode_params_pretty(term),
+         term = fct_relevel(term,
+                              "Intercept",
+                              "Interest at encoding",
+                              "Trivia expertise",
+                              "First vs. second museum",
+                              "Photo memory",
+                              "Museum memory",
+                              "Expertise x photo memory",
+                              "Expertise x museum memory",
+                              "Photo memory x museum memory",
+                              "Photo x museum x expertise")) %>% 
+  group_by(term) %>% 
+    summarize_kable(estimate,
+                    fn_list = fn_list_model.coefs)
+```
+
+This model was run as a Bayesian multilevel logistic regression, with the same model settings as the main model reported in the main text.
+This model has the exact same outcome and predictors as the main model, but has been fit only to trials where participants reported knowing "some" or "all" of the fact prior to the current study.
+Critically, we do not find the same three-way interaction effect of photo memory, museum memory, and trivia expertise when analyzing recall performance only for previously familiar facts.
+
+```{r include=FALSE}
+# These simple effect stats are in the response to PB&R reviewers
+preplot_params_fact_by_both_known.facts %>% 
+  filter(term %in% c("resp_pic", "resp_source", "resp_pic:j_score", "resp_source:j_score")) %>% 
+  mutate(term = str_replace_all(term, ":", ".")) %>% 
+  separate_wider_delim(term, delim = ".", names = c("term", "coef_type"), too_few = "align_start") %>% 
+  mutate(coef_type = if_else(is.na(coef_type), "main", "intxn")) %>% 
+  pivot_wider(names_from = coef_type,
+              values_from = estimate) %>% 
+  mutate(low = main - 2*intxn,
+         high = main + intxn) %>% 
+  select(iteration, term, low, high) %>% 
+  pivot_longer(cols = c(low, high),
+               names_to = "j_score",
+               values_to = "estimate") %>% 
+  group_by(term, j_score) %>% 
+  summarize_kable(estimate,
+                  fn_list = fn_list_model.coefs)
+```

### 2024-01-27 R/analyze/make_models.R

@@ -2,7 +2,7 @@
 
 ## prep data further ----
 
-prep_retrieval_data <- function (retrieval_data) {
+prep_retrieval_data <- function (retrieval_data, extra_cols = NULL) {
   out <- retrieval_data %>%
     # Just drop those extra columns now
     # The recipe validation is super annoying when there's a bunch of leftover cols
@@ -12,14 +12,48 @@ prep_retrieval_data <- function (retrieval_data) {
            j_score, 
            encoding_trial_num, 
            interest, 
-           already_knew)
+           already_knew,
+           {{extra_cols}})
   
   return (out)
 }
 
-make_retrieval_recipe <- function (retrieval_data_prepped) {
-  out <- recipe(retrieval_data_prepped) %>% 
-    step_filter(already_knew == "none") %>% 
+step_retrieval_covariates <- function (in_recipe) {
+  in_recipe %>% 
+    # So that there is a value that will get treated as the true middle
+    # Should never appear for the purposes of modeling
+    # But we need to be able to get a hypothetical middle trial for preplots
+    # with the effect code at 0
+    step_num2factor(encoding_trial_num,
+                    transform = \(x) case_when(x >= 41 ~ 3,
+                                               x > 40 & x < 41 ~ 2,
+                                               x <= 40 ~ 1,
+                                               TRUE ~ NA_real_),
+                    levels = c("early", "mid", "late"),
+                    ordered = TRUE) %>% 
+    step_ordinalscore(encoding_trial_num) %>%
+    # to get it to -0.5 and +0.5
+    # have to use step_range because ordinalscore requires int output
+    step_range(encoding_trial_num, min = -0.5, max = 0.5) %>% 
+    # scaling these to range of 10 makes it so unit change is 10% of the full range
+    step_range(interest, min = -5, max = 5) %>% 
+    # the actual lowest j_score is .26 so this gets it to the same range where a score of 0 would range down to -7
+    step_range(j_score, min = -4.4, max = 3) %>%
+    step_rename(from_encoding_late = encoding_trial_num)
+}
+
+make_retrieval_recipe <- function (retrieval_data_prepped, novel_facts = TRUE) {
+  out <- recipe(retrieval_data_prepped)
+  
+  if (novel_facts) {
+    out %<>%
+      step_filter(already_knew == "none")
+  } else {
+    out %<>%
[…]

### 2024-01-27 R/analyze/make_plots_ms.R

@@ -23,6 +23,24 @@ theme_ms <- function (base_size, base_family, ...) {
 
 ## functions ----
 
+recode_params_pretty <- function (col) {
+  quiet_fct_recode <- quietly(fct_recode)
+  out_quiet <- quiet_fct_recode(
+    col,
+    "Intercept" = "intercept",
+    "Interest at encoding" = "interest",
+    "Trivia expertise" = "j_score",
+    "First vs. second museum" = "from_encoding_late",
+    "Photo memory" = "resp_pic",
+    "Museum memory" = "resp_source",
+    "Expertise x photo memory" = "resp_pic:j_score",
+    "Expertise x museum memory" = "resp_source:j_score",
+    "Photo memory x museum memory" = "resp_pic:resp_source",
+    "Photo x museum x expertise" = "resp_pic:resp_source:j_score"
+  )
+  return (out_quiet$result)
+}
+
 make_plot_demos <- function (demo_data) {
   demo_data %>% 
     mutate(gender = coalesce(gender, "not reported")) %>% 
@@ -99,19 +117,12 @@ make_plot_coefs_fact_by_pic <- function (preplot_params) {
   preplot_params %>% 
     summarize_params() %>% 
     mutate(term = fct_relevel(term,
-                              "intercept",
-                              "interest",
-                              "j_score",
-                              "from_encoding_late",
-                              "resp_pic",
-                              "resp_pic:j_score"),
-           term = fct_recode(term,
-                             "Intercept" = "intercept",
-                             "Interest at encoding" = "interest",
-                             "Trivia expertise" = "j_score",
-                             "First vs. second museum" = "from_encoding_late",
-                             "Photo memory" = "resp_pic",
-                             "Expertise x photo memory" = "resp_pic:j_score")) %>% 
+                              "Intercept",
+                              "Interest at encoding",
+                              "Trivia expertise",
+                              "First vs. second museum",
+                              "Photo memory",
+                              "Expertise x photo memory")) %>% 
     make_plot_coefs()
 }
 
@@ -119,19 +130,12 @@ make_plot_coefs_fact_by_source <- function (preplot_params) {
   preplot_params %>% 
     summarize_params() %>%  
     mutate(term = fct_relevel(term,
-                              "intercept",
-                              "interest",
-                              "j_score",
-                              "from_encoding_late",
-                              "resp_source",
-                              "resp_source:j_score"),
-           term = fct_recode(term,
-                             "Intercept" = "intercept",
[…]

### 2024-01-27 _targets.R

@@ -260,6 +260,11 @@ target_models <- list(
              command = fit_retrieval_model(in_data = retrieval,
                                    in_formula = acc_recall ~ resp_pic * resp_source * j_score + from_encoding_late + interest + (1 | subj_num))
   ),
+  tar_target(name = model_fact_by_both_known.facts,
+             command = fit_retrieval_model(in_data = retrieval,
+                                           in_formula = acc_recall ~ resp_pic * resp_source * j_score + from_encoding_late + interest + (1 | subj_num),
+                                           novel_facts = FALSE)
+  ),
   tar_target(name = model_pic,
              command = fit_retrieval_model(in_data = retrieval,
                                            in_formula = resp_pic ~ j_score + from_encoding_late + interest + (1 | subj_num))
@@ -275,6 +280,25 @@ target_models <- list(
   tar_target(name = model_alreadyknew,
              command = fit_alreadyknew_model(in_data = retrieval,
                                           in_formula = already_knew ~ j_score + (1 | subj_num))
+  ),
+  tar_target(name = model_pic_rt.recall,
+             command = fit_retrieval.rt_model(in_data = retrieval,
+                                           in_formula = resp_pic ~ rt_start_recall * j_score + from_encoding_late + interest + (1 | subj_num))
+               ),
+  tar_target(name = model_source_rt.recall,
+             command = fit_retrieval.rt_model(in_data = retrieval,
+                                              in_formula = resp_source ~ rt_start_recall * j_score + from_encoding_late + interest + (1 | subj_num))
+  ),
+  tar_target(name = model_fact_academic,
+             command = fit_retrieval.category_model(in_data = retrieval,
+                                                    # the formula is like this bc step_dummy renames the dummy vars
+                                                    in_formula = acc_recall ~ category_arms + category_musi + j_score + from_encoding_late + interest + (1 | subj_num),
+                                                    category_group = "academic")
+  ),
+  tar_target(name = model_fact_nonacademic,
+             command = fit_retrieval.category_model(in_data = retrieval,
+                                                    in_formula = acc_recall ~ category_cook + category_dino + j_score + from_encoding_late + interest + (1 | subj_num),
+                                                    category_group = "nonacademic")
   )
 )
 
@@ -285,6 +309,9 @@ target_preplots <- list(
              ),
   tar_target(name = preplot_params_fact_by_both,
              command = posterior_preplot_params(model_fact_by_both)
+  ),
+  tar_target(name = preplot_params_fact_by_both_known.facts,
[…]

### 2024-02-05 writing/supplement.Rmd
update post revision title and authors full names

@@
 title: "Supplementary material"
-subtitle: "Main paper: Episodic memory bolsters acquisition of new semantic knowledge in trivia experts"
-author: "MT, LW, & MA"
+subtitle: "Main paper: New semantic knowledge is more strongly coupled with episodic memory in trivia experts"
+author: "Monica K. Thieu, Lauren J. Wilkins, & Mariam Aly"
 date: "Updated `r Sys.Date()`"
